---
title: "(Phospho-)flow cytometry annotation"
author: "mwitmond"
date: "2024-03-11"
output:
  workflowr::wflow_html:
    toc: TRUE
    toc_float: 
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
editor_options:
  chunk_output_type: console
---


## Set-up

```{r setup, message=F, warning=F}
knitr::opts_chunk$set(
  message = F, warning = F, echo = T, eval = T
)

# Load required packages
source("code/packages_FACS.R", local = knitr::knit_global())
```



## DS102: StimTest

### Load data

Load the gated dataset and create a dataset with live single cells
```{r data_DS102}
# HBL1 data
gs_HBL1 <- load_gs(paste0("output/DS102_StimTest/", "flow_gated_HBL1"))
gated_pops_HBL1 <- gs_get_pop_paths(gs_HBL1, path = "auto")
cs_HBL1 <- gs_pop_get_data(gs_HBL1, tail(gated_pops_HBL1, 1))
df_HBL1 <- fortify(cs_HBL1)
df_HBL1[df_HBL1 <= 0] <- NA # Remove all zero values from df in order to perform log transformations

# OCI-Ly8 data
gs_Ly8 <- load_gs(paste0("output/DS102_StimTest/", "flow_gated_Ly8"))
gated_pops_Ly8 <- gs_get_pop_paths(gs_Ly8, path = "auto")
cs_Ly8 <- gs_pop_get_data(gs_Ly8, tail(gated_pops_Ly8, 1))
df_Ly8 <- fortify(cs_Ly8)
df_Ly8[df_Ly8 <= 0] <- NA # Remove all zero values from df in order to perform log transformations

# Combine all cell line datasets
df_DS102 <- list(df_HBL1, df_Ly8) %>% reduce(full_join)

# Select only columns that are needed
df_DS102 <- df_DS102[ , c("name", "plateID", "rowID", "colID", "wellID", "FSC.A", "SSC.A", "BV421.A", "PE.A", "Alexa.647.A", "Alexa.488.A")]

gc()
```

```{r metadata_DS102}
# Add metadata per well from custom .csv file
metadata_DS102 <- read_csv("data/DS102_StimTest/flow/metadata_plate_DS102.csv")

# Change columns into character if necessary
metadata_DS102$colID <- as.character(metadata_DS102$colID)

df_DS102 <- left_join(df_DS102, metadata_DS102)

# Remove samples with <5000 cells (except if the sample is t = 0 min)
counts_DS102 <- df_DS102 %>% count(plateID, wellID, name = "sample_cell_count")
df_DS102 <- left_join(df_DS102, counts_DS102)
df_DS102 <- df_DS102[df_DS102$sample_cell_count > 5000, ]

gc()

# kable(df_DS102 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Transform data

Pivot the full dataset into a tidy dataset
```{r tidy_DS102}
# Combine all data into one tidy dataframe (all data in one column instead of one column for each fluor)
cols_meta_DS102 <- c("plateID", "wellID", "sample", "cell_line", "stimulus", "conc", "conc_text", "description",  "staining", "sample_cell_count") # include all metadata columns
         
df_PE_DS102 <- df_DS102 %>% 
  select(all_of(cols_meta_DS102), protein_PE, PE.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "PE") %>%
  rename(
    protein = protein_PE, 
    fluorescence = PE.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF647_DS102 <- df_DS102 %>% 
  select(all_of(cols_meta_DS102), protein_AF647, Alexa.647.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF647") %>%
  rename(
    protein = protein_AF647, 
    fluorescence = Alexa.647.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF488_DS102 <- df_DS102 %>% 
  select(all_of(cols_meta_DS102), protein_AF488, Alexa.488.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF488") %>%
  rename(
    protein = protein_AF488, 
    fluorescence = Alexa.488.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_BV421_DS102 <- df_DS102 %>% 
  select(all_of(cols_meta_DS102), protein_BV421, BV421.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "BV421") %>%
  rename(
    protein = protein_BV421, 
    fluorescence = BV421.A, 
    FSC = FSC.A, 
    SSC = SSC.A)

df_tidy_DS102 <- list(df_PE_DS102, df_AF647_DS102, df_AF488_DS102, df_BV421_DS102) %>% reduce(full_join)

gc()

# kable(df_tidy_DS102 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r percent_on_DS102}
data_info_DS102 <- df_tidy_DS102 %>%
  filter(conc == "0") %>%
  group_by(plateID, cell_line, protein) %>%
  summarise(zero_quant97.5 = quantile(fluorescence, c(0.975), na.rm = T))

df_tidy_DS102 <- left_join(df_tidy_DS102, data_info_DS102)

# Create dataframe with percentage ON for each condition
data_total_DS102 <- df_tidy_DS102 %>%
  group_by(plateID, wellID, protein) %>%
  count(name = "count_total")

data_on_DS102 <- df_tidy_DS102 %>%
  filter((fluorescence - zero_quant97.5) > 0) %>%
  group_by(plateID, wellID, protein) %>%
  count(name = "count_on")

data_counts_DS102 <- left_join(data_total_DS102, data_on_DS102) %>%
  mutate(percent_on = (count_on / count_total) * 100)

df_tidy_DS102 <- left_join(df_tidy_DS102, data_counts_DS102)

gc()

kable(df_tidy_DS102 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r fig1_ridge_cell_DS102, fig.width=7, fig.height=4}
cells_DS102 <- c("HBL1", "BJAB", "OCI-Ly8")
conc_DS102 <- c("PBS", 
                "5 ug/mL aIg", "10 ug/mL aIg", "20 ug/mL aIg",
                "3.3 mM H2O2", "10 mM H2O2", "20 mM H2O2",
                "3.3 H2O2 + 10 aIg", "10 H2O2 + 10 aIg", "10 H2O2 + 20 aIg", "15 H2O2 + 15 aIg")

ggplot(subset(df_tidy_DS102, protein == "pPLCy2 (Y759)"), aes(x = fluorescence)) +
  geom_density_ridges(
    aes(y = factor(conc_text, levels = rev(conc_DS102))),
    scale = 2, 
    fill = "#006699", 
    alpha = 0.5
  ) +
  geom_vline(aes(xintercept = zero_quant97.5), linewidth = 0.5) +
  facet_wrap(vars(factor(cell_line, levels = cells_DS102))) +
  scale_x_logicle() + # logicle scale instead of log10 scale
  labs(x = paste("Fluorescent intensity PLCy2"), y = "") +
  theme_bw() +
  theme(legend.position = "none", panel.grid.minor = element_blank())
```

### Median data

Calculate median fluorescent values for each sample/replicate
```{r medians_sample_DS102}
# Calculate median values for each sample
medians_DS102 <- df_tidy_DS102 %>% 
  group_by(plateID, wellID, protein, fluor) %>% 
  summarise_at(vars(fluorescence), list(fluorescence_median = median), na.rm = TRUE)

medians_tidy_DS102 <- left_join(medians_DS102, distinct(select(df_tidy_DS102, cols_meta_DS102))) %>%
  left_join(data_counts_DS102)

# Calculate fold change compared to conc 0 (average of 0 ug/mL aIg + 0 mM H2O2)
median_zero_DS102 <- medians_tidy_DS102 %>%
  filter(conc == "0") %>%
  group_by(plateID, cell_line, protein) %>%
  summarise(zero_median = mean(fluorescence_median))

medians_tidy_DS102 <- left_join(medians_tidy_DS102, median_zero_DS102) %>%
  mutate(FC = (fluorescence_median / zero_median), 
         log2FC = log2(FC))

gc()

# kable(medians_tidy_DS102 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Save data

Save annotated datasets as .csv file
```{r save_DS102}
write.csv(df_tidy_DS102, file = "output/DS102_StimTest/flow_ann/flow_data_DS102.csv", row.names = F)

write.csv(medians_tidy_DS102, file = "output/DS102_StimTest/flow_ann/flow_medians_DS102.csv", row.names = F)
```

```{r clear_DS102}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "_DS102"))
rm(list = ls(pattern = "_HBL1"))
rm(list = ls(pattern = "_Ly8"))
gc()
```



## DS104: StimInhibTest

### Load data

Load the gated dataset and create a dataset with live single cells
```{r data_DS104}
# HBL1 data
gs_HBL1 <- load_gs(paste0("output/DS104_StimInhibTest/", "flow_gated_HBL1"))
gated_pops_HBL1 <- gs_get_pop_paths(gs_HBL1, path = "auto")
cs_HBL1 <- gs_pop_get_data(gs_HBL1, tail(gated_pops_HBL1, 1))
df_HBL1 <- fortify(cs_HBL1)
df_HBL1[df_HBL1 <= 0] <- NA # Remove all zero values from df in order to perform log transformations

# OCI-Ly8 data
gs_Ly8 <- load_gs(paste0("output/DS104_StimInhibTest/", "flow_gated_Ly8"))
gated_pops_Ly8 <- gs_get_pop_paths(gs_Ly8, path = "auto")
cs_Ly8 <- gs_pop_get_data(gs_Ly8, tail(gated_pops_Ly8, 1))
df_Ly8 <- fortify(cs_Ly8)
df_Ly8[df_Ly8 <= 0] <- NA # Remove all zero values from df in order to perform log transformations

# Combine all cell line datasets
df_DS104 <- list(df_HBL1, df_Ly8) %>% reduce(full_join)

# Select only columns that are needed
df_DS104 <- df_DS104[ , c("name", "plateID", "rowID", "colID", "wellID", "FSC.A", "SSC.A", "BV421.A", "PE.A", "Alexa.647.A", "Alexa.488.A")]

gc()
```

```{r metadata_DS104}
# Add metadata per well from custom .csv file
metadata_DS104 <- read_csv("data/DS104_StimInhibTest/flow/metadata_plate_DS104.csv")

# Change columns into character if necessary
metadata_DS104$colID <- as.character(metadata_DS104$colID)

df_DS104 <- left_join(df_DS104, metadata_DS104)

# Remove samples with <5000 cells (except if the sample is t = 0 min)
counts_DS104 <- df_DS104 %>% count(plateID, wellID, name = "sample_cell_count")
df_DS104 <- left_join(df_DS104, counts_DS104)
df_DS104 <- df_DS104[df_DS104$sample_cell_count > 5000, ]

gc()

# kable(df_DS104 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Transform data

Pivot the full dataset into a tidy dataset
```{r tidy_DS104}
# Combine all data into one tidy dataframe (all data in one column instead of one column for each fluor)
cols_meta_DS104 <- c("plateID", "wellID", "sample", "cell_line", "stimulus", "inhibitor", "description", "descript_cell_inhib", "descript_cell_stim", "descript_inhib_stim", "descript_inhib_stim_no", "staining", "nostain") # include all metadata columns
         
df_PE_DS104 <- df_DS104 %>% 
  select(all_of(cols_meta_DS104), protein_PE, PE.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "PE") %>%
  rename(
    protein = protein_PE, 
    fluorescence = PE.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF647_DS104 <- df_DS104 %>% 
  select(all_of(cols_meta_DS104), protein_AF647, Alexa.647.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF647") %>%
  rename(
    protein = protein_AF647, 
    fluorescence = Alexa.647.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF488_DS104 <- df_DS104 %>% 
  select(all_of(cols_meta_DS104), protein_AF488, Alexa.488.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF488") %>%
  rename(
    protein = protein_AF488, 
    fluorescence = Alexa.488.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_BV421_DS104 <- df_DS104 %>% 
  select(all_of(cols_meta_DS104), protein_BV421, BV421.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "BV421") %>%
  rename(
    protein = protein_BV421, 
    fluorescence = BV421.A, 
    FSC = FSC.A, 
    SSC = SSC.A)

df_tidy_DS104 <- list(df_PE_DS104, df_AF647_DS104, df_AF488_DS104, df_BV421_DS104) %>% reduce(full_join)

gc()

# kable(df_tidy_DS104 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r percent_on_DS104}
data_info_DS104 <- df_tidy_DS104 %>%
  filter(stimulus == "PBS" & inhibitor == "DMSO") %>%
  group_by(plateID, cell_line, protein) %>%
  summarise(zero_quant97.5 = quantile(fluorescence, c(0.975), na.rm = T))

df_tidy_DS104 <- left_join(df_tidy_DS104, data_info_DS104)

# Create dataframe with percentage ON for each condition
data_total_DS104 <- df_tidy_DS104 %>%
  group_by(plateID, wellID, protein) %>%
  count(name = "count_total")

data_on_DS104 <- df_tidy_DS104 %>%
  filter((fluorescence - zero_quant97.5) > 0) %>%
  group_by(plateID, wellID, protein) %>%
  count(name = "count_on")

data_counts_DS104 <- left_join(data_total_DS104, data_on_DS104) %>%
  mutate(percent_on = (count_on / count_total) * 100)

df_tidy_DS104 <- left_join(df_tidy_DS104, data_counts_DS104)

gc()

kable(df_tidy_DS104 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r fig1_ridge_cell_DS104, fig.width=7, fig.height=4}
treat_DS104 <- c("DMSO PBS nostain", "DMSO PBS", "iSYK PBS", "iBTK PBS", "iPI3Kd PBS", "iNFkB PBS", 
                 "DMSO aIg/H2O2", "iSYK aIg/H2O2", "iBTK aIg/H2O2", "iPI3Kd aIg/H2O2", "iNFkB aIg/H2O2")

ggplot(subset(df_tidy_DS104, protein == "pPLCy2 (Y759)"), aes(x = fluorescence)) +
  geom_density_ridges(
    aes(y = factor(descript_inhib_stim_no, levels = rev(treat_DS104))),
    scale = 2, 
    fill = "#006699", 
    alpha = 0.5
  ) +
  geom_vline(aes(xintercept = zero_quant97.5), linewidth = 0.5) +
  facet_wrap(vars(factor(cell_line))) +
  scale_x_logicle() + # logicle scale instead of log10 scale
  labs(x = paste("Fluorescent intensity PLCy2"), y = "") +
  theme_bw() +
  theme(legend.position = "none", panel.grid.minor = element_blank())
```


### Median data

Calculate median fluorescent values for each sample/replicate
```{r medians_sample_DS104}
# Calculate median values for each sample
medians_DS104 <- df_tidy_DS104 %>% 
  group_by(plateID, wellID, protein, fluor) %>% 
  summarise_at(vars(fluorescence), list(fluorescence_median = median), na.rm = TRUE)

medians_tidy_DS104 <- left_join(medians_DS104, distinct(select(df_tidy_DS104, cols_meta_DS104))) %>%
  left_join(data_counts_DS104)

# Calculate fold change compared to DMSO PBS
median_zero_DS104 <- medians_tidy_DS104 %>%
  filter(stimulus == "PBS" & inhibitor == "DMSO") %>%
  group_by(plateID, cell_line, protein) %>%
  summarise(zero_median = mean(fluorescence_median))

medians_tidy_DS104 <- left_join(medians_tidy_DS104, median_zero_DS104) %>%
  mutate(FC_median = (fluorescence_median / zero_median), 
         log2FC_median = log2(FC_median))

gc()

# kable(medians_tidy_DS104 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r sum_sample_DS104}
# Calculate median values for each sample
sums_DS104 <- df_tidy_DS104 %>% 
  group_by(plateID, wellID, protein, fluor) %>% 
  summarise_at(vars(fluorescence), list(fluorescence_sum = sum), na.rm = TRUE)

medians_tidy_DS104 <- medians_tidy_DS104 %>% 
  left_join(sums_DS104)

# Calculate fold change compared to DMSO PBS
sums_zero_DS104 <- medians_tidy_DS104 %>%
  filter(stimulus == "PBS" & inhibitor == "DMSO") %>%
  group_by(plateID, cell_line, protein) %>%
  summarise(zero_sum = mean(fluorescence_sum))

medians_tidy_DS104 <- left_join(medians_tidy_DS104, sums_zero_DS104) %>%
  mutate(FC_sum = (fluorescence_sum / zero_sum), 
         log2FC_sum = log2(FC_sum))

gc()

# kable(medians_tidy_DS104 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

### Save data

Save annotated datasets as .csv file
```{r save_DS104}
write.csv(df_tidy_DS104, file = "output/DS104_StimInhibTest/flow_ann/flow_data_DS104.csv", row.names = F)

write.csv(medians_tidy_DS104, file = "output/DS104_StimInhibTest/flow_ann/flow_medians_DS104.csv", row.names = F)
```

```{r clear_DS104}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "_DS104"))
rm(list = ls(pattern = "_HBL1"))
rm(list = ls(pattern = "_Ly8"))
gc()
```



## DS108: StimInhibIDseq

### Load data

Load the gated dataset and create a dataset with live single cells
```{r data_DS108}
gs_DS108 <- load_gs(paste0("output/DS108_StimInhibIDseq/", "flow_gated"))
gated_pops_DS108 <- gs_get_pop_paths(gs_DS108, path = "auto")
cs_DS108 <- gs_pop_get_data(gs_DS108, tail(gated_pops_DS108, 1))
df_DS108 <- fortify(cs_DS108)
df_DS108[df_DS108 <= 0] <- NA # Remove all zero values from df in order to perform log transformations

# Select only columns that are needed
df_DS108 <- df_DS108[ , c("name", "plateID", "rowID", "colID", "wellID", "FSC.A", "SSC.A", "BV421.A", "PE.A", "Alexa.647.A", "Alexa.488.A")]

gc()
```

```{r metadata_DS108}
# Add metadata per well from custom .csv file
metadata_DS108 <- read_csv("data/DS108_StimInhibIDseq/flow/metadata_plate_DS108.csv")

# Change columns into character if necessary
metadata_DS108$colID <- as.character(metadata_DS108$colID)
df_DS108 <- left_join(df_DS108, metadata_DS108)

# Remove samples with <5000 cells (except if the sample is t = 0 min)
counts_DS108 <- df_DS108 %>% count(plateID, wellID, name = "sample_cell_count")
df_DS108 <- left_join(df_DS108, counts_DS108)
df_DS108 <- df_DS108[df_DS108$sample_cell_count > 5000, ]

gc()

# kable(df_DS108 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Transform data

Pivot the full dataset into a tidy dataset
```{r tidy_DS108}
# Combine all data into one tidy dataframe (all data in one column instead of one column for each fluor)
cols_meta_DS108 <- c("plateID", "wellID", "sample", "cell_line", "stimulus", "inhibitor", "inhib_conc_uM", "inhib_conc", "inhib_conc_text", "description", "staining") # include all metadata columns

df_PE_DS108 <- df_DS108 %>% 
  select(all_of(cols_meta_DS108), protein_PE, PE.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "PE") %>%
  rename(
    protein = protein_PE, 
    fluorescence = PE.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF647_DS108 <- df_DS108 %>% 
  select(all_of(cols_meta_DS108), protein_AF647, Alexa.647.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF647") %>%
  rename(
    protein = protein_AF647, 
    fluorescence = Alexa.647.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_AF488_DS108 <- df_DS108 %>% 
  select(all_of(cols_meta_DS108), protein_AF488, Alexa.488.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "AF488") %>%
  rename(
    protein = protein_AF488, 
    fluorescence = Alexa.488.A, 
    FSC = FSC.A, 
    SSC = SSC.A)
df_BV421_DS108 <- df_DS108 %>% 
  select(all_of(cols_meta_DS108), protein_BV421, BV421.A, FSC.A, SSC.A) %>% 
  mutate(fluor = "BV421") %>%
  rename(
    protein = protein_BV421, 
    fluorescence = BV421.A, 
    FSC = FSC.A, 
    SSC = SSC.A)

df_tidy_DS108 <- list(df_PE_DS108, df_AF647_DS108, df_AF488_DS108, df_BV421_DS108) %>% reduce(full_join)

gc()

# kable(df_tidy_DS108 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r percent_on_DS108}
data_info_DS108 <- df_tidy_DS108 %>%
  filter(stimulus == "PBS" & inhib_conc == "0 uM") %>%
  group_by(plateID, cell_line, protein) %>% 
  summarise(zero_quant97.5 = quantile(fluorescence, c(0.975), na.rm = T))

df_tidy_DS108 <- left_join(df_tidy_DS108, data_info_DS108)

# Create dataframe with percentage ON for each condition
data_total_DS108 <- df_tidy_DS108 %>%
  group_by(plateID, wellID, protein) %>%
  count(name = "count_total")

data_on_DS108 <- df_tidy_DS108 %>%
  filter((fluorescence - zero_quant97.5) > 0) %>%
  group_by(plateID, wellID, protein) %>%
  count(name = "count_on")

data_counts_DS108 <- left_join(data_total_DS108, data_on_DS108) %>%
  mutate(percent_on = (count_on / count_total) * 100)

df_tidy_DS108 <- left_join(df_tidy_DS108, data_counts_DS108)

gc()

kable(df_tidy_DS108 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r fig1_ridge_cell_DS108, fig.width=6, fig.height=5}
ggplot(subset(df_tidy_DS108, protein == "pPLCy2 (Y759)"), aes(x = fluorescence)) +
  geom_density_ridges(
    aes(y = factor(inhib_conc, levels = c("100 uM", "0 uM")), fill = stimulus),
    scale = 1, 
    alpha = 0.5
  ) +
  geom_vline(aes(xintercept = zero_quant97.5), linewidth = 0.5) +
  facet_grid(vars(factor(inhibitor, levels = c("iSYK", "iBTK", "iPI3Kd", "iNFkB"))), vars(factor(cell_line))) +
  scale_fill_manual(values = c(PBS = "black", "aIg+H2O2" = "orange"), name = "") +
  scale_x_logicle() + # logicle scale instead of log10 scale
  labs(x = paste("Fluorescent intensity PLCy2"), y = "") +
  theme_bw() +
  theme(legend.position = "none", panel.grid.minor = element_blank())
```


### Median data

Calculate median fluorescent values for each sample/replicate
```{r medians_sample_DS108}
# Calculate median values for each sample
medians_DS108 <- df_tidy_DS108 %>% 
  group_by(plateID, wellID, protein, fluor) %>% 
  summarise_at(vars(fluorescence), list(fluorescence_median = median), na.rm = TRUE)

medians_tidy_DS108 <- left_join(medians_DS108, distinct(select(df_tidy_DS108, cols_meta_DS108))) %>%
  left_join(data_counts_DS108)

# Calculate fold change compared to DMSO PBS
median_zero_DS108 <- medians_tidy_DS108 %>%
  filter(stimulus == "PBS" & inhib_conc == "0 uM") %>%
  group_by(plateID, cell_line, protein) %>% 
  summarise(zero_median = mean(fluorescence_median))

medians_tidy_DS108 <- left_join(medians_tidy_DS108, median_zero_DS108) %>%
  mutate(FC_median = (fluorescence_median / zero_median), 
         log2FC_median = log2(FC_median))

gc()

# kable(medians_tidy_DS108 %>% head(5)) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```


### Save data

Save annotated datasets as .csv file
```{r save_DS108}
write.csv(df_tidy_DS108, file = "output/DS108_StimInhibIDseq/flow_ann/flow_data_DS108.csv", row.names = F)

write.csv(medians_tidy_DS108, file = "output/DS108_StimInhibIDseq/flow_ann/flow_medians_DS108.csv", row.names = F)
```

```{r clear_DS108}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "_DS108"))
gc()
```
