---
title: "ID-seq from FASTQ to count tables"
author: "mwitmond"
date: "2024-03-11"
output:
  workflowr::wflow_html:
    toc: TRUE
    toc_float: 
      collapsed: FALSE
    toc_depth: 3
editor_options:
  chunk_output_type: console
---


## Set-up 

Note: Run all bash code in the terminal (Ubuntu on Windows)

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = F, warning = F, echo = T, eval = T
)
```

```{r libraries}
library(rjson)
library(kableExtra)
library(dplyr)
```

Install the conda environment from a .yml file
```{bash conda_install, eval=F}
# Check the directories for conda environments
conda config --show envs_dirs

# Move to directory with conda_environment.yml file:
cd /mnt/c/Users/meldew/'OneDrive - Radboud Universiteit'/Documenten/data/analysis/template_data_analysis_MW/data/config

# Install conda environment (done only once)
conda env create -f conda_environment.yml
# Environment name: bulkIDseq_kite
# Location: /home/meldewitmond/.conda/envs/bulkIDseq_kite
```


## DS108: StimInhibIDseq

### FASTQ to counts

Activate the conda environment from a .yml file
```{bash conda_activate, eval=F}
# Activate the correct conda environment
conda activate bulkIDseq_kite

# Move to directory with all configuration files:
cd /mnt/c/Users/meldew/'OneDrive - Radboud Universiteit'/Documenten/data/analysis/manuscript_IDseq_DLBCL/data/DS108_StimInhibIDseq/config
```

Step 1: Prepare index and mismatch files to use [kite](https://github.com/pachterlab/kite) from pachterlab.

Use the manually created FeatureBarcodes.csv file, custom_whitelist.txt file and other config files: Huck/Cells/DynSign/GeneralProtocols/general_sequencing_metadata_files/config

#### plateA

```{bash prep_A, eval=F}
# Prepare folders for processing in the data folder:
cd ..
mkdir counts
cd counts
mkdir plateA
cd plateA
```

```{bash count_tables_A, eval=F}
# Create the pseudoalignment of the reads (including time of running in the output)
# Adjust the .fastq.gz file names
time kallisto bus -i ../../config/FeaturesMismatch.idx -o ./ -x 10xv3 -t 4 ../../FASTQ/44375_DS108_A_HLB1_pbs_A42_R1.fastq.gz ../../FASTQ/44375_DS108_A_HLB1_pbs_A42_R2.fastq.gz

# Make the corrected bus
time bustools correct -w ../../config/custom_whitelist.txt output.bus -o output_corrected.bus

# Sort the corrected bus (can take very long with RNA seq; more reads = more time)
time bustools sort -t 4 -o output_sorted.bus output_corrected.bus

# Make count table (.mtx file)
mkdir featurecounts
time bustools count -o featurecounts/featurecounts --genecounts -g ../../config/FeaturesMismatch.t2g -e ./matrix.ec -t ./transcripts.txt ./output_sorted.bus
# Location of count tables: data\counts\plateA\featurecounts

cd ..
```


#### plateB

```{bash prep_B, eval=F}
# Prepare folders for processing in the data folder:
# cd ..
# mkdir counts
# cd counts
mkdir plateB
cd plateB
```

```{bash count_tables_B, eval=F}
# Create the pseudoalignment of the reads (including time of running in the output)
# Adjust the .fastq.gz file names
time kallisto bus -i ../../config/FeaturesMismatch.idx -o ./ -x 10xv3 -t 4 ../../FASTQ/44376_DS108_B_HBL1_stim_A43_R1.fastq.gz ../../FASTQ/44376_DS108_B_HBL1_stim_A43_R2.fastq.gz

# Make the corrected bus
time bustools correct -w ../../config/custom_whitelist.txt output.bus -o output_corrected.bus

# Sort the corrected bus (can take very long with RNA seq; more reads = more time)
time bustools sort -t 4 -o output_sorted.bus output_corrected.bus

# Make count table (.mtx file)
mkdir featurecounts
time bustools count -o featurecounts/featurecounts --genecounts -g ../../config/FeaturesMismatch.t2g -e ./matrix.ec -t ./transcripts.txt ./output_sorted.bus
# Location of count tables: data\counts\plateA\featurecounts

cd ..
```


#### plateC

```{bash prep_C, eval=F}
# Prepare folders for processing in the data folder:
# cd ..
# mkdir counts
# cd counts
mkdir plateC
cd plateC
```

```{bash count_tables_C, eval=F}
# Create the pseudoalignment of the reads (including time of running in the output)
# Adjust the .fastq.gz file names
time kallisto bus -i ../../config/FeaturesMismatch.idx -o ./ -x 10xv3 -t 4 ../../FASTQ/44377_DS108_C_OCI_pbs_A46_R1.fastq.gz ../../FASTQ/44377_DS108_C_OCI_pbs_A46_R2.fastq.gz

# Make the corrected bus
time bustools correct -w ../../config/custom_whitelist.txt output.bus -o output_corrected.bus

# Sort the corrected bus (can take very long with RNA seq; more reads = more time)
time bustools sort -t 4 -o output_sorted.bus output_corrected.bus

# Make count table (.mtx file)
mkdir featurecounts
time bustools count -o featurecounts/featurecounts --genecounts -g ../../config/FeaturesMismatch.t2g -e ./matrix.ec -t ./transcripts.txt ./output_sorted.bus
# Location of count tables: data\counts\plateA\featurecounts

cd ..
```


#### plateD

```{bash prep_D, eval=F}
# Prepare folders for processing in the data folder:
# cd ..
# mkdir counts
# cd counts
mkdir plateD
cd plateD
```

```{bash count_tables_D, eval=F}
# Create the pseudoalignment of the reads (including time of running in the output)
# Adjust the .fastq.gz file names
time kallisto bus -i ../../config/FeaturesMismatch.idx -o ./ -x 10xv3 -t 4 ../../FASTQ/44378_DS108_D_OCI_stim_A47_R1.fastq.gz ../../FASTQ/44378_DS108_D_OCI_stim_A47_R2.fastq.gz

# Make the corrected bus
time bustools correct -w ../../config/custom_whitelist.txt output.bus -o output_corrected.bus

# Sort the corrected bus (can take very long with RNA seq; more reads = more time)
time bustools sort -t 4 -o output_sorted.bus output_corrected.bus

# Make count table (.mtx file)
mkdir featurecounts
time bustools count -o featurecounts/featurecounts --genecounts -g ../../config/FeaturesMismatch.t2g -e ./matrix.ec -t ./transcripts.txt ./output_sorted.bus
# Location of count tables: data\counts\plateA\featurecounts

cd ..
```



### Run log {.tabset}

#### plateA

```{r run_log_A, eval=F}
# Print info on count generation run
PROT_log<- rjson::fromJSON(file = "data/counts/plateA/run_info.json")
PROT_log<- do.call(rbind, lapply(PROT_log, data.frame))
colnames (PROT_log) <- ""
PROT_log %>%
  kbl() %>%
  kable_styling()
```


#### plateB

```{r run_log_B, eval=F}
# Print info on count generation run
PROT_log<- rjson::fromJSON(file = "data/counts/plateB/run_info.json")
PROT_log<- do.call(rbind, lapply(PROT_log, data.frame))
colnames (PROT_log) <- ""
PROT_log %>%
  kbl() %>%
  kable_styling()
```


#### plateC

```{r run_log_C, eval=F}
# Print info on count generation run
PROT_log<- rjson::fromJSON(file = "data/counts/plateC/run_info.json")
PROT_log<- do.call(rbind, lapply(PROT_log, data.frame))
colnames (PROT_log) <- ""
PROT_log %>%
  kbl() %>%
  kable_styling()
```


#### plateD

```{r run_log_D, eval=F}
# Print info on count generation run
PROT_log<- rjson::fromJSON(file = "data/counts/plateD/run_info.json")
PROT_log<- do.call(rbind, lapply(PROT_log, data.frame))
colnames (PROT_log) <- ""
PROT_log %>%
  kbl() %>%
  kable_styling()
```


### Output

Unfiltered counts are stored (for each sample) in data/counts/plate/featurecounts/ folder as .mtx format (sparse matrix). 



## DS113: InhibCombiIDseq

### FASTQ to counts

Activate the conda environment from a .yml file
```{bash conda_activate_DS113, eval=F}
# Activate the correct conda environment
conda activate bulkIDseq_kite

# Move to directory with all configuration files:
cd /mnt/c/Users/meldew/'OneDrive - Radboud Universiteit'/Documenten/data/analysis/manuscript_IDseq_DLBCL/data/DS113_InhibCombiIDseq/config
```

Step 1: Prepare index and mismatch files to use [kite](https://github.com/pachterlab/kite) from pachterlab.

Use the manually created FeatureBarcodes.csv file, custom_whitelist.txt file and other config files: Huck/Cells/DynSign/GeneralProtocols/general_sequencing_metadata_files/config

#### plateA

```{bash prep_DS113, eval=F}
# Prepare folders for processing in the data folder:
cd ..
mkdir counts
cd counts
mkdir plateA
cd plateA
```

```{bash count_tables_DS113, eval=F}
# Create the pseudoalignment of the reads (including time of running in the output)
# Adjust the .fastq.gz file names
time kallisto bus -i ../../config/FeaturesMismatch.idx -o ./ -x 10xv3 -t 4 ../../FASTQ/45408_MeldeWitmond_DS113_DLBCL_A48_R1.fastq.gz ../../FASTQ/45408_MeldeWitmond_DS113_DLBCL_A48_R2.fastq.gz

# Make the corrected bus
time bustools correct -w ../../config/custom_whitelist.txt output.bus -o output_corrected.bus

# Sort the corrected bus (can take very long with RNA seq; more reads = more time)
time bustools sort -t 4 -o output_sorted.bus output_corrected.bus

# Make count table (.mtx file)
mkdir featurecounts
time bustools count -o featurecounts/featurecounts --genecounts -g ../../config/FeaturesMismatch.t2g -e ./matrix.ec -t ./transcripts.txt ./output_sorted.bus
# Location of count tables: data\counts\plateA\featurecounts

cd ..
```

### Run log {.tabset}

#### plateA

```{r run_log_DS113, eval=F}
# Print info on count generation run
PROT_log<- rjson::fromJSON(file = "data/counts/plateA/run_info.json")
PROT_log<- do.call(rbind, lapply(PROT_log, data.frame))
colnames (PROT_log) <- ""
PROT_log %>%
  kbl() %>%
  kable_styling()
```

### Output

Unfiltered counts are stored (for each sample) in data/counts/plate/featurecounts/ folder as .mtx format (sparse matrix). 
