---
title: "Paper supplementary figures"
author: "mwitmond"
date: "2024-03-11"
output:
  workflowr::wflow_html:
    toc: TRUE
    toc_float: 
      collapsed: FALSE
    toc_depth: 3
    code_folding: hide
editor_options:
  chunk_output_type: console
---

## Set-up

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = F, warning = F, echo = T, eval = T
)

# Load required packages
source("code/packages_seq.R", local = knitr::knit_global())
source("code/packages_FACS.R", local = knitr::knit_global())
```

```{r fig_settings}
row_order = c("A", "B", "C", "D", "E", "F", "G", "H")
col_order = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")
panel_labels <- c("a", "b", "c","d", "e", "f", "g", "h", "i", "j", "k", "l", "m")
PANEL_labels <- c("A", "B", "C","D", "E", "F", "G", "H", "I", "J", "K", "L", "M")

textsize <- theme(axis.text.x = element_text(colour = "grey", size = 11), #, face = "bold"
                  axis.text.y = element_text(colour = "grey", size = 11),
                  axis.title = element_text(colour = "black", size = 12), 
                  legend.title = element_text(colour = "black", size = 12),
                  # legend.title = element_blank(), 
                  legend.text = element_text(colour = "grey", size = 11), 
                  strip.text.x = element_text(colour = "black", size = 12)
)

textsize_small <- theme(text = element_text(size = 9, family = "sans", colour = "black"),
                        plot.title = element_text(size = 10)
)
# textsize_small <- theme(axis.text.x = element_text(colour = "black", size = 9),
#                         axis.text.y = element_text(colour = "black", size = 9),
#                         axis.title = element_text(colour = "black", size = 10),
#                         legend.text = element_text(colour = "black", size = 9),
#                         title = element_text(color = "black", size = 10),
#                         strip.text.x = element_text(colour = "black", size = 10, face = "bold"),
#                         strip.text.y = element_text(colour = "black", size = 10, face = "bold")
# )
```

```{r fig_colors}
colors_nord <- c("#2e3440", "#3b4252", "#434c5e", "#4c566a", 
                 "#d8dee9", "#e5e9f0", "#eceff4", 
                 "#8fbcbb", "#88c0d0", "#81a1c1", "#5e81ac", 
                 "#bf616a", "#d08770", "#ebcb8b", "#a3be8c", "#b48ead")

colors_toll_bright <- c("#4477AA", "#66CCEE", "#228833", "#CCBB44", "#EE6677", "#AA3377", "#BBBBBB")
colors_toll_mute <- c("#332288", "#88CCEE", "#44AA99", "#117733", "#999933", "#DDCC77", "#CC6677", "#882255", "#AA4499", "#DDDDDD")
colors_toll_br <- c("#364B9A", "#4A7BB7", "#6EA6CD", "#98CAE1", "#C2E4EF", "#EAECCC", "#FEDA8B", "#FDB366", "#F67A4B", "#DD3D2D", "#A50026")

colors_blue9 <- c("#f7fbff", "#deebf7", "#c6dbef", "#9ecae1", "#6baed6", "#4292c6", "#2171b5", "#08519c", "#08306b")
colors_green9 <- c("#f7fcf5", "#e5f5e0", "#c7e9c0", "#a1d99b", "#74c476", "#41ab5d", "#238b45", "#006d2c", "#00441b")
colors_purple9 <- c("#fcfbfd", "#efedf5", "#dadaeb", "#bcbddc", "#9e9ac8", "#807dba", "#6a51a3", "#54278f", "#3f007d")
colors_red9 <- c("#fff5f0", "#fee0d2", "#fcbba1", "#fc9272", "#fb6a4a", "#ef3b2c", "#cb181d", "#a50f15", "#67000d")
colors_orange9 <- c("#fff5eb", "#fee6ce", "#fdd0a2", "#fdae6b", "#fd8d3c", "#f16913", "#d94801", "#a63603", "#7f2704")
colors_grey9 <- c("#ffffff", "#f0f0f0", "#d9d9d9", "#bdbdbd", "#969696", "#737373", "#525252", "#252525", "#000000")
colors_yb9 <- c("#ffffd9", "#edf8b1", "#c7e9b4", "#7fcdbb", "#41b6c4", "#1d91c0", "#225ea8", "#253494", "#081d58")
colors_pr9 <- c("#f7f4f9", "#e7e1ef", "#d4b9da", "#c994c7", "#df65b0", "#e7298a", "#ce1256", "#980043", "#67001f")

# Variable-specific colors
colors_cell <- c("HBL1" = "#AA4499", "OCI-Ly8" = "#332288")
colors_stim <- c("PBS" = "#737373", "aIg+H2O2" = "#FDB366", 
                 "Basal" = "#737373", "Activated" = "#FDB366")
colors_cell_stim <- c("HBL1 - PBS" = "#c994c7", "HBL1 - aIg+H2O2" = "#AA4499", "OCI-Ly8 - PBS" = "#88CCEE", "OCI-Ly8 - aIg+H2O2" = "#332288")
# colors_inhib <- c("iSYK" = "#228833", "iBTK" = "#4477AA", "iNFkB" = "#AA3377")
colors_inhib <- c("iSYK" = "#9dce5c", "iBTK" = "#5c9dce", "iNFkB" = "#ce5c9d")
colors_conc <- c("#737373", "#dadaeb", "#9e9ac8", "#6a51a3", "#3f007d")
colors_iSYK <- colors_green9[c(3, 5, 6, 8, 9)]
colors_iBTK <- colors_blue9[c(3, 5, 6, 8, 9)]
colors_iNFkB <- colors_pr9[c(3, 5, 6, 8, 9)]
colors_conc_stim <- colors_orange9[c(2, 3, 5, 6, 8, 9)]
colors_conc_PBS <- colors_grey9[c(2, 3, 5, 6, 8, 9)]
```



## Suppl. figure S1

*Detailed schematic of the B-cell signaling network, with proteins measured in ID-seq panel indicated.*

Input:

-   Cytoscape blank network


### Panels {.tabset}

#### Panel A
```{r suppl_figS1_panelA, fig.retina=1}
# Placeholder
suppl_figS1_panelA <- ggplot() +
  geom_blank() +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 10)) + 
  # labs(title = "BCR signaling network") + 
  theme_bw() +
  theme(axis.text = element_text(color = "white"), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank()) +
  textsize_small
# suppl_figS1_panelA

# PNG
png_suppl_figS1 <- magick::image_read("output/figures/non_R_figs/BCR_network_organised.png") %>%
  magick::image_border(color = "black", geometry = "1x1") %>%
  magick::image_ggplot(interpolate = TRUE)
png_suppl_figS1

# Legend
png_suppl_figS1_legend <- magick::image_read("output/figures/non_R_figs/legend_network_projections_blank.png") %>%
  # magick::image_border(color = "black", geometry = "1x1") %>%
  magick::image_ggplot(interpolate = TRUE)
# png_suppl_figS1_legend
```


### Combined fig

```{r suppl_figS1_combi, fig.width=7.3, fig.height=8, fig.retina=1}
# Combine all panels of the figure
suppl_figS1 <- plot_grid(png_suppl_figS1, png_suppl_figS1_legend, ncol = 1, rel_heights = c(8, 1), label_size = 10)
suppl_figS1

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS1,
  filename = "output/figures/paper/suppl_figS1.pdf",
  width = 7.3,
  height = 8,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS1,
  filename = "output/figures/paper/suppl_figS1.jpg",
  width = 7.3,
  height = 8,
  units = "in",
  dpi = 300
  )
```
*Figure S1: Detailed schematic of the B-cell signaling network, with proteins measured in ID-seq panel indicated.*

```{r suppl_figS1_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS1"))
# rm(list = ls(pattern = "_fig1"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S2

*Increased activation upon treatment with both anti-Ig and H2O2 combined compared to treatment with anti-Ig or H2O2 alone.*

Input:

-   DS102 phosphoflow data


### Data

```{r suppl_figS2_data}
data_suppl_figS2 <- read_csv("output/DS102_StimTest/flow_ann/flow_data_DS102.csv")
medians_suppl_figS2 <- read_csv("output/DS102_StimTest/flow_ann/flow_medians_DS102.csv")
```

```{r suppl_figS2_labels}
proteins_suppl_figS2 <- c("pCD79a (Y182)", "pSYK (Y525/Y526)") # "pPLCy2 (Y759)"
stim_suppl_figS2 <- c("aIg", "H2O2", "H2O2 + aIg")
stim_labels_suppl_figS2 <- c("Anti-Ig", "H2O2", "Combination\nAnti-Ig + H2O2")
conc_suppl_figS2 <- c("PBS", 
                      "10 ug/mL aIg", "20 ug/mL aIg",
                      "10 mM H2O2", "20 mM H2O2", 
                      "15 H2O2 + 15 aIg")
conc_labels_suppl_figS2 <- c("PBS", 
                             "10 ug/mL\nanti-Ig", "20 ug/mL\nanti-Ig",
                             "10 mM\nH2O2", "20 mM\nH2O2",
                             "15 anti-Ig +\n15 H2O2")
colors_conc_suppl_figS2 <- c("PBS" = "#737373", 
                             "10 ug/mL aIg" = "#a1d99b", "20 ug/mL aIg" = "#74c476",
                             "10 mM H2O2" = "#98CAE1", "20 mM H2O2" = "#6EA6CD", 
                             "15 H2O2 + 15 aIg" = "#FDB366")
```


### Panels {.tabset}

#### Panel A
```{r suppl_figS2_panelA_alt, fig.retina=1, eval=F}
# Ridge test
# Data
data_suppl_figS2A <- data_suppl_figS2 %>%
  subset(cell_line == "HBL1" & protein %in% proteins_suppl_figS2 & conc_text %in% conc_suppl_figS2)

# Figure
suppl_figS2_panelA_alt <- ggplot(data_suppl_figS2A, aes(x = fluorescence)) +
  geom_density_ridges(
    aes(y = factor(conc_text, levels = rev(conc_suppl_figS2)), fill = factor(conc_text, levels = conc_suppl_figS2)),
    scale = 1.5,
    # fill = "#006699",
    alpha = 0.6
  ) +
  geom_vline(aes(xintercept = zero_quant97.5), linewidth = 0.5) +
  facet_wrap(vars(factor(protein, levels = proteins_suppl_figS2))) +
  scale_x_logicle() + # logicle scale instead of log10 scale
  scale_fill_manual(values = colors_conc_suppl_figS2, labels = conc_labels_suppl_figS2, name = "Stimulus") +
  labs(x = "Fluorescent intensity", y = "") +
  theme_bw() +
  # theme(legend.position = "none", panel.grid.minor = element_blank()) +
  textsize_small
suppl_figS2_panelA_alt
```

```{r suppl_figS2_panelA, fig.width=6, fig.height=3, fig.retina=1}
# Data
data_suppl_figS2A <- medians_suppl_figS2 %>%
  subset(cell_line == "HBL1" & protein == proteins_suppl_figS2[1] & conc_text %in% conc_suppl_figS2)
data_suppl_figS2A_stat <- data_suppl_figS2 %>%
  subset(cell_line == "HBL1" & protein %in% proteins_suppl_figS2[1] & conc_text %in% conc_suppl_figS2)

# Statistics
# Kruskal-Wallis test
figS2A_kruskal <- data_suppl_figS2A_stat %>%
  # group_by(target_nospace) %>%
  kruskal_test(fluorescence ~ conc_text)
figS2A_kruskal

# Post-hoc Dunn's test (without correction)
figS2A_dunn <- data_suppl_figS2A_stat %>%
  # group_by(target_nospace) %>%
  dunn_test(fluorescence ~ conc_text, p.adjust.method = "none") %>%
  dplyr::filter(
    (group1 == "15 H2O2 + 15 aIg") | (group2 == "15 H2O2 + 15 aIg")
      ) %>%
# group_by(target_nospace) %>%
  adjust_pvalue(method = "BH") %>%
  # add_xy_position(x = "conc_text", ref.group = "15 H2O2 + 15 aIg")
  mutate(xmin = c(4, 2, 6, 6, 6), 
         xmax = c(6, 6, 5, 3, 1), 
         plot_order = c(4, 2, 5, 3, 1)) %>%
  arrange(plot_order)
figS2A_dunn

# Figure
suppl_figS2_panelA <- ggplot(data_suppl_figS2A) +
  geom_col(aes(
    x = factor(conc_text, levels = conc_suppl_figS2, labels = conc_labels_suppl_figS2),
    y = fluorescence_median, 
    group = factor(conc_text, levels = conc_suppl_figS2),
    fill = factor(conc_text, levels = conc_suppl_figS2)),
    position = "dodge2") + 
  stat_pvalue_manual(figS2A_dunn, label = "p.adj.signif", tip.length = 0.01, 
                     y.position = 15150, step.increase = 0.05, size = 2.25) +
  facet_wrap(vars(factor(protein, levels = proteins_suppl_figS2)), scale = "free_y") +
  scale_fill_manual(values = colors_conc_suppl_figS2, labels = conc_labels_suppl_figS2, name = "Stimulus") +
  labs(x = "", y = "MFI") +
  theme_bw() +
  textsize_small +
  theme(legend.position = "none", panel.grid.minor = element_blank(), panel.grid.major.x = element_blank(), axis.text.x = element_text(size = 5)) #+
# suppl_figS2_panelA

# Figure alt
suppl_figS2_panelA_alt <- ggplot() +
  geom_jitter(data = data_suppl_figS2A_stat,
              aes(
                x = factor(conc_text, levels = conc_suppl_figS2, labels = conc_labels_suppl_figS2),
                y = fluorescence,
                group = factor(conc_text, levels = conc_suppl_figS2),
                color = factor(conc_text, levels = conc_suppl_figS2)),
              # position = "dodge2",
              width = 0.2, size = 0.2, alpha = 0.1
              ) +
  geom_errorbar(data = data_suppl_figS2A,
                aes(x = factor(conc_text, levels = conc_suppl_figS2, labels = conc_labels_suppl_figS2),
                    ymin = fluorescence_median, ymax = fluorescence_median,
                    group = factor(conc_text, levels = conc_suppl_figS2)),
                color = "black", width = 0.5, size = 0.5) +
  stat_pvalue_manual(figS2A_dunn, label = "p.adj.signif", tip.length = 0.01,
                     y.position = 7e4, step.increase = 0.05, size = 2.25) +
  coord_cartesian(ylim = c(0, 1e5)) +
  facet_wrap(vars(factor(protein, levels = proteins_suppl_figS2)), scale = "free_y") +
  # scale_y_log10() +
  scale_color_manual(values = colors_conc_suppl_figS2, labels = conc_labels_suppl_figS2, name = "Stimulus") +
  labs(x = "", y = "Fluorescent intensity (A.U.)") +
  theme_bw() +
  textsize_small +
  theme(legend.position = "none", panel.grid.minor = element_blank(), panel.grid.major.x = element_blank(), axis.text.x = element_text(size = 6))
suppl_figS2_panelA_alt
```

#### Panel B
```{r suppl_figS2_panelB, fig.width=6, fig.height=3, fig.retina=1}
# Data
data_suppl_figS2B <- medians_suppl_figS2 %>%
  subset(cell_line == "HBL1" & protein == proteins_suppl_figS2[2] & conc_text %in% conc_suppl_figS2)
data_suppl_figS2B_stat <- data_suppl_figS2 %>%
  subset(cell_line == "HBL1" & protein %in% proteins_suppl_figS2[2] & conc_text %in% conc_suppl_figS2)

# Statistics
# Kruskal-Wallis test
figS2B_kruskal <- data_suppl_figS2B_stat %>%
  # group_by(target_nospace) %>%
  kruskal_test(fluorescence ~ conc_text)
figS2B_kruskal

# Post-hoc Dunn's test (without correction)
figS2B_dunn <- data_suppl_figS2B_stat %>%
  # group_by(target_nospace) %>%
  dunn_test(fluorescence ~ conc_text, p.adjust.method = "none") %>%
  dplyr::filter(
    (group1 == "15 H2O2 + 15 aIg") | (group2 == "15 H2O2 + 15 aIg")
      ) %>%
# group_by(target_nospace) %>%
  adjust_pvalue(method = "BH") %>%
  # add_xy_position(x = "conc_text", ref.group = "15 H2O2 + 15 aIg")
  mutate(xmin = c(4, 2, 6, 6, 6), 
         xmax = c(6, 6, 5, 3, 1), 
         plot_order = c(4, 2, 5, 3, 1)) %>%
  arrange(plot_order)
figS2B_dunn

# Figure
suppl_figS2_panelB <- ggplot(data_suppl_figS2B) +
  geom_col(aes(
    x = factor(conc_text, levels = conc_suppl_figS2, labels = conc_labels_suppl_figS2),
    y = fluorescence_median, 
    group = factor(conc_text, levels = conc_suppl_figS2),
    fill = factor(conc_text, levels = conc_suppl_figS2)),
    position = "dodge2") + 
  stat_pvalue_manual(figS2B_dunn, label = "p.adj.signif", tip.length = 0.01,
                     y.position = 42000, step.increase = 0.05, size = 2.25) +
  facet_wrap(vars(factor(protein, levels = proteins_suppl_figS2))) +
  scale_fill_manual(values = colors_conc_suppl_figS2, labels = conc_labels_suppl_figS2, name = "Stimulus") +
  labs(x = "", y = "MFI") +
  theme_bw() +
  textsize_small +
  theme(legend.position = "right", panel.grid.minor = element_blank(), panel.grid.major.x = element_blank(), axis.text.x = element_text(size = 5)) #+
# suppl_figS2_panelB

# Figure alt
suppl_figS2_panelB_alt <- ggplot() +
  geom_jitter(data = data_suppl_figS2B_stat,
              aes(
                x = factor(conc_text, levels = conc_suppl_figS2, labels = conc_labels_suppl_figS2),
                y = fluorescence,
                group = factor(conc_text, levels = conc_suppl_figS2),
                color = factor(conc_text, levels = conc_suppl_figS2)),
              # position = "dodge2",
              width = 0.2, size = 0.2, alpha = 0.1
              ) +
  geom_errorbar(data = data_suppl_figS2B,
                aes(x = factor(conc_text, levels = conc_suppl_figS2, labels = conc_labels_suppl_figS2),
                    ymin = fluorescence_median, ymax = fluorescence_median,
                    group = factor(conc_text, levels = conc_suppl_figS2)),
                color = "black", width = 0.5, size = 0.5) +
  stat_pvalue_manual(figS2B_dunn, label = "p.adj.signif", tip.length = 0.01,
                     y.position = 2.5e5, step.increase = 0.05, size = 2.25) +
  coord_cartesian(ylim = c(0, 3.1e5)) +
  facet_wrap(vars(factor(protein, levels = proteins_suppl_figS2)), scale = "free_y") +
  # scale_y_log10() +
  scale_color_manual(values = colors_conc_suppl_figS2, labels = conc_labels_suppl_figS2, name = "Stimulus") +
  labs(x = "", y = "Fluorescent intensity (A.U.)") +
  theme_bw() +
  textsize_small +
  theme(legend.position = "none", panel.grid.minor = element_blank(), panel.grid.major.x = element_blank(), axis.text.x = element_text(size = 6))
suppl_figS2_panelB_alt
```


### Combined fig

```{r suppl_figS2_combi, fig.width=6.125, fig.height=3, fig.retina=1}
# Combine all panels of the figure
suppl_figS2 <- plot_grid(suppl_figS2_panelA_alt, suppl_figS2_panelB_alt, labels = PANEL_labels[c(1, 2)], ncol = 2, rel_widths = c(1, 1), label_size = 10)
suppl_figS2

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS2,
  filename = "output/figures/paper/suppl_figS2.pdf",
  width = 6.125,
  height = 3,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS2,
  filename = "output/figures/paper/suppl_figS2.jpg",
  width = 6.125,
  height = 3,
  units = "in",
  dpi = 300
  )
```
*Figure S2: Increased activation upon treatment with both anti-Ig and H2O2 combined compared to treatment with anti-Ig or H2O2 alone.*

```{r suppl_figS2_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS2"))
# rm(list = ls(pattern = "_fig1"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S3

*Schematic overview of the experimental workflow of ID-seq.*

Input:

-   BioRender schematic figure


### Panels {.tabset}

#### Panel A
```{r suppl_figS3_panelA, fig.retina=1}
# Placeholder
suppl_figS3_panelA <- ggplot() +
  geom_blank() +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 10)) + 
  labs(title = "ID-seq workflow") +
  theme_bw() +
  theme(axis.text = element_text(color = "white"), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank()) +
  textsize_small
# suppl_figS3_panelA

# PNG
png_suppl_figS3 <- magick::image_read("output/figures/non_R_figs/bulkIDseq_workflow_detailed.png") %>%
  magick::image_ggplot()
png_suppl_figS3
```


### Combined fig

```{r suppl_figS3_combi, fig.width=7.3, fig.height=3.5, fig.retina=1}
# Combine all panels of the figure
png_suppl_figS3

# Save figure as pdf, jpg, and png
# ggsave(
#   suppl_figS3_panelA,
#   filename = "output/figures/paper/suppl_figS3_place.pdf",
#   width = 7.3,
#   height = 3.5,
#   units = "in",
#   dpi = 300
#   )
ggsave(
  suppl_figS3_panelA,
  filename = "output/figures/paper/suppl_figS3_place.jpg",
  width = 7.3,
  height = 3.5,
  units = "in",
  dpi = 300
  )
```
*Figure S3: Schematic overview of the experimental workflow of ID-seq.*

```{r suppl_figS3_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS3"))
# rm(list = ls(pattern = "_fig1"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S4

*Phospho-specific flow cytometry measurements of CD79a (Y182) shows high concordance with ID-seq results.*

Input:

-   DS108 phosphoflow data

-   DS108 ID-seq data

    -   Count data

### Data

```{r suppl_figS4_data}
# Phospshoflow data 
data_flow_suppl_figS4 <- read_csv("output/DS108_StimInhibIDseq/flow_ann/flow_data_DS108.csv") %>%
  subset(cell_line == "HBL1")

# ID-seq data (counts per well/sample and mean per condition)
data_IDsample_suppl_figS4 <- read_csv("output/DS108_StimInhibIDseq/IDseq_ann/IDseq_data_sample.csv") %>%
  subset(inhibitor != "iPI3Kd" & target_nospace != "BIM" & target_nospace != "Histone_H2AX_S139" & cell_line == "HBL1") %>%
  mutate(stim_clean = case_when(stimulus == "PBS" ~ "Basal", 
                                stimulus == "aIg+H2O2" ~ "Activated"),
         inhib_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                               inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                               .default = inhibitor), 
         inhib_text_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                                    inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                                    .default = inhib_conc_text), 
         stim_inhib = paste0(stim_clean, "\n", inhib_text_new)) #%>%
  # subset(inhib_new != "PBS ctrl")
data_IDmean_suppl_figS4 <- read_csv("output/DS108_StimInhibIDseq/IDseq_ann/IDseq_data_condition.csv") %>%
  subset(inhibitor != "iPI3Kd" & target_nospace != "BIM" & target_nospace != "Histone_H2AX_S139" & cell_line == "HBL1") %>%
  mutate(stim_clean = case_when(stimulus == "PBS" ~ "Basal", 
                                stimulus == "aIg+H2O2" ~ "Activated"),
         inhib_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                               inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                               .default = inhibitor), 
         inhib_text_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                                    inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                                    .default = inhib_conc_text), 
         stim_inhib = paste0(stim_clean, "\n", inhib_text_new)) #%>%
  # subset(inhib_new != "PBS ctrl")
```

```{r suppl_figS4_labels}
stim_suppl_figS4 <- c("PBS", "aIg+H2O2")
stim_label_suppl_figS4 <- c("Basal", "Activated")
inhib_suppl_figS4 <- c("iBTK", "iSYK", "iNFkB")

conc_flow_suppl_figS4 <- c("0 uM", "100 uM")
conc_ID_suppl_figS4 <- c("0 uM (DMSO)", "100 uM")
conc_label_suppl_figS4 <- c("DMSO ctrl", "100 uM")

protein_flow_suppl_figS4 <- "pCD79a (Y182)"
protein_ID_suppl_figS4 <- "CD79a_Y182"
```


### Panels {.tabset}

#### Panel A
```{r suppl_figS4_panelA, fig.width=6, fig.height=3, fig.retina=1}
# Select data
data_flow_suppl_figS4A <- data_flow_suppl_figS4 %>%
  subset(protein == protein_flow_suppl_figS4 & inhib_conc %in% conc_flow_suppl_figS4 & inhibitor %in% inhib_suppl_figS4)

# Figure
suppl_figS4_panelA <- ggplot(data_flow_suppl_figS4A, aes(x = fluorescence)) +
  geom_density_ridges(
    aes(y = factor(inhib_conc, levels = rev(conc_flow_suppl_figS4), labels = rev(conc_label_suppl_figS4)), fill = factor(stimulus, levels = stim_suppl_figS4)),
    scale = 1, 
    alpha = 0.5
  ) +
  facet_wrap(vars(factor(inhibitor, levels = inhib_suppl_figS4)), nrow = 1) +
  scale_x_logicle() + # logicle scale instead of log10 scale
  scale_fill_manual(values = colors_stim, labels = stim_label_suppl_figS4, name = "Stimulus") +
  labs(x = "Fluorescent intensity (A.U.)", y = "") +
  theme_bw() +
  # theme(legend.position = "right", panel.grid.minor = element_blank()) +
  theme(panel.grid.minor = element_blank(), legend.key.size = unit(0.5, "cm"), legend.spacing.y = unit(0.2, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "right", legend.justification = "right") +
  textsize_small
suppl_figS4_panelA
```

#### Panel B
```{r suppl_figS4_panelB, fig.width=6, fig.height=3, fig.retina=1}
# Select data
data_IDsample_suppl_figS4B <- data_IDsample_suppl_figS4 %>%
  subset(target_nospace == protein_ID_suppl_figS4 & inhib_conc %in% conc_ID_suppl_figS4)
data_IDmean_suppl_figS4B <- data_IDmean_suppl_figS4 %>%
  subset(target_nospace == protein_ID_suppl_figS4 & inhib_conc %in% conc_ID_suppl_figS4) # & inhibitor %in% inhib_suppl_figS4

# Statistics
# Kruskal-Wallis test
figS4B_kruskal <- data_IDsample_suppl_figS4B %>%
  group_by(inhibitor) %>%
  kruskal_test(counts_norm ~ stim_inhib)
figS4B_kruskal

# Post-hoc Dunn's test (without correction)
figS4B_dunn <- data_IDsample_suppl_figS4B %>%
  group_by(inhibitor) %>%
  dunn_test(counts_norm ~ stim_inhib, p.adjust.method = "none") %>%
  dplyr::filter(
      (group1 == "Activated\n100 uM iBTK" & group2 == "Activated\nDMSO ctrl") | 
      (group1 == "Activated\n100 uM iSYK" & group2 == "Activated\nDMSO ctrl") |  
      (group1 == "Activated\n100 uM iNFkB" & group2 == "Activated\nDMSO ctrl")
      ) %>%
  group_by(inhibitor) %>%
  adjust_pvalue(method = "BH") %>%
  # add_xy_position(x = "conc_text", ref.group = "15 H2O2 + 15 aIg")
  mutate(xmin = c(2, 2, 2), 
         xmax = c(1, 1, 1), 
         plot_order = c(1, 3, 2)) %>%
  arrange(plot_order)
figS4B_dunn

# Figure
suppl_figS4_panelB <- ggplot() +
  geom_jitter(data = data_IDsample_suppl_figS4B, 
              aes(x = factor(inhib_conc, levels = conc_ID_suppl_figS4, labels = conc_label_suppl_figS4), 
                  y = counts_norm, 
                  color = factor(stimulus, levels = stim_suppl_figS4)), 
              alpha = 1, size = 1, width = 0.1) +
  geom_errorbar(data = data_IDmean_suppl_figS4B,
                aes(x = factor(inhib_conc, levels = conc_ID_suppl_figS4, labels = conc_label_suppl_figS4), 
                    ymin = counts_norm, ymax = counts_norm,
                    group = factor(stimulus, levels = stim_suppl_figS4),
                    color = factor(stimulus, levels = stim_suppl_figS4)),
                width = 0.35, size = 0.75) +
  # stat_pvalue_manual(figS4B_dunn, label = "p.adj", tip.length = 0.01,
  #                    y.position = 800, step.increase = 0, size = 2.25) +
  facet_wrap(vars(factor(inhibitor, levels = inhib_suppl_figS4)), nrow = 1) +
  scale_color_manual(values = colors_stim, labels = stim_label_suppl_figS4, name = "Stimulus") +
  labs(x = element_blank(), y = "Normalized counts") +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.5, "cm"), legend.spacing.y = unit(0.2, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "right", legend.justification = "right") +
  textsize_small
suppl_figS4_panelB
```


### Combined fig

```{r suppl_figS4_combi, fig.width=5, fig.height=3.25, fig.retina=1}
# Combine all panels of the figure
suppl_figS4 <- plot_grid(suppl_figS4_panelA, suppl_figS4_panelB, labels = PANEL_labels[c(1, 2)], ncol = 1, rel_heights = c(1, 1), label_size = 10, align = "v")
suppl_figS4

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS4,
  filename = "output/figures/paper/suppl_figS4.pdf",
  width = 5,
  height = 3.25,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS4,
  filename = "output/figures/paper/suppl_figS4.jpg",
  width = 5,
  height = 3.25,
  units = "in",
  dpi = 300
  )
```
*Figure S4: Phospho-specific flow cytometry measurements of CD79a (Y182) shows high concordance with ID-seq results.*

```{r suppl_figS4_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS4"))
# rm(list = ls(pattern = "_fig1"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S5

*DMSO has no effect on signaling activation.*

Input:

- DS108 ID-seq data

    -   DESeq2 analysis of PBS and DMSO controls

### Data

```{r suppl_figS5_data}
# ID-seq data DS108 (counts per well/sample and mean per condition)
data_ID_suppl_figS5 <- read_csv("output/DS108_StimInhibIDseq/IDseq_ann/IDseq_data_sample.csv") %>%
  subset(inhibitor != "iPI3Kd" & target_nospace != "BIM" & target_nospace != "Histone_H2AX_S139" & cell_line == "HBL1") %>%
  mutate(stim_clean = case_when(stimulus == "PBS" ~ "Basal", 
                                stimulus == "aIg+H2O2" ~ "Activated"),
         inhib_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                               inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                               .default = inhibitor), 
         inhib_text_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                                    inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                                    .default = inhib_conc_text), 
         stim_inhib = paste0(stim_clean, "\n", inhib_text_new)) #%>%
  # subset(inhib_new != "PBS ctrl")
```

```{r suppl_figS5_labels}
stim_suppl_figS5 <- c("PBS", "aIg+H2O2")
stim_label_suppl_figS5 <- c("Basal", "Activated")
# inhib_suppl_figS5 <- c("iBTK", "iSYK", "iNFkB")
conc_suppl_figS5 <- c("0 uM (PBS)", "0 uM (DMSO)")
conc_label_suppl_figS5 <- c("PBS ctrl", "DMSO ctrl")

meta_cols_suppl_figS5 <- c("plate_well", "plate", "well", "experiment", "cell_line", "stimulus", "stim_clean", "inhibitor", "inhib_conc_uM", "inhib_conc", "inhib_conc_text", "inhib_text_new", "stim_inhib", "replicate", "description", "descript_rep")
```


Differential expression analysis of the effect of DMSO vs PBS on the stimulation in HBL1

DESeq2 analysis parameters:

-   HBL1: PBS + DMSO ctrls 2 stimuli

-   Compensated counts (>= 1)

-   Model design: inhib_text_new (ref: PBS ctrl) + stimulus (ref: PBS) + inhib_text_new:stimulus

```{r suppl_figS5_DESeq}
# Differential expression analysis
# Prepare data to load into DESeq dataset
# cts: dataframe with proteins as row names, wells as column names, and count data as cell values
# coldata: dataframe with wells as row names and all metadata as columns
cts <- data_ID_suppl_figS5  %>%
  dplyr::filter(cell_line == "HBL1" & inhib_conc %in% conc_suppl_figS5 & counts >= 1) %>%
  dplyr::select(target_nospace, plate_well, counts) %>%
  dplyr::filter(!is.na(counts)) %>%
  spread(plate_well, counts) %>%
  replace(is.na(.), 0) %>%
  column_to_rownames("target_nospace")

cts <- as.matrix(as.data.frame(cts))

coldata <- data.frame(plate_well = colnames(cts)) %>%
  left_join(distinct(dplyr::select(data_ID_suppl_figS5, all_of(meta_cols_suppl_figS5)))) %>%
  distinct()

rownames(coldata) <- coldata$plate_well

# Create DESeq object
# First define how the model is designed. Place most important parameter last
modeldesign <- ~ inhib_text_new + stim_clean + inhib_text_new:stim_clean

# Then create the DESeq dataset
dds <- DESeqDataSetFromMatrix(countData = cts,
                              colData = coldata,
                              design = modeldesign)
# Define the reference samples for design parameter
dds$inhib_text_new <- relevel(dds$inhib_text_new, ref = "PBS ctrl")
dds$stim_clean <- relevel(dds$stim_clean, ref = "Basal")

# Run DESeq2: 
  # This function performs a default analysis through the steps:
  # Estimation of size factors: estimateSizeFactors
  # Estimation of dispersion: estimateDispersions
  # Negative Binomial GLM fitting and Wald statistics: nbinomWaldTest

dds <- DESeq(dds, test = "Wald", fitType = "local")
DESeq_comparisons <- resultsNames(dds) # lists the coefficients
# DESeq_comparisons

# Results
results_stim <- results(dds, name = "stim_clean_Activated_vs_Basal", alpha = 0.05)
results_DMSO <- results(dds, name = "inhib_text_new_DMSO.ctrl_vs_PBS.ctrl", alpha = 0.05)
results_DMSO_stim <- results(dds, name = "inhib_text_newDMSO.ctrl.stim_cleanActivated", alpha = 0.05)

list_results <- list(results_stim, results_DMSO, results_DMSO_stim)

# Data transformation
# Regularized log transform
rld <- rlog(dds, blind = FALSE)

# Data wrangling
# Function to prepare DESeq2 results for volcano plots
# Standard log2FC filter = log2(1.5); standard padj filter = 0.05
prep_forvulcano <- function(dataset = dataset, padj_filter = 0.05, foldchange_filter = log2(1.5)){ 
  dataset$proteins <- rownames(dataset)
  dataset$target_nospace <- rownames(dataset)
  
  # Add a column for differential expression
  dataset$diff_express <- "NO"
  dataset$diff_express[dataset$log2FoldChange > foldchange_filter & dataset$padj < padj_filter] <- "UP"
  dataset$diff_express[dataset$log2FoldChange < -foldchange_filter & dataset$padj < padj_filter] <- "DOWN"
  
  # Add a column for labeling
  dataset$delabel <- NA
  dataset$delabel[dataset$diff_express != "NO"] <- dataset$proteins[dataset$diff_express != "NO"]
  
  # Add Ab metadata
  # dataset <- left_join(as.data.frame(dataset), meta_Abs)
  
  return(as.data.frame(dataset))
}

# Apply function to each dataset
# padj < 0.05
# log2FC > log2(1.05)
names_results_volc <- c("volc_stim", "volc_DMSO", "volc_DMSO_stim")
for(dataset in c(1:length(list_results))){
  assign(names_results_volc[dataset], prep_forvulcano(dataset = list_results[[dataset]], foldchange_filter = log2(1.1)))
}

# Add column with comparison for faceting
comp_suppl_figS5 <- c("Activated vs basal", "DMSO vs PBS", "Effect DMSO on activation")
volc_stim$comparison <- comp_suppl_figS5[1]
volc_DMSO$comparison <- comp_suppl_figS5[2]
volc_DMSO_stim$comparison <- comp_suppl_figS5[3]
dataset_suppl_figS5 <- list(volc_stim, volc_DMSO, volc_DMSO_stim) %>%
  purrr::reduce(full_join)
```

### Panels {.tabset}

#### Panel A
```{r suppl_figS5_panelA, fig.width=6, fig.height=3, fig.retina=1}
# Select data
dataset_suppl_figS5A <- dataset_suppl_figS5 %>%
  subset(comparison == "Activated vs basal")

# Figure
suppl_figS5_panelA <- ggplot(data = dataset_suppl_figS5A,
                      aes(x = log2FoldChange, y = -log10(padj), color = diff_express, label = delabel)) +
  geom_point(size = 0.5) +
  geom_text_repel(size = 1.5,
                  segment.size = 0.2,
                  hjust = 0,
                  direction = "y",
                  nudge_y = -log10(0.005),
                  nudge_x = ifelse(dataset_suppl_figS5A$log2FoldChange < 0, -0.4 - dataset_suppl_figS5A$log2FoldChange, 0.4 - dataset_suppl_figS5A$log2FoldChange)
  ) +
  facet_wrap(~comparison, nrow = 1) +
  scale_color_manual(values = c(UP = "#A50026", NO = "black", DOWN = "#364B9A"),
                     breaks = c("UP", "NO", "DOWN"),
                     labels = c("Increased", "No difference", "Decreased"),
                     name = "Differentially\nexpressed\nproteins") + 
  geom_vline(xintercept = c(-log2(1.1), log2(1.1)), color = "#CC6677") +
  geom_hline(yintercept = -log10(0.05), color = "#CC6677") +
  labs(x = "log2(fold change)", y = "-log10(adjusted p-value)", title = "") +
  coord_cartesian(xlim = c(-0.25, 1), ylim = c(0, 275)) +
  theme_bw() +
  theme(legend.key.size = unit(0.2, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "bottom", legend.justification = "left") + #legend.position = "none"
  guides(color = guide_legend(ncol = 1, byrow = TRUE)) +
  textsize_small
suppl_figS5_panelA
```

#### Panel B
```{r suppl_figS5_panelB, fig.width=6, fig.height=3, fig.retina=1}
# Select data
dataset_suppl_figS5B <- dataset_suppl_figS5 %>%
  subset(comparison == "DMSO vs PBS")

# Figure
suppl_figS5_panelB <- ggplot(data = dataset_suppl_figS5B,
                      aes(x = log2FoldChange, y = -log10(padj), color = diff_express, label = delabel)) +
  geom_point(size = 0.5) +
  geom_text_repel(size = 1.5,
                  segment.size = 0.2,
                  hjust = 0,
                  direction = "y",
                  nudge_y = -log10(0.005),
                  nudge_x = ifelse(dataset_suppl_figS5B$log2FoldChange < 0, -0.4 - dataset_suppl_figS5B$log2FoldChange, 0.4 - dataset_suppl_figS5B$log2FoldChange)
  ) +
  facet_wrap(~comparison, nrow = 1) +
  scale_color_manual(values = c(UP = "#A50026", NO = "black", DOWN = "#364B9A"),
                     breaks = c("UP", "NO", "DOWN"),
                     labels = c("Increased", "No difference", "Decreased"),
                     name = "Differentially\nexpressed\nproteins") + 
  geom_vline(xintercept = c(-log2(1.1), log2(1.1)), color = "#CC6677") +
  geom_hline(yintercept = -log10(0.05), color = "#CC6677") +
  labs(x = "log2(fold change)", y = "-log10(adjusted p-value)", title = "") +
  coord_cartesian(xlim = c(-0.25, 1), ylim = c(0, 275)) +
  theme_bw() +
  theme(legend.key.size = unit(0.2, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "none", legend.justification = "left") + #legend.position = "none"
  # guides(color = guide_legend(nrow = 3, byrow = TRUE)) +
  textsize_small
suppl_figS5_panelB
```

#### Panel C
```{r suppl_figS5_panelC, fig.width=6, fig.height=3, fig.retina=1}
# Select data
dataset_suppl_figS5C <- dataset_suppl_figS5 %>%
  subset(comparison == "Effect DMSO on activation")

# Figure
suppl_figS5_panelC <- ggplot(data = dataset_suppl_figS5C,
                      aes(x = log2FoldChange, y = -log10(padj), color = diff_express, label = delabel)) +
  geom_point(size = 0.5) +
  geom_text_repel(size = 1.5,
                  segment.size = 0.2,
                  hjust = 0,
                  direction = "y",
                  nudge_y = -log10(0.005),
                  nudge_x = ifelse(dataset_suppl_figS5C$log2FoldChange < 0, -0.4 - dataset_suppl_figS5C$log2FoldChange, 0.4 - dataset_suppl_figS5C$log2FoldChange)
  ) +
  facet_wrap(~comparison, nrow = 1) +
  scale_color_manual(values = c(UP = "#A50026", NO = "black", DOWN = "#364B9A"),
                     breaks = c("UP", "NO", "DOWN"),
                     labels = c("Increased", "No difference", "Decreased"),
                     name = "Differentially\nexpressed\nproteins") + 
  geom_vline(xintercept = c(-log2(1.1), log2(1.1)), color = "#CC6677") +
  geom_hline(yintercept = -log10(0.05), color = "#CC6677") +
  labs(x = "log2(fold change)", y = "-log10(adjusted p-value)", title = "") +
  coord_cartesian(xlim = c(-0.25, 1), ylim = c(0, 275)) +
  theme_bw() +
  theme(legend.key.size = unit(0.2, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "none", legend.justification = "left") + #legend.position = "none"
  # guides(color = guide_legend(nrow = 3, byrow = TRUE)) +
  textsize_small
suppl_figS5_panelC
```


### Combined fig

```{r suppl_figS5_combi, fig.width=7.3, fig.height=3.2, fig.retina=1}
# Combine all panels of the figure
suppl_figS5 <- plot_grid(suppl_figS5_panelA, suppl_figS5_panelB, suppl_figS5_panelC, labels = PANEL_labels[c(1, 2, 3)], nrow = 1, rel_widths = c(1, 1, 1), label_size = 10, align = "h")
suppl_figS5

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS5,
  filename = "output/figures/paper/suppl_figS5.pdf",
  width = 7.3,
  height = 3.25,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS5,
  filename = "output/figures/paper/suppl_figS5.jpg",
  width = 7.3,
  height = 3.25,
  units = "in",
  dpi = 300
  )
```

```{r suppl_figS5_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS5"))
# rm(list = ls(pattern = "_fig1"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S6

*Complete PCA signaling state space of the inhibitor concentration experiment.*

Input:
-   DS108 ID-seq data

    -   PCA on all samples

### Data

```{r suppl_figS6_data}
# ID-seq data (counts per well/sample and mean per condition)
data_ID_suppl_figS6 <- read_csv("output/DS108_StimInhibIDseq/IDseq_ann/IDseq_data_sample.csv") %>%
  subset(inhibitor != "iPI3Kd" & target_nospace != "BIM" & target_nospace != "Histone_H2AX_S139" & cell_line == "HBL1") %>%
  mutate(stim_clean = case_when(stimulus == "PBS" ~ "Basal", 
                                stimulus == "aIg+H2O2" ~ "Activated"),
         inhib_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                               inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                               .default = inhibitor), 
         inhib_text_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                                    inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                                    .default = inhib_conc_text), 
         stim_inhib = paste0(stim_clean, "\n", inhib_text_new)) #%>%
  # subset(inhib_new != "PBS ctrl")
```

```{r suppl_figS6_labels}
stim_suppl_figS6 <- c("PBS", "aIg+H2O2")
stim_label_suppl_figS6 <- c("Basal", "Activated")
inhib_suppl_figS6 <- c("iBTK", "iSYK", "iNFkB")

conc_suppl_figS6 <- c("0 uM (DMSO)", "0.1 uM", "1 uM", "10 uM", "100 uM")
conc_label__suppl_figS6 <- c("0 uM", "0.1 uM", "1 uM", "10 uM", "100 uM")

meta_cols_suppl_figS6 <- c("plate_well", "plate", "well", "experiment", "cell_line", "stimulus", "stim_clean", "inhibitor", "inhib_conc_uM", "inhib_conc", "inhib_conc_text", "inhib_text_new", "stim_inhib", "replicate", "description", "descript_rep")
```


### Panels {.tabset}

#### Panel A

PCA of all samples (PCA performed on all samples, all samples plotted).
```{r suppl_figS6_PCA}
# Prepare data for FactoMineR package
# cts_pca: dataframe with wells as row names, proteins as column names, and count data as cell values
# coldata: dataframe with wells as row names and all metadata as columns
cts_pca <- data_ID_suppl_figS6  %>%
  dplyr::filter(counts_norm >= 1) %>%
  dplyr::select(target_nospace, plate_well, counts_norm) %>%
  dplyr::filter(!is.na(counts_norm)) %>%
  spread(target_nospace, counts_norm) %>%
  replace(is.na(.), 0) %>% 
  column_to_rownames("plate_well")

# cts_pca <- scale(cts_pca)

coldata <- data.frame(plate_well = rownames(cts_pca)) %>%
  left_join(distinct(dplyr::select(data_ID_suppl_figS6, all_of(meta_cols_suppl_figS6)))) %>%
  mutate(stimulus = factor(stimulus, levels = stim_suppl_figS6), 
         inhibitor = factor(inhibitor, levels = inhib_suppl_figS6), 
         inhib_conc = factor(inhib_conc, levels = conc_suppl_figS6)) #If necessary, make factors of some metadata columns

rownames(coldata) <- coldata$plate_well

# Results
pca_results <- PCA(cts_pca, scale.unit = FALSE, ncp = 5, graph = FALSE)

pca_expl_var <- as.data.frame(get_eigenvalue(pca_results)) %>% # Percentage variance explained by each PC
  rownames_to_column("PC") %>%
  pull(var = variance.percent, name = PC) %>%
  round(digits = 1)

pca_variab <- get_pca_var(pca_results) # Results focused on variables (proteins)
pca_indiv <- get_pca_ind(pca_results) # Results focused on individuals (wells)

pca_data <- as.data.frame(pca_indiv$coord[, 1:3]) %>%
  rownames_to_column("plate_well") %>%
  dplyr::rename(PC1 = Dim.1, PC2 = Dim.2, PC3 = Dim.3) %>% 
  left_join(coldata)
```

```{r suppl_figS6_panelA, fig.width=6, fig.height=3, fig.retina=1}
# Data
pca_legend_levels <- c("Basal\nPBS ctrl", "Basal\nDMSO ctrl", 
                       "Basal\n0.1 uM iBTK", "Basal\n1 uM iBTK", "Basal\n10 uM iBTK", "Basal\n100 uM iBTK", 
                       "Basal\n0.1 uM iSYK", "Basal\n1 uM iSYK", "Basal\n10 uM iSYK", "Basal\n100 uM iSYK", 
                       "Basal\n0.1 uM iNFkB", "Basal\n1 uM iNFkB", "Basal\n10 uM iNFkB", "Basal\n100 uM iNFkB", 
                       "Activated\nPBS ctrl", "Activated\nDMSO ctrl", 
                       "Activated\n0.1 uM iBTK", "Activated\n1 uM iBTK", "Activated\n10 uM iBTK", "Activated\n100 uM iBTK", 
                       "Activated\n0.1 uM iSYK", "Activated\n1 uM iSYK", "Activated\n10 uM iSYK", "Activated\n100 uM iSYK", 
                       "Activated\n0.1 uM iNFkB", "Activated\n1 uM iNFkB", "Activated\n10 uM iNFkB", "Activated\n100 uM iNFkB")
pca_legend_shapes <- c(16, 16, 
                       16, 16, 16, 16, 
                       16, 16, 16, 16, 
                       16, 16, 16, 16, 
                       17, 17,
                       17, 17, 17, 17, 
                       17, 17, 17, 17,  
                       17, 17, 17, 17)
pca_legend_values <- c("#d9d9d9", "#bdbdbd", 
                       "#cfd9e0", "#bcc9d4",  "#a0b3c2", "#90a1ae", 
                       "#d9e0cf", "#c9d4bc",  "#b3c2a0", "#a1ae90", 
                       "#e0cfd9", "#d4bcc9",  "#c2a0b3", "#ae90a1", 
                       "#969696", "#737373", 
                       "#bdd7eb", "#9dc4e1",  "#7cb0d7", "#5c9dce", 
                       "#d7ebbd", "#c4e19d",  "#b0d77c", "#9dce5c", 
                       "#ebbdd7", "#e19dc4",  "#d77cb0", "#ce5c9d")
names(pca_legend_shapes) <- pca_legend_levels
names(pca_legend_values) <- pca_legend_levels

# Figure
suppl_figS6_panelA <- ggplot(pca_data) + 
  geom_point(aes(x = PC1, y = PC3, 
                 shape = stim_inhib, color = stim_inhib), 
             size = 2.5) +
  scale_color_manual(values = pca_legend_values,
                     breaks = pca_legend_levels,
                     name = "Treatment") +
  scale_shape_manual(values = pca_legend_shapes,
                     breaks = pca_legend_levels,
                     name = "Treatment") +
  xlab(paste0("PC1: ", pca_expl_var[1], "% variance")) +
  ylab(paste0("PC3: ", pca_expl_var[3], "% variance")) + 
  theme_bw() +
  theme(panel.grid.minor = element_blank(), legend.key.size = unit(0.65, "cm"), legend.spacing.y = unit(0.5, "cm"), legend.box.spacing = unit(0.2, "cm"), legend.position = "right", legend.justification = "left", legend.text = element_text(size = 6.5)) +
  textsize_small
suppl_figS6_panelA
```


### Combined fig

```{r suppl_figS6_combi, fig.width=6.125, fig.height=4.4, fig.retina=1}
# Combine all panels of the figure
suppl_figS6_panelA

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS6_panelA,
  filename = "output/figures/paper/suppl_figS6.pdf",
 width = 6.125,
  height = 4.5,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS6_panelA,
  filename = "output/figures/paper/suppl_figS6.jpg",
  width = 6.125,
  height = 4.5,
  units = "in",
  dpi = 300
  )
```
*Figure S6: Complete PCA signaling state space of the inhibitor concentration experiment.*

```{r suppl_figS6_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "suppl_figS6"))
rm(list = ls(pattern = "pca"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S7

*Principal components PC1-3 visualized for DMSO controls (basal and activated) and 100 uM iBTK treatment.*

Input:
-   DS108 ID-seq data

    -   PCA on all samples

### Data
```{r suppl_figS7_data}
# ID-seq data (counts per well/sample and mean per condition)
data_ID_suppl_figS7 <- read_csv("output/DS108_StimInhibIDseq/IDseq_ann/IDseq_data_sample.csv") %>%
  subset(inhibitor != "iPI3Kd" & target_nospace != "BIM" & target_nospace != "Histone_H2AX_S139" & cell_line == "HBL1") %>%
  mutate(stim_clean = case_when(stimulus == "PBS" ~ "Basal", 
                                stimulus == "aIg+H2O2" ~ "Activated"),
         inhib_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                               inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                               .default = inhibitor), 
         inhib_text_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                                    inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                                    .default = inhib_conc_text), 
         stim_inhib = paste0(stim_clean, "\n", inhib_text_new)) #%>%
  # subset(inhib_new != "PBS ctrl")
```

```{r suppl_figS7_labels}
stim_suppl_figS7 <- c("PBS", "aIg+H2O2")
stim_label_suppl_figS7 <- c("Basal", "Activated")
inhib_suppl_figS7 <- c("iBTK", "iSYK", "iNFkB")

conc_suppl_figS7 <- c("0 uM (DMSO)", "0.1 uM", "1 uM", "10 uM", "100 uM")
conc_label__suppl_figS7 <- c("0 uM", "0.1 uM", "1 uM", "10 uM", "100 uM")
conc_select_suppl_figS7 <- c("0 uM (DMSO)", "100 uM")

meta_cols_suppl_figS7 <- c("plate_well", "plate", "well", "experiment", "cell_line", "stimulus", "stim_clean", "inhibitor", "inhib_conc_uM", "inhib_conc", "inhib_conc_text", "inhib_text_new", "stim_inhib", "replicate", "description", "descript_rep")

conditions_suppl_figS7 <- c("DMSO ctrl", "100 uM iBTK")
stim_inhib_suppl_figS7 <- c("Basal\nDMSO ctrl", "Basal\n100 uM iBTK", "Activated\nDMSO ctrl", "Activated\n100 uM iBTK")
# select_colors <- c("DMSO ctrl" = "grey", "100 uM iSYK" = "#9dce5c", "100 uM iBTK" = "#5c9dce", "100 uM iNFkB" = "#ce5c9d")
colors_suppl_figS7 <- c("Basal\nDMSO ctrl" = "#bdbdbd", "Basal\n100 uM iBTK" = "#9dc4e1", 
                               "Activated\nDMSO ctrl" = "#737373", "Activated\n100 uM iBTK" = "#5c9dce")
shape_suppl_figS7 <- c("Basal\nDMSO ctrl" = 16, "Basal\n100 uM iBTK" = 16, 
                              "Activated\nDMSO ctrl" = 17, "Activated\n100 uM iBTK" = 17)
```

```{r suppl_figS7_PCA}
# Prepare data for FactoMineR package
# cts_pca: dataframe with wells as row names, proteins as column names, and count data as cell values
# coldata: dataframe with wells as row names and all metadata as columns
cts_pca <- data_ID_suppl_figS7  %>%
  dplyr::filter(counts_norm >= 1) %>%
  dplyr::select(target_nospace, plate_well, counts_norm) %>%
  dplyr::filter(!is.na(counts_norm)) %>%
  spread(target_nospace, counts_norm) %>%
  replace(is.na(.), 0) %>% 
  column_to_rownames("plate_well")

# cts_pca <- scale(cts_pca)

coldata <- data.frame(plate_well = rownames(cts_pca)) %>%
  left_join(distinct(dplyr::select(data_ID_suppl_figS7, all_of(meta_cols_suppl_figS7)))) %>%
  mutate(stimulus = factor(stimulus, levels = stim_suppl_figS7), 
         inhibitor = factor(inhibitor, levels = inhib_suppl_figS7), 
         inhib_conc = factor(inhib_conc, levels = conc_suppl_figS7)) #If necessary, make factors of some metadata columns

rownames(coldata) <- coldata$plate_well

# Results
pca_results <- PCA(cts_pca, scale.unit = FALSE, ncp = 5, graph = FALSE)

pca_expl_var <- as.data.frame(get_eigenvalue(pca_results)) %>% # Percentage variance explained by each PC
  rownames_to_column("PC") %>%
  pull(var = variance.percent, name = PC) %>%
  round(digits = 1)

pca_variab <- get_pca_var(pca_results) # Results focused on variables (proteins)
pca_indiv <- get_pca_ind(pca_results) # Results focused on individuals (wells)

pca_data <- as.data.frame(pca_indiv$coord[, 1:3]) %>%
  rownames_to_column("plate_well") %>%
  dplyr::rename(PC1 = Dim.1, PC2 = Dim.2, PC3 = Dim.3) %>% 
  left_join(coldata)
```


### Panels {.tabset}

#### Panel A
```{r suppl_figS7_panelA, fig.width=6, fig.height=3, fig.retina=1}
# Figure
# Selected samples only
suppl_figS7_panelA <- ggplot(subset(pca_data, inhib_text_new %in% conditions_suppl_figS7)) + 
  geom_point(aes(x = PC1, y = PC2, shape = stim_inhib, color = stim_inhib), size = 2.5) +
  scale_color_manual(values = colors_suppl_figS7, breaks = names(colors_suppl_figS7), name = "Treatment") +
  scale_shape_manual(values = shape_suppl_figS7, breaks = names(shape_suppl_figS7), name = "Treatment") +
  xlab(paste0("PC1: ", pca_expl_var[1], "% variance")) +
  ylab(paste0("PC2: ", pca_expl_var[2], "% variance")) +
  facet_wrap(vars(factor(experiment, labels = "PC1 vs PC2"))) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(), legend.key.size = unit(0.4, "cm"), legend.spacing.y = unit(0.5, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "none", legend.justification = "left") +
  textsize_small
suppl_figS7_panelA
```

#### Panel B
```{r suppl_figS7_panelB, fig.width=6, fig.height=3, fig.retina=1}
# Figure
# Selected samples only
suppl_figS7_panelB <- ggplot(subset(pca_data, inhib_text_new %in% conditions_suppl_figS7)) + 
  geom_point(aes(x = PC3, y = PC2, shape = stim_inhib, color = stim_inhib), size = 2.5) +
  scale_color_manual(values = colors_suppl_figS7, breaks = names(colors_suppl_figS7), name = "Treatment") +
  scale_shape_manual(values = shape_suppl_figS7, breaks = names(shape_suppl_figS7), name = "Treatment") +
  xlab(paste0("PC3: ", pca_expl_var[3], "% variance")) +
  ylab(paste0("PC2: ", pca_expl_var[2], "% variance")) +
  facet_wrap(vars(factor(experiment, labels = "PC3 vs PC2"))) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(), legend.key.size = unit(0.65, "cm"), legend.spacing.y = unit(0.75, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "right", legend.justification = "left") +
  guides(color = guide_legend(by_row = TRUE), shape = guide_legend(by_row = TRUE)) +
  textsize_small
suppl_figS7_panelB
```


### Combined fig

```{r suppl_figS7_combi, fig.width=5, fig.height=2, fig.retina=1}
# Combine all panels of the figure
suppl_figS7 <- plot_grid(suppl_figS7_panelA, suppl_figS7_panelB, labels = PANEL_labels[c(1, 2)], nrow = 1, rel_widths = c(1, 1.55), label_size = 10)
suppl_figS7

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS7,
  filename = "output/figures/paper/suppl_figS7.pdf",
  width = 5,
  height = 2,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS7,
  filename = "output/figures/paper/suppl_figS7.jpg",
  width = 5,
  height = 2,
  units = "in",
  dpi = 300
  )
```
*Figure S7: Principal components PC1-3 visualized for DMSO controls (basal and activated) and 100 uM iBTK treatment.*

```{r suppl_figS7_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS7"))
# rm(list = ls(pattern = "_fig1"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S8

*Effect of iBTK concentration on the comparison between activated and basal signaling. Volcano plot visualization of the data represented in the heatmap of Figure 2A.*

Input:
-   DS108 ID-seq data

    -   DESeq2 analysis of basal and activated signaling with inhibitors

### Data

```{r suppl_figS8_data}
# ID-seq data DS108 (counts per well/sample and mean per condition)
data_ID_suppl_figS8 <- read_csv("output/DS108_StimInhibIDseq/IDseq_ann/IDseq_data_sample.csv") %>%
  subset(inhibitor != "iPI3Kd" & target_nospace != "BIM" & target_nospace != "Histone_H2AX_S139" & cell_line == "HBL1") %>%
  mutate(stim_clean = case_when(stimulus == "PBS" ~ "Basal", 
                                stimulus == "aIg+H2O2" ~ "Activated"),
         inhib_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                               inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                               .default = inhibitor), 
         inhib_text_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                                    inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                                    .default = inhib_conc_text), 
         stim_inhib = paste0(stim_clean, "\n", inhib_text_new)) #%>%
  # subset(inhib_new != "PBS ctrl")
```

```{r suppl_figS8_labels}
stim_suppl_figS8 <- c("PBS", "aIg+H2O2")
stim_label_suppl_figS8 <- c("Basal", "Activated")
inhib_suppl_figS8 <- c("iBTK", "iSYK", "iNFkB")
conc_suppl_figS8 <- c("0 uM (DMSO)", "0.1 uM", "1 uM", "10 uM", "100 uM")
conc_label_suppl_figS8 <- c("DMSO ctrl", "0.1 uM", "1 uM", "10 uM", "100 uM")

meta_cols_suppl_figS8 <- c("plate_well", "plate", "well", "experiment", "cell_line", "stimulus", "stim_clean", "inhibitor", "inhib_conc_uM", "inhib_conc", "inhib_conc_text", "inhib_text_new", "stim_inhib", "replicate", "description", "descript_rep")
```


Differential expression analysis of the effect of inhibitor concentration on the stimulation in HBL1

DESeq2 analysis parameters:

-   HBL1: 1 inhibitor, 5 conc, 2 stimuli

-   Compensated counts (>= 1)

-   Model design: inhib_text_new (ref: DMSO ctrl) + stimulus (ref: PBS) + inhib_text_new:stimulus

```{r suppl_figS8_DESeq}
# Differential expression analysis
# Prepare data to load into DESeq dataset
# cts: dataframe with proteins as row names, wells as column names, and count data as cell values
# coldata: dataframe with wells as row names and all metadata as columns
cts <- data_ID_suppl_figS8  %>%
  dplyr::filter(cell_line == "HBL1" & inhib_conc %in% conc_suppl_figS8 & counts >= 1) %>%
  dplyr::select(target_nospace, plate_well, counts) %>%
  dplyr::filter(!is.na(counts)) %>%
  spread(plate_well, counts) %>%
  replace(is.na(.), 0) %>%
  column_to_rownames("target_nospace")

cts <- as.matrix(as.data.frame(cts))

coldata <- data.frame(plate_well = colnames(cts)) %>%
  left_join(distinct(dplyr::select(data_ID_suppl_figS8, all_of(meta_cols_suppl_figS8)))) %>%
  distinct()

rownames(coldata) <- coldata$plate_well

# Create DESeq object
# First define how the model is designed. Place most important parameter last
modeldesign <- ~ inhib_text_new + stim_clean + inhib_text_new:stim_clean

# Then create the DESeq dataset
dds <- DESeqDataSetFromMatrix(countData = cts,
                              colData = coldata,
                              design = modeldesign)
# Define the reference samples for design parameter
dds$inhib_text_new <- relevel(dds$inhib_text_new, ref = "DMSO ctrl")
dds$stim_clean <- relevel(dds$stim_clean, ref = "Basal")

# Run DESeq2: 
  # This function performs a default analysis through the steps:
  # Estimation of size factors: estimateSizeFactors
  # Estimation of dispersion: estimateDispersions
  # Negative Binomial GLM fitting and Wald statistics: nbinomWaldTest

dds <- DESeq(dds, test = "Wald", fitType = "local")
DESeq_comparisons <- resultsNames(dds) # lists the coefficients
# DESeq_comparisons

# Results
results_stim <- results(dds, name = "stim_clean_Activated_vs_Basal", alpha = 0.05)
results_iBTK0.1 <- results(dds, name = "inhib_text_new0.1.uM.iBTK.stim_cleanActivated", alpha = 0.05)
results_iBTK1 <- results(dds, name = "inhib_text_new1.uM.iBTK.stim_cleanActivated", alpha = 0.05)
results_iBTK10 <- results(dds, name = "inhib_text_new10.uM.iBTK.stim_cleanActivated", alpha = 0.05)
results_iBTK100 <- results(dds, name = "inhib_text_new100.uM.iBTK.stim_cleanActivated", alpha = 0.05)

list_results <- list(results_stim, results_iBTK0.1, results_iBTK1, results_iBTK10, results_iBTK100)

# Data transformation
# Regularized log transform
rld <- rlog(dds, blind = FALSE)

# Data wrangling
# Function to prepare DESeq2 results for volcano plots
# Standard log2FC filter = log2(1.5); standard padj filter = 0.05
prep_forvulcano <- function(dataset = dataset, padj_filter = 0.05, foldchange_filter = log2(1.5)){ 
  dataset$proteins <- rownames(dataset)
  dataset$target_nospace <- rownames(dataset)
  
  # Add a column for differential expression
  dataset$diff_express <- "NO"
  dataset$diff_express[dataset$log2FoldChange > foldchange_filter & dataset$padj < padj_filter] <- "UP"
  dataset$diff_express[dataset$log2FoldChange < -foldchange_filter & dataset$padj < padj_filter] <- "DOWN"
  
  # Add a column for labeling
  dataset$delabel <- NA
  dataset$delabel[dataset$diff_express != "NO"] <- dataset$proteins[dataset$diff_express != "NO"]
  
  # Add Ab metadata
  # dataset <- left_join(as.data.frame(dataset), meta_Abs)
  
  return(as.data.frame(dataset))
}

# Apply function to each dataset
# padj < 0.05
# log2FC > log2(1.05)
names_results_volc <- c("volc_stim", "volc_iBTK0.1", "volc_iBTK1", "volc_iBTK10", "volc_iBTK100")
for(dataset in c(1:length(list_results))){
  assign(names_results_volc[dataset], prep_forvulcano(dataset = list_results[[dataset]], foldchange_filter = log2(1.1)))
}

# Add column with comparison for faceting
comp_suppl_figS8 <- c("Activated vs basal", 
                      "Effect of 0.1 uM iBTK", "Effect of 1 uM iBTK", "Effect of 10 uM iBTK", "Effect of 100 uM iBTK")
volc_stim$comparison <- comp_suppl_figS8[1]
volc_iBTK0.1$comparison <- comp_suppl_figS8[2]
volc_iBTK1$comparison <- comp_suppl_figS8[3]
volc_iBTK10$comparison <- comp_suppl_figS8[4]
volc_iBTK100$comparison <- comp_suppl_figS8[5]
dataset_suppl_figS8 <- list(volc_stim, volc_iBTK0.1, volc_iBTK1, volc_iBTK10, volc_iBTK100) %>%
  purrr::reduce(full_join)
```

### Panels {.tabset}

#### Panel A
```{r suppl_figS8_panelA, fig.width=6, fig.height=3, fig.retina=1}
# Select data
dataset_suppl_figS8A <- dataset_suppl_figS8 %>%
  subset(comparison == "Activated vs basal")
# comp_suppl_figS8 <- c("Activated vs basal", "Effect of 0.1 uM iBTK", "Effect of 1 uM iBTK", "Effect of 10 uM iBTK", "Effect of 100 uM iBTK")

# Figure
suppl_figS8_panelA <- ggplot(data = dataset_suppl_figS8A,
                      aes(x = log2FoldChange, y = -log10(padj), color = diff_express, label = delabel)) +
  geom_point(size = 0.5) +
  geom_text_repel(size = 1.75,
                  segment.size = 0.2,
                  hjust = 0,
                  direction = "y",
                  nudge_y = -log10(0.005),
                  nudge_x = ifelse(dataset_suppl_figS8A$log2FoldChange < 0, -0.4 - dataset_suppl_figS8A$log2FoldChange, 0.4 - dataset_suppl_figS8A$log2FoldChange)
  ) +
  facet_wrap(~comparison, nrow = 1) +
  scale_color_manual(values = c(UP = "#A50026", NO = "black", DOWN = "#364B9A"),
                     breaks = c("UP", "NO", "DOWN"),
                     labels = c("Increased", "No difference", "Decreased"),
                     name = "Differentially\nexpressed\nproteins") + 
  geom_vline(xintercept = c(-log2(1.1), log2(1.1)), color = "#CC6677") +
  geom_hline(yintercept = -log10(0.05), color = "#CC6677") +
  labs(x = "log2(fold change)", y = "-log10(adjusted p-value)", title = "") +
  coord_cartesian(xlim = c(-0.5, 1.5), ylim = c(0, 325)) +
  theme_bw() +
  theme(legend.key.size = unit(0.2, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "right", legend.justification = "left") + #legend.position = "none"
  # guides(color = guide_legend(nrow = 3, byrow = TRUE)) +
  textsize_small
suppl_figS8_panelA
```

#### Panel B
```{r suppl_figS8_panelB, fig.width=6, fig.height=3, fig.retina=1}
# Select data
dataset_suppl_figS8B <- dataset_suppl_figS8 %>%
  subset(comparison == "Effect of 0.1 uM iBTK")
# comp_suppl_figS8 <- c("Activated vs basal", "Effect of 0.1 uM iBTK", "Effect of 1 uM iBTK", "Effect of 10 uM iBTK", "Effect of 100 uM iBTK")

# Figure
suppl_figS8_panelB <- ggplot(data = dataset_suppl_figS8B,
                      aes(x = log2FoldChange, y = -log10(padj), color = diff_express, label = delabel)) +
  geom_point(size = 0.5) +
  geom_text_repel(size = 1.75,
                  segment.size = 0.2,
                  hjust = 0,
                  direction = "y",
                  nudge_y = -log10(0.005),
                  nudge_x = ifelse(dataset_suppl_figS8B$log2FoldChange < 0, -0.4 - dataset_suppl_figS8B$log2FoldChange, 0.4 - dataset_suppl_figS8B$log2FoldChange)
  ) +
  facet_wrap(~comparison, nrow = 1) +
  scale_color_manual(values = c(UP = "#A50026", NO = "black", DOWN = "#364B9A"),
                     breaks = c("UP", "NO", "DOWN"),
                     labels = c("Increased", "No difference", "Decreased"),
                     name = "Differentially expressed proteins") + 
  geom_vline(xintercept = c(-log2(1.1), log2(1.1)), color = "#CC6677") +
  geom_hline(yintercept = -log10(0.05), color = "#CC6677") +
  labs(x = "log2(fold change)", y = "-log10(adjusted p-value)", title = "") +
  coord_cartesian(xlim = c(-1.5, 0.5), ylim = c(0, 75)) +
  theme_bw() +
  theme(legend.key.size = unit(0.2, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "none", legend.justification = "left") + #legend.position = "none"
  guides(color = guide_legend(nrow = 3, byrow = TRUE)) +
  textsize_small
suppl_figS8_panelB
```

#### Panel C
```{r suppl_figS8_panelC, fig.width=6, fig.height=3, fig.retina=1}
# Select data
dataset_suppl_figS8C <- dataset_suppl_figS8 %>%
  subset(comparison == "Effect of 1 uM iBTK")
# comp_suppl_figS8 <- c("Activated vs basal", "Effect of 0.1 uM iBTK", "Effect of 1 uM iBTK", "Effect of 10 uM iBTK", "Effect of 100 uM iBTK")

# Figure
suppl_figS8_panelC <- ggplot(data = dataset_suppl_figS8C,
                      aes(x = log2FoldChange, y = -log10(padj), color = diff_express, label = delabel)) +
  geom_point(size = 0.5) +
  geom_text_repel(size = 1.75,
                  segment.size = 0.2,
                  hjust = 0,
                  direction = "y",
                  nudge_y = -log10(0.005),
                  nudge_x = ifelse(dataset_suppl_figS8C$log2FoldChange < 0, -0.4 - dataset_suppl_figS8C$log2FoldChange, 0.4 - dataset_suppl_figS8C$log2FoldChange)
  ) +
  facet_wrap(~comparison, nrow = 1) +
  scale_color_manual(values = c(UP = "#A50026", NO = "black", DOWN = "#364B9A"),
                     breaks = c("UP", "NO", "DOWN"),
                     labels = c("Increased", "No difference", "Decreased"),
                     name = "Differentially expressed proteins") + 
  geom_vline(xintercept = c(-log2(1.1), log2(1.1)), color = "#CC6677") +
  geom_hline(yintercept = -log10(0.05), color = "#CC6677") +
  labs(x = "log2(fold change)", y = "-log10(adjusted p-value)", title = "") +
  coord_cartesian(xlim = c(-1.5, 0.5), ylim = c(0, 75)) +
  theme_bw() +
  theme(legend.key.size = unit(0.2, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "none", legend.justification = "left") + #legend.position = "none"
  guides(color = guide_legend(nrow = 3, byrow = TRUE)) +
  textsize_small
suppl_figS8_panelC
```

#### Panel D
```{r suppl_figS8_panelD, fig.width=6, fig.height=3, fig.retina=1}
# Select data
dataset_suppl_figS8D <- dataset_suppl_figS8 %>%
  subset(comparison == "Effect of 10 uM iBTK")
# comp_suppl_figS8 <- c("Activated vs basal", "Effect of 0.1 uM iBTK", "Effect of 1 uM iBTK", "Effect of 10 uM iBTK", "Effect of 100 uM iBTK")

# Figure
suppl_figS8_panelD <- ggplot(data = dataset_suppl_figS8D,
                      aes(x = log2FoldChange, y = -log10(padj), color = diff_express, label = delabel)) +
  geom_point(size = 0.5) +
  geom_text_repel(size = 1.75,
                  segment.size = 0.2,
                  hjust = 0,
                  direction = "y",
                  nudge_y = -log10(0.005),
                  nudge_x = ifelse(dataset_suppl_figS8D$log2FoldChange < 0, -0.4 - dataset_suppl_figS8D$log2FoldChange, 0.4 - dataset_suppl_figS8D$log2FoldChange)
  ) +
  facet_wrap(~comparison, nrow = 1) +
  scale_color_manual(values = c(UP = "#A50026", NO = "black", DOWN = "#364B9A"),
                     breaks = c("UP", "NO", "DOWN"),
                     labels = c("Increased", "No difference", "Decreased"),
                     name = "Differentially expressed proteins") + 
  geom_vline(xintercept = c(-log2(1.1), log2(1.1)), color = "#CC6677") +
  geom_hline(yintercept = -log10(0.05), color = "#CC6677") +
  labs(x = "log2(fold change)", y = "-log10(adjusted p-value)", title = "") +
  coord_cartesian(xlim = c(-1.5, 0.5), ylim = c(0, 75)) +
  theme_bw() +
  theme(legend.key.size = unit(0.2, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "none", legend.justification = "left") + #legend.position = "none"
  guides(color = guide_legend(nrow = 3, byrow = TRUE)) +
  textsize_small
suppl_figS8_panelD
```

#### Panel E
```{r suppl_figS8_panelE, fig.width=6, fig.height=3, fig.retina=1}
# Select data
dataset_suppl_figS8E <- dataset_suppl_figS8 %>%
  subset(comparison == "Effect of 100 uM iBTK")
# comp_suppl_figS8 <- c("Activated vs basal", "Effect of 0.1 uM iBTK", "Effect of 1 uM iBTK", "Effect of 10 uM iBTK", "Effect of 100 uM iBTK")

# Figure
suppl_figS8_panelE <- ggplot(data = dataset_suppl_figS8E,
                      aes(x = log2FoldChange, y = -log10(padj), color = diff_express, label = delabel)) +
  geom_point(size = 0.5) +
  geom_text_repel(size = 1.75,
                  segment.size = 0.2,
                  hjust = 0,
                  direction = "y",
                  nudge_y = -log10(0.005),
                  nudge_x = ifelse(dataset_suppl_figS8E$log2FoldChange < 0, -0.4 - dataset_suppl_figS8E$log2FoldChange, 0.4 - dataset_suppl_figS8E$log2FoldChange)
  ) +
  facet_wrap(~comparison, nrow = 1) +
  scale_color_manual(values = c(UP = "#A50026", NO = "black", DOWN = "#364B9A"),
                     breaks = c("UP", "NO", "DOWN"),
                     labels = c("Increased", "No difference", "Decreased"),
                     name = "Differentially expressed proteins") + 
  geom_vline(xintercept = c(-log2(1.1), log2(1.1)), color = "#CC6677") +
  geom_hline(yintercept = -log10(0.05), color = "#CC6677") +
  labs(x = "log2(fold change)", y = "-log10(adjusted p-value)", title = "") +
  coord_cartesian(xlim = c(-1.5, 0.5), ylim = c(0, 75)) +
  theme_bw() +
  theme(legend.key.size = unit(0.2, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "none", legend.justification = "left") + #legend.position = "none"
  guides(color = guide_legend(nrow = 3, byrow = TRUE)) +
  textsize_small
suppl_figS8_panelE
```


### Combined fig

```{r suppl_figS8_combi, fig.width=6.125, fig.height=8, fig.retina=1}
# Combine all panels of the figure
suppl_figS8_A <- plot_grid(suppl_figS8_panelA, NULL, labels = PANEL_labels[c(1)], nrow = 1, rel_widths = c(1.75, 1), label_size = 10)
suppl_figS8_BCDE <- plot_grid(suppl_figS8_panelB, suppl_figS8_panelC, suppl_figS8_panelD, suppl_figS8_panelE, labels = PANEL_labels[c(2:5)], ncol = 2, rel_widths = c(1, 1), rel_heights = c(1, 1), label_size = 10)
suppl_figS8 <- plot_grid(suppl_figS8_A, suppl_figS8_BCDE, ncol = 1, rel_heights = c(1, 2))
suppl_figS8

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS8,
  filename = "output/figures/paper/suppl_figS8.pdf",
  width = 6.125,
  height = 8,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS8,
  filename = "output/figures/paper/suppl_figS8.jpg",
  width = 6.125,
  height = 8,
  units = "in",
  dpi = 300
  )
```
*Figure S8: Effect of iBTK concentration on the comparison between activated and basal signaling. Volcano plot visualization of the data represented in the heatmap of Figure 2A.*

```{r suppl_figS8_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS8"))
rm(list = ls(pattern = "results_"))
rm(list = ls(pattern = "volc_"))
rm(list = ls(pattern = "list_"))
rm(list = ls(pattern = "names_"))
rm(list = ls(pattern = "titles_"))
rm(list = ls(pattern = "data_"))
rm(list = ls(pattern = "pca"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S9

*Inhibition effect of 100 uM iSYK or 100 uM iNFkB versus DMSO control in activated cells.*

Input:
-   Cytoscape network figures


### Panels {.tabset}

#### Panel A
```{r suppl_figS9_panelA, fig.retina=1}
# Placeholder
suppl_figS9_panelA <- ggplot() +
  geom_blank() +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 10)) + 
  # labs(title = "BCR signaling network") + 
  theme_bw() +
  theme(axis.text = element_text(color = "white"), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank()) +
  textsize_small
# suppl_figS9_panelA

# PNG
# 100 uM iSYK (DS108)
png_suppl_figS9_panelA <- magick::image_read("output/figures/non_R_figs/HBL1_StimOnly_iSYK100uMvsDMSO.png") %>%
  magick::image_border(color = "black", geometry = "1x1") %>%
  magick::image_ggplot(interpolate = TRUE) +
  ggtitle("100 uM iSYK vs DMSO ctrl in activated cells") +
  # theme(axis.title = element_text(colour = "white"), axis.text = element_blank()) +
  textsize_small
png_suppl_figS9_panelA

# legend
png_suppl_figS9_legend <- magick::image_read("output/figures/non_R_figs/legend_network_projections.png") %>%
  # magick::image_border(color = "black", geometry = "1x1") %>%
  magick::image_ggplot(interpolate = TRUE) +
  # ggtitle("\n") +
  textsize_small
# png_suppl_figS9_legend
```

#### Panel B
```{r suppl_figS9_panelB, fig.retina=1}
# Placeholder
suppl_figS9_panelB <- ggplot() +
  geom_blank() +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 10)) + 
  # labs(title = "BCR signaling network") + 
  theme_bw() +
  theme(axis.text = element_text(color = "white"), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank()) +
  textsize_small
# suppl_figS9_panelB

# PNG
# 100 uM iNFkB (DS108)
png_suppl_figS9_panelB <- magick::image_read("output/figures/non_R_figs/HBL1_StimOnly_iNFkB100uMvsDMSO.png") %>%
  magick::image_border(color = "black", geometry = "1x1") %>%
  magick::image_ggplot(interpolate = TRUE) +
  ggtitle("100 uM iNFkB vs DMSO ctrl in activated cells") +
  # theme(axis.title = element_text(colour = "white"), axis.text = element_blank()) +
  textsize_small
png_suppl_figS9_panelB
```


### Combined fig

```{r suppl_figS9_combi, fig.width=7.3, fig.height=4.6, fig.retina=1}
# Combine all panels of the figure
suppl_figS9_AB <- plot_grid(png_suppl_figS9_panelA, png_suppl_figS9_panelB, labels = PANEL_labels[c(1, 2)], nrow = 1, rel_widths = c(1, 1), label_size = 10)
suppl_figS9 <- plot_grid(suppl_figS9_AB, png_suppl_figS9_legend, ncol = 1, rel_heights = c(7, 1), label_size = 10)
suppl_figS9

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS9,
  filename = "output/figures/paper/suppl_figS9.pdf",
  width = 7.3,
  height = 4.6,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS9,
  filename = "output/figures/paper/suppl_figS9.jpg",
  width = 7.3,
  height = 4.6,
  units = "in",
  dpi = 300
  )
```
*Figure S9: Inhibition effect of 100 uM iSYK or 100 uM iNFkB versus DMSO control in activated cells.*

```{r suppl_figS9_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS9"))
# rm(list = ls(pattern = "_fig1"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S10

*Effect of iNFkB concentration on the comparison between activated and basal signaling.*

Input:
-   DS108 ID-seq data

    -   DESeq2 analysis of basal and activated signaling with inhibitors

### Data

```{r suppl_figS10_data}
# ID-seq data DS108 (counts per well/sample and mean per condition)
data_ID_suppl_figS10 <- read_csv("output/DS108_StimInhibIDseq/IDseq_ann/IDseq_data_sample.csv") %>%
  subset(inhibitor != "iPI3Kd" & target_nospace != "BIM" & target_nospace != "Histone_H2AX_S139" & cell_line == "HBL1") %>%
  mutate(stim_clean = case_when(stimulus == "PBS" ~ "Basal", 
                                stimulus == "aIg+H2O2" ~ "Activated"),
         inhib_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                               inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                               .default = inhibitor), 
         inhib_text_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                                    inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                                    .default = inhib_conc_text), 
         stim_inhib = paste0(stim_clean, "\n", inhib_text_new)) #%>%
  # subset(inhib_new != "PBS ctrl")
```

```{r suppl_figS10_labels}
stim_suppl_figS10 <- c("PBS", "aIg+H2O2")
stim_label_suppl_figS10 <- c("Basal", "Activated")
inhib_suppl_figS10 <- c("iBTK", "iSYK", "iNFkB")

conc_suppl_figS10 <- c("0 uM (DMSO)", "100 uM")
conc_label_suppl_figS10 <- c("DMSO ctrl", "100 uM")
conc_all_suppl_figS10 <- c("0 uM (DMSO)", "0.1 uM", "1 uM", "10 uM", "100 uM")
conc_all_label_suppl_figS10 <- c("DMSO\nctrl", "0.1 uM", "1 uM", "10 uM", "100 uM")

meta_cols_suppl_figS10 <- c("plate_well", "plate", "well", "experiment", "cell_line", "stimulus", "stim_clean", "inhibitor", "inhib_new", "inhib_conc_uM", "inhib_conc", "inhib_conc_text", "inhib_text_new", "stim_inhib", "replicate", "description", "descript_rep")
```


### Panels {.tabset}

#### Panel A

Differential expression analysis of the effect of inhibitor concentration on the stimulation in HBL1

DESeq2 analysis parameters:

-   HBL1: 3 inhibitors, 5 conc, 2 stimuli

-   Compensated counts (>= 1)

-   Model design: inhib_text_new (ref: DMSO ctrl) + stimulus (ref: PBS) + inhib_text_new:stimulus

```{r fig3A_DESeq_HBL1}
# Differential expression analysis
# Prepare data to load into DESeq dataset
# cts: dataframe with proteins as row names, wells as column names, and count data as cell values
# coldata: dataframe with wells as row names and all metadata as columns
cts <- data_ID_suppl_figS10  %>%
  dplyr::filter(cell_line == "HBL1" & inhib_conc %in% conc_all_suppl_figS10 & counts >= 1) %>%
  dplyr::select(target_nospace, plate_well, counts) %>%
  dplyr::filter(!is.na(counts)) %>%
  spread(plate_well, counts) %>%
  replace(is.na(.), 0) %>%
  column_to_rownames("target_nospace")

cts <- as.matrix(as.data.frame(cts))

coldata <- data.frame(plate_well = colnames(cts)) %>%
  left_join(data_ID_suppl_figS10[c(1:13, 28:31)]) %>% 
  distinct()

rownames(coldata) <- coldata$plate_well

# Create DESeq object
# First define how the model is designed. Place most important parameter last
modeldesign <- ~ inhib_text_new + stim_clean + inhib_text_new:stim_clean

# Then create the DESeq dataset
dds <- DESeqDataSetFromMatrix(countData = cts,
                              colData = coldata,
                              design = modeldesign)
# Define the reference samples for design parameter
dds$inhib_text_new <- relevel(dds$inhib_text_new, ref = "DMSO ctrl")
dds$stim_clean <- relevel(dds$stim_clean, ref = "Basal")

# Run DESeq2: 
  # This function performs a default analysis through the steps:
  # Estimation of size factors: estimateSizeFactors
  # Estimation of dispersion: estimateDispersions
  # Negative Binomial GLM fitting and Wald statistics: nbinomWaldTest

dds <- DESeq(dds, test = "Wald", fitType = "local")
DESeq_comparisons <- resultsNames(dds) # lists the coefficients
# DESeq_comparisons

# Results
results_HBL1_stim <- results(dds, name = "stim_clean_Activated_vs_Basal", alpha = 0.05)
# results_HBL1_iSYK100 <- results(dds, name = "inhib_text_new100.uM.iSYK.stim_cleanActivated", alpha = 0.05)
# results_HBL1_iBTK100 <- results(dds, name = "inhib_text_new100.uM.iBTK.stim_cleanActivated", alpha = 0.05)
results_HBL1_iNFkB100 <- results(dds, name = "inhib_text_new100.uM.iNFkB.stim_cleanActivated", alpha = 0.05)

list_results <- list(results_HBL1_stim, results_HBL1_iNFkB100)

# Data transformation
# Regularized log transform
rld_HBL1 <- rlog(dds, blind = FALSE)

# Data wrangling
# Function to prepare DESeq2 results for volcano plots
# Standard log2FC filter = log2(1.5); standard padj filter = 0.05
prep_forvulcano <- function(dataset = dataset, padj_filter = 0.05, foldchange_filter = log2(1.5)){ 
  dataset$proteins <- rownames(dataset)
  dataset$target_nospace <- rownames(dataset)
  
  # Add a column for differential expression
  dataset$diff_express <- "NO"
  dataset$diff_express[dataset$log2FoldChange > foldchange_filter & dataset$padj < padj_filter] <- "UP"
  dataset$diff_express[dataset$log2FoldChange < -foldchange_filter & dataset$padj < padj_filter] <- "DOWN"
  
  # Add a column for labeling
  dataset$delabel <- NA
  dataset$delabel[dataset$diff_express != "NO"] <- dataset$proteins[dataset$diff_express != "NO"]
  
  # Add Ab metadata
  # dataset <- left_join(as.data.frame(dataset), meta_Abs)
  
  return(dataset)
}

# Apply function to each dataset
# Applied thresholds:
# padj < 0.05
# log2FC > log2(1.05)
names_volc <- c("volc_HBL1_stim", "volc_HBL1_iNFkB100")
for(dataset in c(1:length(list_results))){
  assign(names_volc[dataset], prep_forvulcano(dataset = list_results[[dataset]], foldchange_filter = log2(1.1)))
}

# Function to filter the data
# Standard log2FC filter = log2(1.5); standard padj filter = 0.05
filter_heatmap <- function(dataset = dataset, padj_filter = 0.05, foldchange_filter = log2(1.5), select_top = TRUE, select_n = 10) {
  data <- as.data.frame(dataset) %>%
    dplyr::filter(padj <= padj_filter & abs(log2FoldChange) >= foldchange_filter) %>%
    arrange(-log2FoldChange) 
  rownames(data) <- data$target_nospace
  
  # Select top 10 proteins with most increased and decreased expression
  if (select_top == TRUE) {
    data_top <- data %>%
      slice_max(order_by = abs(log2FoldChange), n = select_n)
    return(data_top)
  } else {
    return(data)
  }
}

# Apply function to each dataset
list_results_volc <- list(volc_HBL1_stim, volc_HBL1_iNFkB100)
names_heat <- c("heat_HBL1_stim", "heat_HBL1_iNFkB100")
for(dataset in c(1:length(list_results_volc))){
  assign(names_heat[[dataset]], filter_heatmap(dataset = list_results_volc[[dataset]], select_top = FALSE, foldchange_filter = log2(1.1)))
  dataset
}
```

```{r suppl_figS10_panelA, fig.width=6, fig.height=3, fig.retina=1}
# Select data
# Combine heatmap datasets (without DESeq2 analysis values)
heat_inhib_HBL1 <- list(heat_HBL1_stim, heat_HBL1_iNFkB100) %>%
  purrr::reduce(full_join) %>%
  dplyr::select(-c(baseMean, log2FoldChange, lfcSE, stat, pvalue, padj, diff_express)) %>%
  left_join(data_ID_suppl_figS10[, 14:21]) %>%
  dplyr::filter(modification == "phospho") %>%
  distinct()

figS10A_prot_stim <- sort(unique(c(heat_HBL1_stim$target_nospace)))
figS10A_prot_iBTK <- sort(unique(c(heat_HBL1_iNFkB100$target_nospace)))

# Subset the full dataframe to get metadata for heatmap plotting
info_suppl_figS10 <- data_ID_suppl_figS10 %>%
  dplyr::select(plate_well, stim_clean, inhib_conc, inhibitor, cell_line) %>%
  distinct() %>%
  dplyr::filter(cell_line == "HBL1" & inhibitor == "iNFkB" & inhib_conc %in% conc_all_suppl_figS10 & !(stim_clean == "Basal" & inhib_conc %in% conc_all_suppl_figS10[2:5])) %>%
  mutate(inhibitor = factor(inhibitor, levels = inhib_suppl_figS10)) %>%
  as.data.frame()
rownames(info_suppl_figS10) <- info_suppl_figS10$plate_well
info_suppl_figS10 <- dplyr::select(info_suppl_figS10, -c(plate_well, cell_line))

# Get the rld transformed data for the heatmap and scale per row
data_heat_suppl_figS10 <- t(scale(t(assay(rld_HBL1)[c(heat_inhib_HBL1$target_nospace), rownames(info_suppl_figS10)])))
# sort_hclust <- function(...) as.hclust(dendsort(as.dendrogram(...)))
# data_cluster_rows <- sort_hclust(hclust(dist(data_cell)))
# plot(data_cluster_rows, main = "Unsorted Dendrogram", xlab = "", sub = "")

# Figure
ann_colors_suppl_figS10 <- list(stim_clean = colors_stim, 
                         inhibitor = colors_inhib,
                         # inhib_new = c("DMSO ctrl" = "grey", colors_inhib), 
                         inhib_conc = setNames(colors_conc, unique(info_suppl_figS10$inhib_conc)))

suppl_figS10_panelA <- ggplotify::as.ggplot(ComplexHeatmap::pheatmap(
  data_heat_suppl_figS10,
  scale = "none",
  cluster_rows = TRUE,
  treeheight_row = 0,
  show_rownames = TRUE,
  show_colnames = FALSE,
  cluster_cols = FALSE,
  annotation_col = info_suppl_figS10,
  annotation_colors = ann_colors_suppl_figS10,
  colorRampPalette(c("navy", "white", "firebrick3"))(50),
  column_split = info_suppl_figS10$inhibitor,
  row_split = subset(heat_inhib_HBL1)$modification,
  # cellwidth = 10,
  # cellheight = 10,
  fontsize = 5,
  border_color = NA,
  # legend = FALSE,
  # annotation_legend = FALSE,
  # main = "aIg+H2O2 vs PBS (without inhibitors)"
))
# suppl_figS10_panelA

#################
ann_colors_suppl_figS10 <- list(Stimulus = colors_stim, 
                         Inhibitor = colors_inhib,
                         # inhib_new = c("DMSO ctrl" = "grey", colors_inhib), 
                         "Inhibitor conc" = setNames(colors_conc, unique(info_suppl_figS10$inhib_conc)))
heat_legend_suppl_figS10 <- list(title = "Scaled\nexpression", title_gp = gpar(fontsize = 7), labels_gp = gpar(fontsize = 7), 
                          grid_width = unit(2, "mm"), grid_height = unit(20, "mm"))

col_ann_suppl_figS10 <- HeatmapAnnotation(Inhibitor = info_suppl_figS10$inhibitor, 
                                   "Inhibitor conc" = info_suppl_figS10$inhib_conc, 
                                   Stimulus = info_suppl_figS10$stim_clean, 
                                   simple_anno_size = unit(2.5, "mm"), 
                                   annotation_name_gp = gpar(fontsize = 7),
                                   col = ann_colors_suppl_figS10, 
                                   annotation_legend_param = list(Inhibitor = list(title = "Inhibitor", 
                                                                                   title_gp = gpar(fontsize = 7), 
                                                                                   labels_gp = gpar(fontsize = 7), 
                                                                                   grid_width = unit(2, "mm"), 
                                                                                   grid_height = unit(1, "mm")), 
                                                                  "Inhibitor conc" = list(title = "Inhibitor\nconcentration", 
                                                                                   title_gp = gpar(fontsize = 7), 
                                                                                   labels_gp = gpar(fontsize = 7), 
                                                                                   grid_width = unit(2, "mm"), 
                                                                                   grid_height = unit(1, "mm")), 
                                                                  Stimulus = list(title = "Stimulus", 
                                                                                   title_gp = gpar(fontsize = 7), 
                                                                                   labels_gp = gpar(fontsize = 7), 
                                                                                   grid_width = unit(2, "mm"), 
                                                                                   grid_height = unit(1, "mm"))), 
                                   show_legend = c(FALSE, TRUE, TRUE))

suppl_figS10_panelA <- ggplotify::as.ggplot(ComplexHeatmap::pheatmap(
  data_heat_suppl_figS10,
  scale = "none",
  cluster_rows = TRUE,
  # treeheight_row = 10,
  show_rownames = TRUE,
  show_colnames = FALSE,
  cluster_cols = FALSE,
  # annotation_col = fig3A_info_Ly8,
  top_annotation = col_ann_suppl_figS10,
  # annotation_colors = fig3A_ann_colors,
  colorRampPalette(c("navy", "white", "firebrick3"))(50),
  column_split = info_suppl_figS10$inhibitor,
  # row_split = subset(heat_inhib_HBL1)$modification,
  row_gap = unit(1, "mm"), 
  # cellwidth = 10,
  # cellheight = 10,
  fontsize = 6,
  row_title_gp = gpar(fontsize = 7),
  column_title_gp = gpar(fontsize = 7), 
  annotation_names_col = gpar(fontsize = 7),
  border_color = NA,
  heatmap_legend_param = heat_legend_suppl_figS10, 
  # annotation_legend = FALSE,
)) +
  ggtitle("          Effect of 100 uM iNFkB on activated vs basal signaling") +
  textsize_small
suppl_figS10_panelA
```


### Combined fig

```{r suppl_figS10_combi, fig.width=5, fig.height=3, fig.retina=1}
# Combine all panels of the figure
suppl_figS10_panelA

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS10_panelA,
  filename = "output/figures/paper/suppl_figS10.pdf",
  width = 5,
  height = 3,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS10_panelA,
  filename = "output/figures/paper/suppl_figS10.jpg",
  width = 5,
  height = 3,
  units = "in",
  dpi = 300
  )
```
*Figure: S10: Effect of iNFkB concentration on the comparison between activated and basal signaling.*

```{r suppl_figS10_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS10"))
rm(list = ls(pattern = "results_"))
rm(list = ls(pattern = "volc_"))
rm(list = ls(pattern = "heat_"))
rm(list = ls(pattern = "list_"))
rm(list = ls(pattern = "names_"))
rm(list = ls(pattern = "titles_"))
rm(list = ls(pattern = "data_"))
rm(list = ls(pattern = "pca"))
rm(list = ls(pattern = "png_"))
gc()
```


## Suppl. figure S11

*Phosphorylation levels of CD79a, IKKa/b, and MAPK p38 upon activation and inhibition.*

Input:

-   DS108 ID-seq data

    -   Counts
    
### Data

```{r suppl_figS11_data}
# ID-seq data DS108 (counts per well/sample and mean per condition)
data_ID_suppl_figS11 <- read_csv("output/DS108_StimInhibIDseq/IDseq_ann/IDseq_data_sample.csv") %>%
  subset(inhibitor != "iPI3Kd" & target_nospace != "BIM" & target_nospace != "Histone_H2AX_S139" & cell_line == "HBL1") %>%
  mutate(stim_clean = case_when(stimulus == "PBS" ~ "Basal", 
                                stimulus == "aIg+H2O2" ~ "Activated"),
         inhib_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                               inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                               .default = inhibitor), 
         inhib_text_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                                    inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                                    .default = inhib_conc_text), 
         stim_inhib = paste0(stim_clean, "\n", inhib_text_new)) #%>%
  # subset(inhib_new != "PBS ctrl")
mean_ID_suppl_figS11 <- read_csv("output/DS108_StimInhibIDseq/IDseq_ann/IDseq_data_condition.csv") %>%
  subset(inhibitor != "iPI3Kd" & target_nospace != "BIM" & target_nospace != "Histone_H2AX_S139" & cell_line == "HBL1") %>%
  mutate(stim_clean = case_when(stimulus == "PBS" ~ "Basal", 
                                stimulus == "aIg+H2O2" ~ "Activated"),
         inhib_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                               inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                               .default = inhibitor), 
         inhib_text_new = case_when(inhib_conc == "0 uM (DMSO)" ~ "DMSO ctrl", 
                                    inhib_conc == "0 uM (PBS)" ~ "PBS ctrl", 
                                    .default = inhib_conc_text), 
         stim_inhib = paste0(stim_clean, "\n", inhib_text_new)) #%>%
  # subset(inhib_new != "PBS ctrl")
```

```{r suppl_figS11_labels}
# fig3_cells <- c("HBL1", "OCI-Ly8")
stim_suppl_figS11 <- c("PBS", "aIg+H2O2")
stim_label_suppl_figS11 <- c("Basal", "Activated")
inhib_suppl_figS11 <- c("iBTK", "iSYK", "iNFkB")
conc_all_suppl_figS11 <- c("0 uM (DMSO)", "0.1 uM", "1 uM", "10 uM", "100 uM")
conc_label_suppl_figS11 <- c("DMSO\nctrl", "0.1 uM", "1 uM", "10 uM", "100 uM")
# label_conc <- c("0 uM", "0.1 uM", "1 uM", "10 uM", "100 uM")

meta_cols_suppl_figS11 <- c("plate_well", "plate", "well", "experiment", "cell_line", "stimulus", "stim_clean", "inhibitor", "inhib_new", "inhib_conc_uM", "inhib_conc", "inhib_conc_text", "inhib_text_new", "stim_inhib", "replicate", "description", "descript_rep")
```


### Panels {.tabset}

#### Panel A

Example protein CD79a
```{r suppl_figS11_panelA, fig.width=4, fig.height=6, fig.retina=1}
# Data
figS11A_prot <- c(
  "CD79a_Y182" 
  # "IKKa_b_S176_S180",
  # "JAK1_Y1022_Y1023"
  # "LYN_Y397"
  # "MAPK_p38_T180_Y182"
  # "CDK1_T14_Y15"
  # "PYK2_Y402"
) 
figS11A_prot_label <- c("CD79a (Y182)")
figS11A_data <- data_ID_suppl_figS11 %>%
  subset(target_nospace %in% figS11A_prot & inhib_conc %in% conc_all_suppl_figS11 & cell_line == "HBL1")
figS11A_mean <- mean_ID_suppl_figS11 %>%
  subset(target_nospace %in% figS11A_prot & inhib_conc %in% conc_all_suppl_figS11 & cell_line == "HBL1") 

# Figure
suppl_figS11_panelA <- ggplot() +
  geom_point(data = figS11A_data, 
             aes(factor(inhib_conc, levels = conc_all_suppl_figS11, labels = conc_label_suppl_figS11), 
                 counts_norm, 
                 color = stimulus, 
                 shape = stimulus
             ), 
             alpha = 1, size = 0.75) +
  geom_line(data = figS11A_mean, 
            aes(factor(inhib_conc, levels = conc_all_suppl_figS11, labels = conc_label_suppl_figS11), 
                counts_norm,
                group = paste(inhibitor, stimulus),
                color = stimulus
            ),
            size = 0.5) +
  facet_wrap(vars(factor(inhibitor, levels = inhib_suppl_figS11)), ncol = 1) +
  scale_shape_manual(values = c(17, 16), breaks = stim_suppl_figS11, labels = stim_label_suppl_figS11, name = "Stimulus") +
  scale_color_manual(values = colors_stim, breaks = stim_suppl_figS11, labels = stim_label_suppl_figS11, name = "Stimulus") +
  labs(x = "Inhibitor conc.", y = "Normalized counts", title = figS11A_prot_label) +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.3, "cm"), legend.spacing.y = unit(0.2, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "bottom", strip.text.x = element_text(margin = margin(0.05, 0, 0.05, 0, "cm")), axis.text.x = element_text(size = 6)) +
  guides(shape = guide_legend(nrow = 2, byrow = TRUE), color = guide_legend(nrow = 2, byrow = TRUE)) +
  textsize_small
suppl_figS11_panelA
```

#### Panel B

Example protein IKKa/b
```{r suppl_figS11_panelB, fig.width=4, fig.height=6, fig.retina=1}
# Data
figS11B_prot <- c(
  # "CD79a_Y182" 
  "IKKa_b_S176_S180"
  # "MAPK_p38_T180_Y182"
) 
figS11B_prot_label <- c("IKKa/b (S176/S180)")
figS11B_data <- data_ID_suppl_figS11 %>%
  subset(target_nospace %in% figS11B_prot & inhib_conc %in% conc_all_suppl_figS11 & cell_line == "HBL1")
figS11B_mean <- mean_ID_suppl_figS11 %>%
  subset(target_nospace %in% figS11B_prot & inhib_conc %in% conc_all_suppl_figS11 & cell_line == "HBL1") 

# Figure
suppl_figS11_panelB <- ggplot() +
  geom_point(data = figS11B_data, 
             aes(factor(inhib_conc, levels = conc_all_suppl_figS11, labels = conc_label_suppl_figS11), 
                 counts_norm, 
                 color = stimulus, 
                 shape = stimulus
             ), 
             alpha = 1, size = 0.75) +
  geom_line(data = figS11B_mean, 
            aes(factor(inhib_conc, levels = conc_all_suppl_figS11, labels = conc_label_suppl_figS11), 
                counts_norm,
                group = paste(inhibitor, stimulus),
                color = stimulus
            ),
            size = 0.5) +
  facet_wrap(vars(factor(inhibitor, levels = inhib_suppl_figS11)), ncol = 1) +
  scale_shape_manual(values = c(17, 16), breaks = stim_suppl_figS11, labels = stim_label_suppl_figS11, name = "Stimulus") +
  scale_color_manual(values = colors_stim, breaks = stim_suppl_figS11, labels = stim_label_suppl_figS11, name = "Stimulus") +
  labs(x = "Inhibitor conc.", y = "Normalized counts", title = figS11B_prot_label) +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.3, "cm"), legend.spacing.y = unit(0.2, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "none", strip.text.x = element_text(margin = margin(0.05, 0, 0.05, 0, "cm")), axis.text.x = element_text(size = 6)) +
  # guides(shape = guide_legend(nrow = 2, byrow = TRUE), color = guide_legend(nrow = 2, byrow = TRUE)) +
  textsize_small
suppl_figS11_panelB
```

#### Panel C

Example protein MAPK p38
```{r suppl_figS11_panelC, fig.width=4, fig.height=6, fig.retina=1}
# Data
figS11C_prot <- c(
  # "CD79a_Y182" 
  # "IKKa_b_S176_S180",
  "MAPK_p38_T180_Y182"
) 
figS11C_prot_label <- c("MAPK p38 (T180/Y182)")
figS11C_data <- data_ID_suppl_figS11 %>%
  subset(target_nospace %in% figS11C_prot & inhib_conc %in% conc_all_suppl_figS11 & cell_line == "HBL1")
figS11C_mean <- mean_ID_suppl_figS11 %>%
  subset(target_nospace %in% figS11C_prot & inhib_conc %in% conc_all_suppl_figS11 & cell_line == "HBL1") 

# Figure
suppl_figS11_panelC <- ggplot() +
  geom_point(data = figS11C_data, 
             aes(factor(inhib_conc, levels = conc_all_suppl_figS11, labels = conc_label_suppl_figS11), 
                 counts_norm, 
                 color = stimulus, 
                 shape = stimulus
             ), 
             alpha = 1, size = 0.75) +
  geom_line(data = figS11C_mean, 
            aes(factor(inhib_conc, levels = conc_all_suppl_figS11, labels = conc_label_suppl_figS11), 
                counts_norm,
                group = paste(inhibitor, stimulus),
                color = stimulus
            ),
            size = 0.5) +
  facet_wrap(vars(factor(inhibitor, levels = inhib_suppl_figS11)), ncol = 1) +
  # facet_grid(inhibitor~target_nospace, scales = "free_y") +
  scale_shape_manual(values = c(17, 16), breaks = stim_suppl_figS11, labels = stim_label_suppl_figS11, name = "Stimulus") +
  scale_color_manual(values = colors_stim, breaks = stim_suppl_figS11, labels = stim_label_suppl_figS11, name = "Stimulus") +
  labs(x = "Inhibitor conc.", y = "Normalized counts", title = figS11C_prot_label) +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.3, "cm"), legend.spacing.y = unit(0.2, "cm"), legend.box.spacing = unit(0.1, "cm"), legend.position = "none", strip.text.x = element_text(margin = margin(0.05, 0, 0.05, 0, "cm")), axis.text.x = element_text(size = 6)) +
  # guides(shape = guide_legend(nrow = 2, byrow = TRUE), color = guide_legend(nrow = 2, byrow = TRUE)) +
  textsize_small
suppl_figS11_panelC
```


### Combined fig

```{r suppl_figS11_combi, fig.width=6.125, fig.height=3.8, fig.retina=1}
# Combine all panels of the figure
suppl_figS11 <- plot_grid(suppl_figS11_panelA, suppl_figS11_panelB, suppl_figS11_panelC, labels = PANEL_labels[c(1:3)], nrow = 1, rel_widths = c(1, 1, 1), label_size = 10, align = "h")
suppl_figS11

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS11,
  filename = "output/figures/paper/suppl_figS11.pdf",
  width = 6.125,
  height = 3.8,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS11,
  filename = "output/figures/paper/suppl_figS11.jpg",
  width = 6.125,
  height = 3.8,
  units = "in",
  dpi = 300
  )
```
*Figure S11: Phosphorylation levels of CD79a, IKKa/b, and MAPK p38 upon activation and inhibition.*

```{r suppl_figS11_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS11"))
rm(list = ls(pattern = "pca"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S12

*Complete PCA signaling state space of the inhibitor combination experiment.*

Input:
-   DS113 ID-seq data

    -   PCA on all samples

### Data

```{r suppl_figS12_data}
# ID-seq data (counts per well/sample and mean per condition)
data_ID_suppl_figS12 <- read_csv("output/DS113_InhibCombiIDseq/IDseq_ann/IDseq_data_sample.csv") %>%
  subset(inhibitor != "iPI3Kd" & target_nospace != "BIM" & target_nospace != "Histone_H2AX_S139" & cell_line == "HBL1") %>%
  mutate(stim_inhib = paste0(stim_clean, "\n", inhib_text_new)) #%>%
  # subset(inhib_new != "PBS ctrl")
```

```{r suppl_figS12_labels}
stim_suppl_figS12 <- c("PBS", "aIg+H2O2")
stim_label_suppl_figS12 <- c("Basal", "Activated")

legend_label_suppl_figS12 <- "iSYK + iBTK + iNFkB"
inhib_group_suppl_figS12 <- c("DMSO ctrl", "single", "two", "three_equal", "three_mix")
inhib_suppl_figS12 <- c("DMSO ctrl", 
                        "iBTK", "iSYK", "iNFkB", 
                        "iSYK + iBTK", "iBTK + iNFkB", "iSYK +iNFkB", 
                        "iSYK + iBTK + iNFkB")
inhib_label_suppl_figS12 <- c("DMSO ctrl", 
                              "iBTK", "iSYK", "iNFkB", 
                              "iBTK+ iSYK", "iBTK + iNFkB", "iSYK +iNFkB", 
                              "iBTK + iSYK + iNFkB")
conc_single_suppl_figS12 <- c(0, 1, 2.5, 5, 10)
conc_all1_suppl_figS12 <- c("0 + 0 + 0 uM", 
                            "0 + 10 + 0 uM", "10 + 0 + 0 uM", "0 + 0 + 10 uM", 
                            "2.5 + 2.5 + 0 uM", "0 + 2.5 + 2.5 uM", "2.5 + 0 + 2.5 uM", 
                            "1 + 1 + 1 uM", "2.5 + 2.5 + 2.5 uM", "10 + 10 + 10 uM", 
                            "1 + 5 + 1 uM", "5 + 1 + 1 uM", "1 + 1 + 5 uM", 
                            "10 + 10 + 10 uM (nostain)")
conc_all2_suppl_figS12 <- c("DMSO ctrl", 
                            "10 uM iBTK", "10 uM iSYK", "10 uM iNFkB", 
                            "2.5 uM of iSYK + iBTK", "2.5 uM of iBTK + iNFkB", "2.5 uM of iSYK + iNFkB", 
                            "1 uM of iSYK + iBTK + iNFkB", "2.5 uM of iSYK + iBTK + iNFkB", "10 uM of iSYK + iBTK + iNFkB", 
                            "5 uM iBTK + 1 uM of iSYK + iNFkB", "5 uM iSYK + 1 uM of iBTK + iNFkB", "5 uM iNFkB + 1 uM of iSYK + iBTK")

meta_cols_suppl_figS12 <- c("plate_well", "plate", "well", "experiment", "cell_line", "stimulus", "stim_clean", "inhibitor", "inhib_new", "inhib_conc", "inhib_conc_new", "inhib_group", "iSYK_conc_uM", "iBTK_conc_uM", "iNFkB_conc_uM", "inhib_conc_text", "inhib_text_new", "stim_inhib", "replicate", "description", "descript_rep")
```


### Panels {.tabset}

#### Panel A

PCA of all samples (PCA performed on all samples, all samples plotted).
```{r suppl_figS12_PCA}
# Prepare data for FactoMineR package
# cts_pca: dataframe with wells as row names, proteins as column names, and count data as cell values
# coldata: dataframe with wells as row names and all metadata as columns
cts_pca <- data_ID_suppl_figS12  %>%
  dplyr::filter(counts_norm >= 1) %>%
  dplyr::select(target_nospace, plate_well, counts_norm) %>%
  dplyr::filter(!is.na(counts_norm)) %>%
  spread(target_nospace, counts_norm) %>%
  replace(is.na(.), 0) %>% 
  column_to_rownames("plate_well")

# cts_pca <- scale(cts_pca)

coldata <- data.frame(plate_well = rownames(cts_pca)) %>%
  left_join(distinct(dplyr::select(data_ID_suppl_figS12, all_of(meta_cols_suppl_figS12)))) %>%
  mutate(stimulus = factor(stimulus, levels = stim_suppl_figS12), 
         inhibitor = factor(inhibitor, levels = inhib_suppl_figS12), 
         inhib_conc = factor(inhib_conc, levels = conc_all1_suppl_figS12)) #If necessary, make factors of some metadata columns

rownames(coldata) <- coldata$plate_well

# Results
pca_results <- PCA(cts_pca, scale.unit = FALSE, ncp = 5, graph = FALSE)

pca_expl_var <- as.data.frame(get_eigenvalue(pca_results)) %>% # Percentage variance explained by each PC
  rownames_to_column("PC") %>%
  pull(var = variance.percent, name = PC) %>%
  round(digits = 1)

pca_variab <- get_pca_var(pca_results) # Results focused on variables (proteins)
pca_indiv <- get_pca_ind(pca_results) # Results focused on individuals (wells)

pca_data <- as.data.frame(pca_indiv$coord[, 1:3]) %>%
  rownames_to_column("plate_well") %>%
  dplyr::rename(PC1 = Dim.1, PC2 = Dim.2, PC3 = Dim.3) %>% 
  left_join(coldata)
```

```{r suppl_figS12_panelA, fig.width=6, fig.height=3, fig.retina=1}
# Data
pca_legend_levels <- c("Basal\nDMSO ctrl", "Basal\n10 uM of iSYK + iBTK + iNFkB", 
                       "Activated\nDMSO ctrl", 
                       "Activated\n10 uM iBTK", "Activated\n10 uM iSYK", "Activated\n10 uM iNFkB", 
                       "Activated\n2.5 uM of iSYK + iBTK", "Activated\n2.5 uM of iBTK + iNFkB", "Activated\n2.5 uM of iSYK + iNFkB", 
                       "Activated\n1 uM of iSYK + iBTK + iNFkB", "Activated\n2.5 uM of iSYK + iBTK + iNFkB", "Activated\n10 uM of iSYK + iBTK + iNFkB", 
                       "Activated\n5 uM iBTK + 1 uM of iSYK + iNFkB", "Activated\n5 uM iSYK + 1 uM of iBTK + iNFkB", "Activated\n5 uM iNFkB + 1 uM of iSYK + iBTK")
pca_legend_shapes <- c(16, 16, 
                       17, 
                       17, 17, 17, 
                       17, 17, 17, 
                       17, 17, 17, 
                       17, 17, 17)
pca_legend_values <- c("#bdbdbd", "#857892", 
                       "#737373", 
                       "#5c9dce", "#9dce5c", "#ce5c9d", 
                       "#5cce8d", "#8d5cce", "#ce8d5c", 
                       "#d3bceb", "#ae82da", "#8351b6",  
                       "#729cb9", "#9bb677", "#b6779b")
names(pca_legend_shapes) <- pca_legend_levels
names(pca_legend_values) <- pca_legend_levels
pca_legend_labels <- c(
  "Basal\nDMSO ctrl" = "Basal\nDMSO ctrl", 
  "Basal\n10 uM of iSYK + iBTK + iNFkB" = "Basal\n10 uM of each",
  "Activated\nDMSO ctrl" = "Activated\nDMSO ctrl", 
  "Activated\n10 uM iBTK" = "10 uM iBTK",
  "Activated\n10 uM iSYK" = "10 uM iSYK",
  "Activated\n10 uM iNFkB" = "10 uM iNFkB",
  "Activated\n2.5 uM of iSYK + iBTK" = "2.5 uM iBTK + iSYK", 
  "Activated\n2.5 uM of iBTK + iNFkB" = "2.5 uM iBTK + iNFkB", 
  "Activated\n2.5 uM of iSYK + iNFkB" = "2.5 uM iSYK + iNFkB",  
  "Activated\n1 uM of iSYK + iBTK + iNFkB" = "1 uM of each",
  "Activated\n2.5 uM of iSYK + iBTK + iNFkB" = "2.5 uM of each",
  "Activated\n10 uM of iSYK + iBTK + iNFkB" = "10 uM of each",
  "Activated\n5 uM iBTK + 1 uM of iSYK + iNFkB" = "5 uM iBTK + \n1 uM iSYK + iNFkB",
  "Activated\n5 uM iSYK + 1 uM of iBTK + iNFkB" = "5 uM iSYK + \n1 uM iBTK + iNFkB",
  "Activated\n5 uM iNFkB + 1 uM of iSYK + iBTK" = "5 uM iNFkB + \n1 uM iSYK + iBTK")

# Figure
suppl_figS12_panelA <- ggplot(pca_data) + 
  geom_point(aes(x = PC1, y = PC2, 
                 shape = stim_inhib, color = stim_inhib), 
             size = 3) +
  scale_color_manual(values = pca_legend_values,
                     breaks = pca_legend_levels,
                     labels = pca_legend_labels,
                     name = "Treatment") +
  scale_shape_manual(values = pca_legend_shapes,
                     breaks = pca_legend_levels,
                     labels = pca_legend_labels,
                     name = "Treatment") +
  xlab(paste0("PC1: ", pca_expl_var[1], "% variance")) +
  ylab(paste0("PC2: ", pca_expl_var[2], "% variance")) + 
  theme_bw() +
  theme(panel.grid.minor = element_blank(), legend.key.size = unit(0.7, "cm"), legend.spacing.y = unit(0.5, "cm"), legend.box.spacing = unit(0.2, "cm"), legend.position = "right", legend.justification = "left") +
  textsize_small
suppl_figS12_panelA
```


### Combined fig

```{r suppl_figS12_combi, fig.width=6.125, fig.height=4.7, fig.retina=1}
# Combine all panels of the figure
suppl_figS12_panelA

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS12_panelA,
  filename = "output/figures/paper/suppl_figS12.pdf",
  width = 6.125,
  height = 4.7,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS12_panelA,
  filename = "output/figures/paper/suppl_figS12.jpg",
  width = 6.125,
  height = 4.7,
  units = "in",
  dpi = 300
  )
```
*Figure S12: Complete PCA signaling state space of the inhibitor combination experiment.*

```{r suppl_figS12_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS12"))
rm(list = ls(pattern = "pca"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S13

*Proteins contributing >2.5% to a PC in the inhibitor combination experiment. *

Input:
-   DS113 ID-seq data

    -   PCA on all samples

### Data

```{r suppl_figS13_data}
# ID-seq data (counts per well/sample and mean per condition)
data_ID_suppl_figS13 <- read_csv("output/DS113_InhibCombiIDseq/IDseq_ann/IDseq_data_sample.csv") %>%
  subset(inhibitor != "iPI3Kd" & target_nospace != "BIM" & target_nospace != "Histone_H2AX_S139" & cell_line == "HBL1") %>%
  mutate(stim_inhib = paste0(stim_clean, "\n", inhib_text_new)) #%>%
  # subset(inhib_new != "PBS ctrl")
```

```{r suppl_figS13_labels}
stim_suppl_figS13 <- c("PBS", "aIg+H2O2")
stim_label_suppl_figS13 <- c("Basal", "Activated")

legend_label_suppl_figS13 <- "iSYK + iBTK + iNFkB"
inhib_group_suppl_figS13 <- c("DMSO ctrl", "single", "two", "three_equal", "three_mix")
group_select_suppl_figS13 <- c("DMSO ctrl", "single")
inhib_suppl_figS13 <- c("DMSO ctrl", 
                        "iBTK", "iSYK", "iNFkB", 
                        "iSYK + iBTK", "iBTK + iNFkB", "iSYK +iNFkB", 
                        "iSYK + iBTK + iNFkB")
inhib_label_suppl_figS13 <- c("DMSO ctrl", 
                              "iBTK", "iSYK", "iNFkB", 
                              "iBTK+ iSYK", "iBTK + iNFkB", "iSYK +iNFkB", 
                              "iBTK + iSYK + iNFkB")
conc_single_suppl_figS13 <- c(0, 1, 2.5, 5, 10)
conc_all1_suppl_figS13 <- c("0 + 0 + 0 uM", 
                            "0 + 10 + 0 uM", "10 + 0 + 0 uM", "0 + 0 + 10 uM", 
                            "2.5 + 2.5 + 0 uM", "0 + 2.5 + 2.5 uM", "2.5 + 0 + 2.5 uM", 
                            "1 + 1 + 1 uM", "2.5 + 2.5 + 2.5 uM", "10 + 10 + 10 uM", 
                            "1 + 5 + 1 uM", "5 + 1 + 1 uM", "1 + 1 + 5 uM", 
                            "10 + 10 + 10 uM (nostain)")
conc_all2_suppl_figS13 <- c("DMSO ctrl", 
                            "10 uM iBTK", "10 uM iSYK", "10 uM iNFkB", 
                            "2.5 uM of iSYK + iBTK", "2.5 uM of iBTK + iNFkB", "2.5 uM of iSYK + iNFkB", 
                            "1 uM of iSYK + iBTK + iNFkB", "2.5 uM of iSYK + iBTK + iNFkB", "10 uM of iSYK + iBTK + iNFkB", 
                            "5 uM iBTK + 1 uM of iSYK + iNFkB", "5 uM iSYK + 1 uM of iBTK + iNFkB", "5 uM iNFkB + 1 uM of iSYK + iBTK")

meta_cols_suppl_figS13 <- c("plate_well", "plate", "well", "experiment", "cell_line", "stimulus", "stim_clean", "inhibitor", "inhib_new", "inhib_conc", "inhib_conc_new", "inhib_group", "iSYK_conc_uM", "iBTK_conc_uM", "iNFkB_conc_uM", "inhib_conc_text", "inhib_text_new", "stim_inhib", "replicate", "description", "descript_rep")
```

PCA of all samples (PCA performed on all samples, selected samples plotted).
```{r suppl_figS13_PCA}
# Prepare data for FactoMineR package
# cts_pca: dataframe with wells as row names, proteins as column names, and count data as cell values
# coldata: dataframe with wells as row names and all metadata as columns
cts_pca <- data_ID_suppl_figS13  %>%
  dplyr::filter(counts_norm >= 1) %>%
  dplyr::select(target_nospace, plate_well, counts_norm) %>%
  dplyr::filter(!is.na(counts_norm)) %>%
  spread(target_nospace, counts_norm) %>%
  replace(is.na(.), 0) %>% 
  column_to_rownames("plate_well")

# cts_pca <- scale(cts_pca)

coldata <- data.frame(plate_well = rownames(cts_pca)) %>%
  left_join(distinct(dplyr::select(data_ID_suppl_figS13, all_of(meta_cols_suppl_figS13)))) %>%
  mutate(stimulus = factor(stimulus, levels = stim_suppl_figS13), 
         inhibitor = factor(inhibitor, levels = inhib_suppl_figS13), 
         inhib_conc = factor(inhib_conc, levels = conc_all1_suppl_figS13)) #If necessary, make factors of some metadata columns

rownames(coldata) <- coldata$plate_well

# Results
pca_results <- PCA(cts_pca, scale.unit = FALSE, ncp = 5, graph = FALSE)

pca_expl_var <- as.data.frame(get_eigenvalue(pca_results)) %>% # Percentage variance explained by each PC
  rownames_to_column("PC") %>%
  pull(var = variance.percent, name = PC) %>%
  round(digits = 1)

pca_variab <- get_pca_var(pca_results) # Results focused on variables (proteins)
pca_indiv <- get_pca_ind(pca_results) # Results focused on individuals (wells)

pca_data <- as.data.frame(pca_indiv$coord[, 1:3]) %>%
  rownames_to_column("plate_well") %>%
  dplyr::rename(PC1 = Dim.1, PC2 = Dim.2, PC3 = Dim.3) %>% 
  left_join(coldata)
```


### Panels {.tabset}

#### Panel A
```{r suppl_figS13_panelA, fig.width=6, fig.height=3, fig.retina=1}
# Idea:
# Visualise proteins contributing to PCs
# Quality of representation: cos2 - size of dot
# Percentage contribution to one PC: contrib - colour of dot

# Select data
data_contrib_2.5p <- as.data.frame(pca_variab$contrib) %>%
  dplyr::filter(Dim.1 >= 2.5 | Dim.2 >= 2.5 | Dim.3 >= 2.5) %>% # | Dim.4 >= 1 | Dim.5 >= 1
  dplyr::rename(PC1 = Dim.1, PC2 =  Dim.2, PC3 = Dim.3, PC4 = Dim.4, PC5 = Dim.5) %>%
  dplyr::select(c(PC1, PC2, PC3)) %>%
  mutate_all(function(x){x/100}) %>%
  as.matrix()
data_contrib_prot <- factor(rownames(data_contrib_2.5p))

data_cos2_2.5p <- as.data.frame(pca_variab$cos2) %>%
  rownames_to_column("proteins") %>%
  dplyr::filter(proteins %in% data_contrib_prot) %>%
  column_to_rownames("proteins") %>%
  dplyr::rename(PC1 = Dim.1, PC2 =  Dim.2, PC3 = Dim.3, PC4 = Dim.4, PC5 = Dim.5) %>%
  dplyr::select(c(PC1, PC2, PC3)) %>%
  as.matrix()

# Tidy data format
data_cos2_tidy <- as.data.frame(data_cos2_2.5p) %>%
  rownames_to_column("proteins") %>%
  pivot_longer(2:4, names_to = "PC", values_to = "cos2")
data_contrib_tidy <- as.data.frame(data_contrib_2.5p) %>%
  rownames_to_column("proteins") %>%
  pivot_longer(2:4, names_to = "PC", values_to = "contrib") %>%
  mutate(contrib = contrib * 100)
data_contrib_all <- full_join(data_cos2_tidy, data_contrib_tidy)

# Figure
# ggplot geom_count
suppl_figS13_panelA <- ggplot() +
  geom_point(data = data_contrib_all, aes(x = PC, y = factor(proteins, levels = rev(data_contrib_prot)), size = cos2, fill = contrib), color = "black", pch = 21) +
  scale_size_area(max_size = 10, breaks = c(0, 0.25, 0.5, 0.75, 1), name = "Quality of\nrepresentation\nin PCs") +
  scale_fill_gradient(low = "#FEDA8B", high = "#73001a", name = "Percentage\ncontribution\nwithin one PC") + #7f2704 #67000d
  labs(x = "", y = "") + 
  theme_bw() +
  # theme(legend.key.size = unit(0.4, "cm"), legend.spacing.y = unit(0.25, "cm"), legend.box.spacing = unit(0.25, "cm"), axis.text = element_text(size = 8), legend.title = element_text(size = 9), legend.text = element_text(size = 8), legend.position = "right", panel.grid = element_line(color = "#f0f0f0")) + 
  theme(legend.key.size = unit(0.4, "cm"), legend.spacing.y = unit(0.25, "cm"), legend.box.spacing = unit(0.25, "cm"), legend.position = "right", panel.grid = element_line(color = "#f0f0f0")) + 
  textsize_small
suppl_figS13_panelA
```


### Combined fig

```{r suppl_figS13_combi, fig.width=3.5, fig.height=5, fig.retina=1}
# Combine all panels of the figure
suppl_figS13_panelA

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS13_panelA,
  filename = "output/figures/paper/suppl_figS13.pdf",
  width = 3.5,
  height = 5,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS13_panelA,
  filename = "output/figures/paper/suppl_figS13.jpg",
  width = 3.5,
  height = 5,
  units = "in",
  dpi = 300
  )
```
*Figure S13: Proteins contributing >2.5% to a PC in the inhibitor combination experiment. *

```{r suppl_figS13_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS13"))
# rm(list = ls(pattern = "_fig1"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S14

*Principal components PC1-3 visualized for DMSO controls (basal and activated) and 10 uM single inhibitor treatment.*

Input:
-   DS113 ID-seq data

    -   PCA on all samples

### Data

```{r suppl_figS14_data}
# ID-seq data (counts per well/sample and mean per condition)
data_ID_suppl_figS14 <- read_csv("output/DS113_InhibCombiIDseq/IDseq_ann/IDseq_data_sample.csv") %>%
  subset(inhibitor != "iPI3Kd" & target_nospace != "BIM" & target_nospace != "Histone_H2AX_S139" & cell_line == "HBL1") %>%
  mutate(stim_inhib = paste0(stim_clean, "\n", inhib_text_new)) #%>%
  # subset(inhib_new != "PBS ctrl")
```

```{r suppl_figS14_labels}
stim_suppl_figS14 <- c("PBS", "aIg+H2O2")
stim_label_suppl_figS14 <- c("Basal", "Activated")

legend_label_suppl_figS14 <- "iSYK + iBTK + iNFkB"
inhib_group_suppl_figS14 <- c("DMSO ctrl", "single", "two", "three_equal", "three_mix")
group_select_suppl_figS14 <- c("DMSO ctrl", "single")
inhib_suppl_figS14 <- c("DMSO ctrl", 
                        "iBTK", "iSYK", "iNFkB", 
                        "iSYK + iBTK", "iBTK + iNFkB", "iSYK +iNFkB", 
                        "iSYK + iBTK + iNFkB")
inhib_label_suppl_figS14 <- c("DMSO ctrl", 
                              "iBTK", "iSYK", "iNFkB", 
                              "iBTK+ iSYK", "iBTK + iNFkB", "iSYK +iNFkB", 
                              "iBTK + iSYK + iNFkB")
conc_single_suppl_figS14 <- c(0, 1, 2.5, 5, 10)
conc_all1_suppl_figS14 <- c("0 + 0 + 0 uM", 
                            "0 + 10 + 0 uM", "10 + 0 + 0 uM", "0 + 0 + 10 uM", 
                            "2.5 + 2.5 + 0 uM", "0 + 2.5 + 2.5 uM", "2.5 + 0 + 2.5 uM", 
                            "1 + 1 + 1 uM", "2.5 + 2.5 + 2.5 uM", "10 + 10 + 10 uM", 
                            "1 + 5 + 1 uM", "5 + 1 + 1 uM", "1 + 1 + 5 uM", 
                            "10 + 10 + 10 uM (nostain)")
conc_all2_suppl_figS14 <- c("DMSO ctrl", 
                            "10 uM iBTK", "10 uM iSYK", "10 uM iNFkB", 
                            "2.5 uM of iSYK + iBTK", "2.5 uM of iBTK + iNFkB", "2.5 uM of iSYK + iNFkB", 
                            "1 uM of iSYK + iBTK + iNFkB", "2.5 uM of iSYK + iBTK + iNFkB", "10 uM of iSYK + iBTK + iNFkB", 
                            "5 uM iBTK + 1 uM of iSYK + iNFkB", "5 uM iSYK + 1 uM of iBTK + iNFkB", "5 uM iNFkB + 1 uM of iSYK + iBTK")

meta_cols_suppl_figS14 <- c("plate_well", "plate", "well", "experiment", "cell_line", "stimulus", "stim_clean", "inhibitor", "inhib_new", "inhib_conc", "inhib_conc_new", "inhib_group", "iSYK_conc_uM", "iBTK_conc_uM", "iNFkB_conc_uM", "inhib_conc_text", "inhib_text_new", "stim_inhib", "replicate", "description", "descript_rep")
```

PCA of all samples (PCA performed on all samples, selected samples plotted).
```{r suppl_figS14_PCA}
# Prepare data for FactoMineR package
# cts_pca: dataframe with wells as row names, proteins as column names, and count data as cell values
# coldata: dataframe with wells as row names and all metadata as columns
cts_pca <- data_ID_suppl_figS14  %>%
  dplyr::filter(counts_norm >= 1) %>%
  dplyr::select(target_nospace, plate_well, counts_norm) %>%
  dplyr::filter(!is.na(counts_norm)) %>%
  spread(target_nospace, counts_norm) %>%
  replace(is.na(.), 0) %>% 
  column_to_rownames("plate_well")

# cts_pca <- scale(cts_pca)

coldata <- data.frame(plate_well = rownames(cts_pca)) %>%
  left_join(distinct(dplyr::select(data_ID_suppl_figS14, all_of(meta_cols_suppl_figS14)))) %>%
  mutate(stimulus = factor(stimulus, levels = stim_suppl_figS14), 
         inhibitor = factor(inhibitor, levels = inhib_suppl_figS14), 
         inhib_conc = factor(inhib_conc, levels = conc_all1_suppl_figS14)) #If necessary, make factors of some metadata columns

rownames(coldata) <- coldata$plate_well

# Results
pca_results <- PCA(cts_pca, scale.unit = FALSE, ncp = 5, graph = FALSE)

pca_expl_var <- as.data.frame(get_eigenvalue(pca_results)) %>% # Percentage variance explained by each PC
  rownames_to_column("PC") %>%
  pull(var = variance.percent, name = PC) %>%
  round(digits = 1)

pca_variab <- get_pca_var(pca_results) # Results focused on variables (proteins)
pca_indiv <- get_pca_ind(pca_results) # Results focused on individuals (wells)

pca_data <- as.data.frame(pca_indiv$coord[, 1:3]) %>%
  rownames_to_column("plate_well") %>%
  dplyr::rename(PC1 = Dim.1, PC2 = Dim.2, PC3 = Dim.3) %>% 
  left_join(coldata)
```


### Panels {.tabset}

#### Panel A
```{r suppl_figS14_panelA, fig.width=6, fig.height=3, fig.retina=1}
# Select Data
data_suppl_figS14 <- pca_data %>%
   dplyr::filter(inhib_group %in% group_select_suppl_figS14)

pca_legend_levels <- c("Basal\nDMSO ctrl", 
                       "Activated\nDMSO ctrl", 
                       "Activated\n10 uM iBTK", "Activated\n10 uM iSYK", "Activated\n10 uM iNFkB", 
                       "Activated\n2.5 uM of iSYK + iBTK", "Activated\n2.5 uM of iBTK + iNFkB", "Activated\n2.5 uM of iSYK + iNFkB", 
                       "Activated\n1 uM of iSYK + iBTK + iNFkB", "Activated\n2.5 uM of iSYK + iBTK + iNFkB", "Activated\n10 uM of iSYK + iBTK + iNFkB", "Basal\n10 uM of iSYK + iBTK + iNFkB", 
                       "Activated\n5 uM iBTK + 1 uM of iSYK + iNFkB", "Activated\n5 uM iSYK + 1 uM of iBTK + iNFkB", "Activated\n5 uM iNFkB + 1 uM of iSYK + iBTK")
pca_legend_shapes <- c(16, 
                       17, 
                       17, 17, 17, 
                       17, 17, 17, 
                       17, 17, 17, 16, 
                       17, 17, 17)
pca_legend_values <- c("#bdbdbd", 
                       "#737373", 
                       "#5c9dce", "#9dce5c", "#ce5c9d", 
                       "#5cce8d", "#8d5cce", "#ce8d5c", 
                       "#d3bceb", "#ae82da", "#8351b6", "#857892", 
                       "#729cb9", "#9bb677", "#b6779b")
names(pca_legend_shapes) <- pca_legend_levels
names(pca_legend_values) <- pca_legend_levels
pca_legend_labels <- c(
  "Basal\nDMSO ctrl" = "Basal\nDMSO ctrl", 
  "Activated\nDMSO ctrl" = "Activated\nDMSO ctrl", 
  "Activated\n10 uM iBTK" = "10 uM iBTK",
  "Activated\n10 uM iSYK" = "10 uM iSYK",
  "Activated\n10 uM iNFkB" = "10 uM iNFkB",
  "Activated\n2.5 uM of iSYK + iBTK" = "2.5 uM iBTK + iSYK", 
  "Activated\n2.5 uM of iBTK + iNFkB" = "2.5 uM iBTK + iNFkB", 
  "Activated\n2.5 uM of iSYK + iNFkB" = "2.5 uM iSYK + iNFkB",  
  "Activated\n1 uM of iSYK + iBTK + iNFkB" = "1 uM of each",
  "Activated\n2.5 uM of iSYK + iBTK + iNFkB" = "2.5 uM of each",
  "Activated\n10 uM of iSYK + iBTK + iNFkB" = "10 uM of each",
  "Basal\n10 uM of iSYK + iBTK + iNFkB" = "Basal\n10 uM of each",
  "Activated\n5 uM iBTK + 1 uM of iSYK + iNFkB" = "5 uM iBTK + \n1 uM iSYK + iNFkB",
  "Activated\n5 uM iSYK + 1 uM of iBTK + iNFkB" = "5 uM iSYK + \n1 uM iBTK + iNFkB",
  "Activated\n5 uM iNFkB + 1 uM of iSYK + iBTK" = "5 uM iNFkB + \n1 uM iSYK + iBTK")

# Figure
suppl_figS14_panelA <- ggplot(data_suppl_figS14) + 
  geom_point(aes(x = PC1, y = PC3, 
                 shape = stim_inhib, color = stim_inhib), 
             size = 2.5) +
  scale_color_manual(values = pca_legend_values,
                     breaks = pca_legend_levels,
                     labels = pca_legend_labels,
                     name = "Treatment") +
  scale_shape_manual(values = pca_legend_shapes,
                     breaks = pca_legend_levels,
                     labels = pca_legend_labels,
                     name = "Treatment") +
  xlab(paste0("PC1: ", pca_expl_var[1], "% variance")) +
  ylab(paste0("PC3: ", pca_expl_var[3], "% variance")) + 
  facet_wrap(vars(factor(experiment, labels = "PC1 vs PC3"))) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(), legend.key.size = unit(0.6, "cm"), legend.spacing.y = unit(0.5, "cm"), legend.box.spacing = unit(0.2, "cm"), legend.position = "none", legend.justification = "left") +
  textsize_small
suppl_figS14_panelA
```

#### Panel B
```{r suppl_figS14_panelB, fig.width=6, fig.height=3, fig.retina=1}
# Figure
suppl_figS14_panelB <- ggplot(data_suppl_figS14) + 
  geom_point(aes(x = PC2, y = PC3, 
                 shape = stim_inhib, color = stim_inhib), 
             size = 2.5) +
  scale_color_manual(values = pca_legend_values,
                     breaks = pca_legend_levels,
                     labels = pca_legend_labels,
                     name = "Treatment") +
  scale_shape_manual(values = pca_legend_shapes,
                     breaks = pca_legend_levels,
                     labels = pca_legend_labels,
                     name = "Treatment") +
  xlab(paste0("PC2: ", pca_expl_var[2], "% variance")) +
  ylab(paste0("PC3: ", pca_expl_var[3], "% variance")) + 
  facet_wrap(vars(factor(experiment, labels = "PC1 vs PC3"))) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(), legend.key.size = unit(0.6, "cm"), legend.spacing.y = unit(0.5, "cm"), legend.box.spacing = unit(0.2, "cm"), legend.position = "right", legend.justification = "left") +
  textsize_small
suppl_figS14_panelB
```


### Combined fig

```{r suppl_figS14_combi, fig.width=6.125, fig.height=2.5, fig.retina=1}
# Combine all panels of the figure
suppl_figS14 <- plot_grid(suppl_figS14_panelA, suppl_figS14_panelB, labels = PANEL_labels[c(1, 2)], nrow = 1, rel_widths = c(1, 1.35), label_size = 10)
suppl_figS14

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS14,
  filename = "output/figures/paper/suppl_figS14.pdf",
  width = 6.125,
  height = 2.5,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS14,
  filename = "output/figures/paper/suppl_figS14.jpg",
  width = 6.125,
  height = 2.5,
  units = "in",
  dpi = 300
  )
```
*Figure S14: Principal components PC1-3 visualized for DMSO controls (basal and activated) and 10 uM single inhibitor treatment.*

```{r suppl_figS14_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS14"))
rm(list = ls(pattern = "pca"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S15

*Inhibition effect of 10 uM iSYK or 100 uM iNFkB versus DMSO control in activated cells (inhibitor combination experiment).*

Input:
-   Cytoscape network figures


### Panels {.tabset}

#### Panel A
```{r suppl_figS15_panelA, fig.retina=1}
# Placeholder
suppl_figS15_panelA <- ggplot() +
  geom_blank() +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 10)) + 
  # labs(title = "BCR signaling network") + 
  theme_bw() +
  theme(axis.text = element_text(color = "white"), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank()) +
  textsize_small
# suppl_figS15_panelA

# PNG
# 100 uM iSYK (DS108)
png_suppl_figS15_panelA <- magick::image_read("output/figures/non_R_figs/combi_iSYKvsDMSOctrl.png") %>%
  magick::image_border(color = "black", geometry = "1x1") %>%
  magick::image_ggplot(interpolate = TRUE) +
  ggtitle("10 uM iSYK vs DMSO ctrl in activated cells") +
  # theme(axis.title = element_text(colour = "white"), axis.text = element_blank()) +
  textsize_small
png_suppl_figS15_panelA

# legend
png_suppl_figS15_legend <- magick::image_read("output/figures/non_R_figs/legend_network_projections.png") %>%
  # magick::image_border(color = "black", geometry = "1x1") %>%
  magick::image_ggplot(interpolate = TRUE) +
  # ggtitle("\n") +
  textsize_small
# png_suppl_figS15_legend
```

#### Panel B
```{r suppl_figS15_panelB, fig.retina=1}
# Placeholder
suppl_figS15_panelB <- ggplot() +
  geom_blank() +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 10)) + 
  # labs(title = "BCR signaling network") + 
  theme_bw() +
  theme(axis.text = element_text(color = "white"), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank()) +
  textsize_small
# suppl_figS15_panelB

# PNG
# 100 uM iNFkB (DS108)
png_suppl_figS15_panelB <- magick::image_read("output/figures/non_R_figs/combi_iNFkBvsDMSOctrl.png") %>%
  magick::image_border(color = "black", geometry = "1x1") %>%
  magick::image_ggplot(interpolate = TRUE) +
  ggtitle("10 uM iNFkB vs DMSO ctrl in activated cells") +
  # theme(axis.title = element_text(colour = "white"), axis.text = element_blank()) +
  textsize_small
png_suppl_figS15_panelB
```


### Combined fig

```{r suppl_figS15_combi, fig.width=7.3, fig.height=4.4, fig.retina=1}
# Combine all panels of the figure
suppl_figS15_AB <- plot_grid(png_suppl_figS15_panelA, png_suppl_figS15_panelB, labels = PANEL_labels[c(1, 2)], nrow = 1, rel_widths = c(1, 1), label_size = 10)
suppl_figS15 <- plot_grid(suppl_figS15_AB, png_suppl_figS15_legend, ncol = 1, rel_heights = c(7, 1), label_size = 10)
suppl_figS15

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS15,
  filename = "output/figures/paper/suppl_figS15.pdf",
  width = 7.3,
  height = 4.5,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS15,
  filename = "output/figures/paper/suppl_figS15.jpg",
  width = 7.3,
  height = 4.5,
  units = "in",
  dpi = 300
  )
```
*Figure S15: Inhibition effect of 10 uM iSYK or 100 uM iNFkB versus DMSO control in activated cells (inhibitor combination experiment).*

```{r suppl_figS15_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS15"))
# rm(list = ls(pattern = "_fig1"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S16

*Individual protein data exemplifying either strong repression across all inhibitor combinations that were investigated, or inhibitor-dependent differences in the strength of repression.*

Input:
-   DS113 ID-seq data

    -   Count data

### Data

```{r suppl_figS16_data}
# ID-seq data (counts per well/sample and mean per condition)
data_ID_suppl_figS16 <- read_csv("output/DS113_InhibCombiIDseq/IDseq_ann/IDseq_data_sample.csv") %>%
  subset(inhibitor != "iPI3Kd" & target_nospace != "BIM" & target_nospace != "Histone_H2AX_S139" & cell_line == "HBL1") %>%
  mutate(stim_inhib = paste0(stim_clean, "\n", inhib_text_new)) #%>%
  # subset(inhib_new != "PBS ctrl")
mean_ID_suppl_figS16 <- read_csv("output/DS113_InhibCombiIDseq/IDseq_ann/IDseq_data_condition.csv") %>%
  subset(inhibitor != "iPI3Kd" & target_nospace != "BIM" & target_nospace != "Histone_H2AX_S139" & cell_line == "HBL1") %>%
  mutate(stim_inhib = paste0(stim_clean, "\n", inhib_text_new)) #%>%
  # subset(inhib_new != "PBS ctrl")
```

```{r suppl_figS16_labels}
stim_suppl_figS16 <- c("PBS", "aIg+H2O2")
stim_label_suppl_figS16 <- c("Basal", "Activated")

legend_label_suppl_figS16 <- "iSYK + iBTK + iNFkB"
inhib_group_suppl_figS16 <- c("DMSO ctrl", "single", "two", "three_equal", "three_mix")
inhib_group_label_suppl_figS16 <- c("DMSO ctrl", "Single inhibitor", "Two inhibitors", "Three inhibitors equal", "Three inhibitors mixed")
group_select_suppl_figS16 <- c("DMSO ctrl", "single")
inhib_suppl_figS16 <- c("DMSO ctrl", 
                        "iBTK", "iSYK", "iNFkB", 
                        "iSYK + iBTK", "iBTK + iNFkB", "iSYK +iNFkB", 
                        "iSYK + iBTK + iNFkB")
inhib_label_suppl_figS16 <- c("DMSO ctrl", 
                              "iBTK", "iSYK", "iNFkB", 
                              "iBTK+ iSYK", "iBTK + iNFkB", "iSYK +iNFkB", 
                              "iBTK + iSYK + iNFkB")
conc_single_suppl_figS16 <- c(0, 1, 2.5, 5, 10)
conc_all1_suppl_figS16 <- c("0 + 0 + 0 uM", 
                            "0 + 10 + 0 uM", "10 + 0 + 0 uM", "0 + 0 + 10 uM", 
                            "2.5 + 2.5 + 0 uM", "0 + 2.5 + 2.5 uM", "2.5 + 0 + 2.5 uM", 
                            "1 + 1 + 1 uM", "2.5 + 2.5 + 2.5 uM", "10 + 10 + 10 uM", 
                            "1 + 5 + 1 uM", "5 + 1 + 1 uM", "1 + 1 + 5 uM", 
                            "10 + 10 + 10 uM (nostain)")
conc_all2_suppl_figS16 <- c("DMSO ctrl", 
                            "10 uM iBTK", "10 uM iSYK", "10 uM iNFkB", 
                            "2.5 uM of iSYK + iBTK", "2.5 uM of iBTK + iNFkB", "2.5 uM of iSYK + iNFkB", 
                            "1 uM of iSYK + iBTK + iNFkB", "2.5 uM of iSYK + iBTK + iNFkB", "10 uM of iSYK + iBTK + iNFkB", 
                            "5 uM iBTK + 1 uM of iSYK + iNFkB", "5 uM iSYK + 1 uM of iBTK + iNFkB", "5 uM iNFkB + 1 uM of iSYK + iBTK")
conc_label_suppl_figS16 <- c(
  "DMSO ctrl" = "iBTK             -\niSYK             -\niNFkB            -", #"iBTK\niSYK\niNFkB"
  "10 uM iBTK" = "10\n-\n-", 
  "10 uM iSYK" = "-\n10\n-", 
  "10 uM iNFkB" = "-\n-\n10",
  "2.5 uM of iSYK + iBTK" = "2.5\n2.5\n-", 
  "2.5 uM of iBTK + iNFkB" = "2.5\n-\n2.5", 
  "2.5 uM of iSYK + iNFkB" = "-\n2.5\n2.5", 
  "1 uM of iSYK + iBTK + iNFkB" = "1\n1\n1", 
  "2.5 uM of iSYK + iBTK + iNFkB" = "2.5\n2.5\n2.5", 
  "10 uM of iSYK + iBTK + iNFkB" = "10\n10\n10", 
  "5 uM iBTK + 1 uM of iSYK + iNFkB" = "5\n1\n1", 
  "5 uM iSYK + 1 uM of iBTK + iNFkB" = "1\n5\n1", 
  "5 uM iNFkB + 1 uM of iSYK + iBTK" = "1\n1\n5")

meta_cols_suppl_figS16 <- c("plate_well", "plate", "well", "experiment", "cell_line", "stimulus", "stim_clean", "inhibitor", "inhib_new", "inhib_conc", "inhib_conc_new", "inhib_group", "iSYK_conc_uM", "iBTK_conc_uM", "iNFkB_conc_uM", "inhib_conc_text", "inhib_text_new", "stim_inhib", "replicate", "description", "descript_rep")
```


### Panels {.tabset}

#### Panel A
```{r suppl_figS16_panelA, fig.width=6, fig.height=3, fig.retina=1}
# Select data
proteins_suppl_figS16 <- c("LYN_Y397")
# c("LYN_Y397", "BTK_Y223", "S6_S240_S244", "BTK_Y551")
# c("VAV1_Y174", "BTK_Y223", "BTK_Y551", "CD79a_Y182", "JAK1_Y1022_Y1023", "LYN_Y397", "S6_S235_S236", "S6_S240_S244")
proteins_name_suppl_figS16 <- c("LYN (Y397)")

data_select_suppl_figS16A <- data_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

mean_select_suppl_figS16A <- mean_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

# Figure
suppl_figS16_panelA <- ggplot() +
  # geom_jitter(data = subset(fig1F_data, target_nospace == fig1F_proteins[1]), 
  geom_jitter(data = data_select_suppl_figS16A, 
              aes(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16), 
                  counts_norm, 
                  color = factor(stimulus, levels = stim_suppl_figS16)), 
              alpha = 1, size = 1, width = 0.16) +
  geom_errorbar(data = mean_select_suppl_figS16A,
                aes(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16), 
                    ymin = counts_norm, ymax = counts_norm,
                    group = factor(stimulus, levels = stim_suppl_figS16),
                    color = factor(stimulus, levels = stim_suppl_figS16)),
                width = 0.5, size = 0.75) +
  facet_grid(cols = vars(factor(inhib_group, levels = inhib_group_suppl_figS16, labels = inhib_group_label_suppl_figS16)), 
             # rows = vars(factor(target_nospace, levels = proteins_suppl_figS16)), 
             scales = "free_x", space = "free_x") +
  scale_color_manual(values = colors_stim, breaks = stim_suppl_figS16, labels = stim_label_suppl_figS16, name = "Stimulus") +
  labs(x = element_blank(), y = "Normalized counts", title = proteins_name_suppl_figS16) +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), 
        legend.key.size = unit(0.5, "cm"), legend.spacing.y = unit(0.2, "cm"), legend.box.spacing = unit(0.1, "cm"), 
        legend.position = "right", legend.justification = "right", 
        axis.text.x = element_text(hjust = 0.9, size = 6)) +
  textsize_small
suppl_figS16_panelA
```

```{r suppl_figS16_panelA_stat, fig.width=6, fig.height=3, fig.retina=1}
# Select data
proteins_suppl_figS16 <- c("LYN_Y397")
# c("LYN_Y397", "BTK_Y223", "S6_S240_S244", "BTK_Y551")
# c("VAV1_Y174", "BTK_Y223", "BTK_Y551", "CD79a_Y182", "JAK1_Y1022_Y1023", "LYN_Y397", "S6_S235_S236", "S6_S240_S244")
proteins_name_suppl_figS16 <- c("LYN (Y397)")

data_select_suppl_figS16A <- data_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

mean_select_suppl_figS16A <- mean_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

# Statistics
# Kruskal-Wallis test
figS16A_kruskal <- subset(data_select_suppl_figS16A, stim_clean == "Activated") %>%
  # group_by(target_nospace) %>%
  kruskal_test(counts_norm ~ inhib_text_new)
figS16A_kruskal

# Post-hoc Dunn's test (without correction)
figS16A_dunn <- subset(data_select_suppl_figS16A, stim_clean == "Activated") %>%
  dunn_test(counts_norm ~ inhib_text_new, p.adjust.method = "none") %>%
  dplyr::filter(
    (group2 == "DMSO ctrl") | 
      (group1 == "10 uM iBTK" & (group2 == "10 uM iSYK" | group2 == "10 uM iNFkB")) | 
      (group1 == "10 uM iNFkB" & group2 == "10 uM iSYK") |
      (group1 == "2.5 uM of iBTK + iNFkB" & (group2 == "2.5 uM of iSYK + iBTK" | group2 == "2.5 uM of iSYK + iNFkB")) | 
      (group1 == "2.5 uM of iSYK + iBTK" & group2 == "2.5 uM of iSYK + iNFkB") | 
      (group1 == "1 uM of iSYK + iBTK + iNFkB" & (group2 == "2.5 uM of iSYK + iBTK + iNFkB" | group2 == "10 uM of iSYK + iBTK + iNFkB")) |
      (group1 == "10 uM of iSYK + iBTK + iNFkB" & group2 == "2.5 uM of iSYK + iBTK + iNFkB") | 
      
      (group1 == "5 uM iBTK + 1 uM of iSYK + iNFkB" & (group2 == "5 uM iNFkB + 1 uM of iSYK + iBTK" | group2 == "5 uM iSYK + 1 uM of iBTK + iNFkB")) | 
      (group1 == "5 uM iNFkB + 1 uM of iSYK + iBTK" & group2 == "5 uM iSYK + 1 uM of iBTK + iNFkB")
      ) %>%
  adjust_pvalue(method = "BH") %>%
  # add_xy_position(x = "inhib_text_new")
  mutate(xmin = c(8,  8, 8, 2, 2, 2, 4, 4, 3, 10, 10, 6, 6, 6, 5, 5, 9, 7, 11, 11, 11, 13, 13, 12),
         xmax = c(10, 9, 1, 4, 3, 1, 3, 1, 1, 9,  1,  5, 7, 1, 7, 1, 1, 1, 13, 12, 1,  12, 1,  1),
         plot_order = c(20, 19, 7, 14, 13, 1, 15, 3, 2, 21, 9, 16, 18, 5, 17, 4, 8, 6, 23, 22, 10, 24, 12, 11), 
         plot_order_alt = c(20, 19, 7, -1, -2, 1, 0, 3, 2, 21, 9, 16, 18, 5, 17, 4, 8, 6, 23, 22, 10, 24, 12, 11)) %>%
  arrange(plot_order) %>%
    mutate(grouping = c(rep("DMSO ctrl", times = 12), 
                        rep("Single inhibitor", times = 3), 
                        rep("Two inhibitors", times = 3), 
                        rep("Three inhibitors equal", times = 3), 
                        rep("Three inhibitors mixed", times = 3)), 
           grouping_alt = c(rep("lvl1", times = 12), 
                         rep("lvl1", times = 3), 
                         rep("lvl2", times = 3), 
                         rep("lvl3", times = 3), 
                         rep("lvl4", times = 3))) %>%
  arrange(plot_order_alt)
figS16A_dunn

# Figure
suppl_figS16_panelA_stat <- ggplot() +
  geom_jitter(data = data_select_suppl_figS16A, 
              aes(x = interaction(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16),
                                  factor(inhib_group, levels = inhib_group_suppl_figS16, labels = inhib_group_label_suppl_figS16)
                                  , sep = "!"), 
                  y = counts_norm, 
                  group = factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16), 
                  color = factor(stimulus, levels = stim_suppl_figS16)), 
              alpha = 1, size = 1, width = 0.16) +
  geom_errorbar(data = mean_select_suppl_figS16A,
                aes(interaction(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16),
                                factor(inhib_group, levels = inhib_group_suppl_figS16, labels = inhib_group_label_suppl_figS16)
                                , sep = "!"), 
                    ymin = counts_norm, ymax = counts_norm,
                    group = factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16),
                    color = factor(stimulus, levels = stim_suppl_figS16)),
                width = 0.5, size = 0.6) +
  stat_pvalue_manual(figS16A_dunn, label = "p.adj.signif", tip.length = 0.025,
                     y.position = 4300, step.increase = 0.1, step.group.by = "grouping_alt", size = 2.5, vjust = 0.3) + 
  scale_color_manual(values = colors_stim, breaks = stim_suppl_figS16, labels = stim_label_suppl_figS16, name = "Stimulus") +
  scale_x_discrete(guide = guide_axis_nested(delim = "!"), name = "") +
  labs(x = element_blank(), y = "Normalized counts", title = proteins_name_suppl_figS16) +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), 
        legend.key.size = unit(0.5, "cm"), legend.spacing.y = unit(0.2, "cm"), legend.box.spacing = unit(0.1, "cm"), 
        legend.position = "right", legend.justification = "right", 
        axis.text.x = element_text(hjust = 0.9, size = 7)) +
  textsize_small
suppl_figS16_panelA_stat
```

#### Panel B
```{r suppl_figS16_panelB, fig.width=6, fig.height=3, fig.retina=1}
## Select data
proteins_suppl_figS16 <- c("BTK_Y223")
# c("LYN_Y397", "BTK_Y223", "S6_S240_S244", "BTK_Y551")
# c("VAV1_Y174", "BTK_Y223", "BTK_Y551", "CD79a_Y182", "JAK1_Y1022_Y1023", "LYN_Y397", "S6_S235_S236", "S6_S240_S244")
proteins_name_suppl_figS16 <- c("BTK (Y223)")

data_select_suppl_figS16B <- data_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

mean_select_suppl_figS16B <- mean_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

# Figure
suppl_figS16_panelB <- ggplot() +
  # geom_jitter(data = subset(fig1F_data, target_nospace == fig1F_proteins[1]), 
  geom_jitter(data = data_select_suppl_figS16B, 
              aes(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16), 
                  counts_norm, 
                  color = factor(stimulus, levels = stim_suppl_figS16)), 
              alpha = 1, size = 1, width = 0.16) +
  geom_errorbar(data = mean_select_suppl_figS16B,
                aes(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16), 
                    ymin = counts_norm, ymax = counts_norm,
                    group = factor(stimulus, levels = stim_suppl_figS16),
                    color = factor(stimulus, levels = stim_suppl_figS16)),
                width = 0.5, size = 0.75) +
  facet_grid(cols = vars(factor(inhib_group, levels = inhib_group_suppl_figS16, labels = inhib_group_label_suppl_figS16)), 
             # rows = vars(factor(target_nospace, levels = proteins_suppl_figS16)), 
             scales = "free_x", space = "free_x") +
  scale_color_manual(values = colors_stim, breaks = stim_suppl_figS16, labels = stim_label_suppl_figS16, name = "Stimulus") +
  labs(x = element_blank(), y = "Normalized counts", title = proteins_name_suppl_figS16) +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), 
        legend.key.size = unit(0.5, "cm"), legend.spacing.y = unit(0.2, "cm"), legend.box.spacing = unit(0.1, "cm"), 
        legend.position = "right", legend.justification = "right", 
        axis.text.x = element_text(hjust = 0.9, size = 6)) +
  textsize_small
suppl_figS16_panelB
```

```{r suppl_figS16_panelB_stat, fig.width=6, fig.height=3, fig.retina=1}
# Select data
proteins_suppl_figS16 <- c("BTK_Y223")
# c("LYN_Y397", "BTK_Y223", "S6_S240_S244", "BTK_Y551")
# c("VAV1_Y174", "BTK_Y223", "BTK_Y551", "CD79a_Y182", "JAK1_Y1022_Y1023", "LYN_Y397", "S6_S235_S236", "S6_S240_S244")
proteins_name_suppl_figS16 <- c("BTK (Y223)")

data_select_suppl_figS16B <- data_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

mean_select_suppl_figS16B <- mean_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

# Statistics
# Kruskal-Wallis test
figS16B_kruskal <- subset(data_select_suppl_figS16B, stim_clean == "Activated") %>%
  # group_by(target_nospace) %>%
  kruskal_test(counts_norm ~ inhib_text_new)
figS16B_kruskal

# Post-hoc Dunn's test (without correction)
figS16B_dunn <- subset(data_select_suppl_figS16B, stim_clean == "Activated") %>%
  dunn_test(counts_norm ~ inhib_text_new, p.adjust.method = "none") %>%
  dplyr::filter(
    (group2 == "DMSO ctrl") | 
      (group1 == "10 uM iBTK" & (group2 == "10 uM iSYK" | group2 == "10 uM iNFkB")) | 
      (group1 == "10 uM iNFkB" & group2 == "10 uM iSYK") |
      (group1 == "2.5 uM of iBTK + iNFkB" & (group2 == "2.5 uM of iSYK + iBTK" | group2 == "2.5 uM of iSYK + iNFkB")) | 
      (group1 == "2.5 uM of iSYK + iBTK" & group2 == "2.5 uM of iSYK + iNFkB") | 
      (group1 == "1 uM of iSYK + iBTK + iNFkB" & (group2 == "2.5 uM of iSYK + iBTK + iNFkB" | group2 == "10 uM of iSYK + iBTK + iNFkB")) |
      (group1 == "10 uM of iSYK + iBTK + iNFkB" & group2 == "2.5 uM of iSYK + iBTK + iNFkB") | 
      
      (group1 == "5 uM iBTK + 1 uM of iSYK + iNFkB" & (group2 == "5 uM iNFkB + 1 uM of iSYK + iBTK" | group2 == "5 uM iSYK + 1 uM of iBTK + iNFkB")) | 
      (group1 == "5 uM iNFkB + 1 uM of iSYK + iBTK" & group2 == "5 uM iSYK + 1 uM of iBTK + iNFkB")
      ) %>%
  adjust_pvalue(method = "BH") %>%
  # add_xy_position(x = "inhib_text_new")
  mutate(xmin = c(8,  8, 8, 2, 2, 2, 4, 4, 3, 10, 10, 6, 6, 6, 5, 5, 9, 7, 11, 11, 11, 13, 13, 12),
         xmax = c(10, 9, 1, 4, 3, 1, 3, 1, 1, 9,  1,  5, 7, 1, 7, 1, 1, 1, 13, 12, 1,  12, 1,  1),
         plot_order = c(20, 19, 7, 14, 13, 1, 15, 3, 2, 21, 9, 16, 18, 5, 17, 4, 8, 6, 23, 22, 10, 24, 12, 11), 
         plot_order_alt = c(20, 19, 7, -1, -2, 1, 0, 3, 2, 21, 9, 16, 18, 5, 17, 4, 8, 6, 23, 22, 10, 24, 12, 11)) %>%
  arrange(plot_order) %>%
    mutate(grouping = c(rep("DMSO ctrl", times = 12), 
                        rep("Single inhibitor", times = 3), 
                        rep("Two inhibitors", times = 3), 
                        rep("Three inhibitors equal", times = 3), 
                        rep("Three inhibitors mixed", times = 3)), 
           grouping_alt = c(rep("lvl1", times = 12), 
                         rep("lvl1", times = 3), 
                         rep("lvl2", times = 3), 
                         rep("lvl3", times = 3), 
                         rep("lvl4", times = 3))) %>%
  arrange(plot_order_alt)
figS16B_dunn

# Figure
suppl_figS16_panelB_stat <- ggplot() +
  geom_jitter(data = data_select_suppl_figS16B, 
              aes(x = interaction(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16),
                                  factor(inhib_group, levels = inhib_group_suppl_figS16, labels = inhib_group_label_suppl_figS16)
                                  , sep = "!"), 
                  y = counts_norm, 
                  group = factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16), 
                  color = factor(stimulus, levels = stim_suppl_figS16)), 
              alpha = 1, size = 1, width = 0.16) +
  geom_errorbar(data = mean_select_suppl_figS16B,
                aes(interaction(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16),
                                factor(inhib_group, levels = inhib_group_suppl_figS16, labels = inhib_group_label_suppl_figS16)
                                , sep = "!"), 
                    ymin = counts_norm, ymax = counts_norm,
                    group = factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16),
                    color = factor(stimulus, levels = stim_suppl_figS16)),
                width = 0.5, size = 0.6) +
  stat_pvalue_manual(figS16B_dunn, label = "p.adj.signif", tip.length = 0.01,
                     y.position = 2000, step.increase = 0.1, step.group.by = "grouping_alt", size = 1.25, vjust = 0.4) + 
  scale_color_manual(values = colors_stim, breaks = stim_suppl_figS16, labels = stim_label_suppl_figS16, name = "Stimulus") +
  scale_x_discrete(guide = guide_axis_nested(delim = "!"), name = "") +
  labs(x = element_blank(), y = "Normalized counts", title = proteins_name_suppl_figS16) +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), 
        legend.key.size = unit(0.5, "cm"), legend.spacing.y = unit(0.2, "cm"), legend.box.spacing = unit(0.1, "cm"), 
        legend.position = "right", legend.justification = "right", 
        axis.text.x = element_text(hjust = 0.9, size = 6)) +
  textsize_small
suppl_figS16_panelB_stat
```

#### Panel C
```{r suppl_figS16_panelC, fig.width=6, fig.height=3, fig.retina=1}
## Select data
proteins_suppl_figS16 <- c("S6_S240_S244")
# c("LYN_Y397", "BTK_Y223", "S6_S240_S244", "BTK_Y551")
# c("VAV1_Y174", "BTK_Y223", "BTK_Y551", "CD79a_Y182", "JAK1_Y1022_Y1023", "LYN_Y397", "S6_S235_S236", "S6_S240_S244")
proteins_name_suppl_figS16 <- c("S6 (S240/S244)")

data_select_suppl_figS16C <- data_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

mean_select_suppl_figS16C <- mean_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

# Figure
suppl_figS16_panelC <- ggplot() +
  # geom_jitter(data = subset(fig1F_data, target_nospace == fig1F_proteins[1]), 
  geom_jitter(data = data_select_suppl_figS16C, 
              aes(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16), 
                  counts_norm, 
                  color = factor(stimulus, levels = stim_suppl_figS16)), 
              alpha = 1, size = 1, width = 0.16) +
  geom_errorbar(data = mean_select_suppl_figS16C,
                aes(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16), 
                    ymin = counts_norm, ymax = counts_norm,
                    group = factor(stimulus, levels = stim_suppl_figS16),
                    color = factor(stimulus, levels = stim_suppl_figS16)),
                width = 0.5, size = 0.75) +
  facet_grid(cols = vars(factor(inhib_group, levels = inhib_group_suppl_figS16, label = inhib_group_label_suppl_figS16)), 
             # rows = vars(factor(target_nospace, levels = proteins_suppl_figS16)), 
             scales = "free_x", space = "free_x") +
  scale_color_manual(values = colors_stim, breaks = stim_suppl_figS16, labels = stim_label_suppl_figS16, name = "Stimulus") +
  labs(x = element_blank(), y = "Normalized counts", title = proteins_name_suppl_figS16) +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), 
        legend.key.size = unit(0.5, "cm"), legend.spacing.y = unit(0.2, "cm"), legend.box.spacing = unit(0.1, "cm"), 
        legend.position = "right", legend.justification = "right", 
        axis.text.x = element_text(hjust = 0.9, size = 6)) +
  textsize_small
suppl_figS16_panelC
```

```{r suppl_figS16_panelC_stat, fig.width=6, fig.height=3, fig.retina=1}
## Select data
proteins_suppl_figS16 <- c("S6_S240_S244")
# c("LYN_Y397", "BTK_Y223", "S6_S240_S244", "BTK_Y551")
# c("VAV1_Y174", "BTK_Y223", "BTK_Y551", "CD79a_Y182", "JAK1_Y1022_Y1023", "LYN_Y397", "S6_S235_S236", "S6_S240_S244")
proteins_name_suppl_figS16 <- c("S6 (S240/S244)")

data_select_suppl_figS16C <- data_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

mean_select_suppl_figS16C <- mean_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

# Statistics
# Kruskal-Wallis test
figS16C_kruskal <- subset(data_select_suppl_figS16C, stim_clean == "Activated") %>%
  # group_by(target_nospace) %>%
  kruskal_test(counts_norm ~ inhib_text_new)
figS16C_kruskal

# Post-hoc Dunn's test (without correction)
figS16C_dunn <- subset(data_select_suppl_figS16C, stim_clean == "Activated") %>%
  dunn_test(counts_norm ~ inhib_text_new, p.adjust.method = "none") %>%
  dplyr::filter(
    (group2 == "DMSO ctrl") | 
      (group1 == "10 uM iBTK" & (group2 == "10 uM iSYK" | group2 == "10 uM iNFkB")) | 
      (group1 == "10 uM iNFkB" & group2 == "10 uM iSYK") |
      (group1 == "2.5 uM of iBTK + iNFkB" & (group2 == "2.5 uM of iSYK + iBTK" | group2 == "2.5 uM of iSYK + iNFkB")) | 
      (group1 == "2.5 uM of iSYK + iBTK" & group2 == "2.5 uM of iSYK + iNFkB") | 
      (group1 == "1 uM of iSYK + iBTK + iNFkB" & (group2 == "2.5 uM of iSYK + iBTK + iNFkB" | group2 == "10 uM of iSYK + iBTK + iNFkB")) |
      (group1 == "10 uM of iSYK + iBTK + iNFkB" & group2 == "2.5 uM of iSYK + iBTK + iNFkB") | 
      
      (group1 == "5 uM iBTK + 1 uM of iSYK + iNFkB" & (group2 == "5 uM iNFkB + 1 uM of iSYK + iBTK" | group2 == "5 uM iSYK + 1 uM of iBTK + iNFkB")) | 
      (group1 == "5 uM iNFkB + 1 uM of iSYK + iBTK" & group2 == "5 uM iSYK + 1 uM of iBTK + iNFkB")
      ) %>%
  adjust_pvalue(method = "BH") %>%
  # add_xy_position(x = "inhib_text_new")
  mutate(xmin = c(8,  8, 8, 2, 2, 2, 4, 4, 3, 10, 10, 6, 6, 6, 5, 5, 9, 7, 11, 11, 11, 13, 13, 12),
         xmax = c(10, 9, 1, 4, 3, 1, 3, 1, 1, 9,  1,  5, 7, 1, 7, 1, 1, 1, 13, 12, 1,  12, 1,  1),
         plot_order = c(20, 19, 7, 14, 13, 1, 15, 3, 2, 21, 9, 16, 18, 5, 17, 4, 8, 6, 23, 22, 10, 24, 12, 11), 
         plot_order_alt = c(20, 19, 7, -1, -2, 1, 0, 3, 2, 21, 9, 16, 18, 5, 17, 4, 8, 6, 23, 22, 10, 24, 12, 11)) %>%
  arrange(plot_order) %>%
    mutate(grouping = c(rep("DMSO ctrl", times = 12), 
                        rep("Single inhibitor", times = 3), 
                        rep("Two inhibitors", times = 3), 
                        rep("Three inhibitors equal", times = 3), 
                        rep("Three inhibitors mixed", times = 3)), 
           grouping_alt = c(rep("lvl1", times = 12), 
                         rep("lvl1", times = 3), 
                         rep("lvl2", times = 3), 
                         rep("lvl3", times = 3), 
                         rep("lvl4", times = 3))) %>%
  arrange(plot_order_alt)
figS16C_dunn

# Figure
suppl_figS16_panelC_stat <- ggplot() +
  geom_jitter(data = data_select_suppl_figS16C, 
              aes(x = interaction(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16),
                                  factor(inhib_group, levels = inhib_group_suppl_figS16, labels = inhib_group_label_suppl_figS16)
                                  , sep = "!"), 
                  y = counts_norm, 
                  group = factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16), 
                  color = factor(stimulus, levels = stim_suppl_figS16)), 
              alpha = 1, size = 1, width = 0.16) +
  geom_errorbar(data = mean_select_suppl_figS16C,
                aes(interaction(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16),
                                factor(inhib_group, levels = inhib_group_suppl_figS16, labels = inhib_group_label_suppl_figS16)
                                , sep = "!"), 
                    ymin = counts_norm, ymax = counts_norm,
                    group = factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16),
                    color = factor(stimulus, levels = stim_suppl_figS16)),
                width = 0.5, size = 0.6) +
  stat_pvalue_manual(figS16C_dunn, label = "p.adj.signif", tip.length = 0.025,
                     y.position = 1750, step.increase = 0.1, step.group.by = "grouping_alt", size = 2.5, vjust = 0.3) + 
  scale_color_manual(values = colors_stim, breaks = stim_suppl_figS16, labels = stim_label_suppl_figS16, name = "Stimulus") +
  scale_x_discrete(guide = guide_axis_nested(delim = "!"), name = "") +
  labs(x = element_blank(), y = "Normalized counts", title = proteins_name_suppl_figS16) +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), 
        legend.key.size = unit(0.5, "cm"), legend.spacing.y = unit(0.2, "cm"), legend.box.spacing = unit(0.1, "cm"), 
        legend.position = "right", legend.justification = "right", 
        axis.text.x = element_text(hjust = 0.9, size = 7)) +
  textsize_small
suppl_figS16_panelC_stat
```

#### Panel D
```{r suppl_figS16_panelD, fig.width=6, fig.height=3, fig.retina=1}
## Select data
proteins_suppl_figS16 <- c("BTK_Y551")
# c("LYN_Y397", "BTK_Y223", "S6_S240_S244", "BTK_Y551")
# c("VAV1_Y174", "BTK_Y223", "BTK_Y551", "CD79a_Y182", "JAK1_Y1022_Y1023", "LYN_Y397", "S6_S235_S236", "S6_S240_S244")
proteins_name_suppl_figS16 <- c("BTK (Y551)")

data_select_suppl_figS16D <- data_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

mean_select_suppl_figS16D <- mean_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

# Figure
suppl_figS16_panelD <- ggplot() +
  # geom_jitter(data = subset(fig1F_data, target_nospace == fig1F_proteins[1]), 
  geom_jitter(data = data_select_suppl_figS16D, 
              aes(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16), 
                  counts_norm, 
                  color = factor(stimulus, levels = stim_suppl_figS16)), 
              alpha = 1, size = 1, width = 0.16) +
  geom_errorbar(data = mean_select_suppl_figS16D,
                aes(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16), 
                    ymin = counts_norm, ymax = counts_norm,
                    group = factor(stimulus, levels = stim_suppl_figS16),
                    color = factor(stimulus, levels = stim_suppl_figS16)),
                width = 0.5, size = 0.75) +
  facet_grid(cols = vars(factor(inhib_group, levels = inhib_group_suppl_figS16, labels = inhib_group_label_suppl_figS16)), 
             # rows = vars(factor(target_nospace, levels = proteins_suppl_figS16)), 
             scales = "free_x", space = "free_x") +
  scale_color_manual(values = colors_stim, breaks = stim_suppl_figS16, labels = stim_label_suppl_figS16, name = "Stimulus") +
  labs(x = element_blank(), y = "Normalized counts", title = proteins_name_suppl_figS16) +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), 
        legend.key.size = unit(0.5, "cm"), legend.spacing.y = unit(0.2, "cm"), legend.box.spacing = unit(0.1, "cm"), 
        legend.position = "right", legend.justification = "right", 
        axis.text.x = element_text(hjust = 0.9, size = 6)) +
  textsize_small
suppl_figS16_panelD
```

```{r suppl_figS16_panelD_stat, fig.width=6, fig.height=3, fig.retina=1}
## Select data
proteins_suppl_figS16 <- c("BTK_Y551")
# c("LYN_Y397", "BTK_Y223", "S6_S240_S244", "BTK_Y551")
# c("VAV1_Y174", "BTK_Y223", "BTK_Y551", "CD79a_Y182", "JAK1_Y1022_Y1023", "LYN_Y397", "S6_S235_S236", "S6_S240_S244")
proteins_name_suppl_figS16 <- c("BTK (Y551)")

data_select_suppl_figS16D <- data_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

mean_select_suppl_figS16D <- mean_ID_suppl_figS16 %>%
  subset(target_nospace %in% proteins_suppl_figS16 & stim_inhib != "Basal\n10 uM of iSYK + iBTK + iNFkB") %>%
  mutate(target_nospace = factor(target_nospace, levels = proteins_suppl_figS16), 
         inhib_conc_new = factor(inhib_text_new, levels = conc_all2_suppl_figS16))

# Statistics
# Kruskal-Wallis test
figS16D_kruskal <- subset(data_select_suppl_figS16D, stim_clean == "Activated") %>%
  # group_by(target_nospace) %>%
  kruskal_test(counts_norm ~ inhib_text_new)
figS16D_kruskal

# Post-hoc Dunn's test (without correction)
figS16D_dunn <- subset(data_select_suppl_figS16D, stim_clean == "Activated") %>%
  dunn_test(counts_norm ~ inhib_text_new, p.adjust.method = "none") %>%
  dplyr::filter(
    (group2 == "DMSO ctrl") | 
      (group1 == "10 uM iBTK" & (group2 == "10 uM iSYK" | group2 == "10 uM iNFkB")) | 
      (group1 == "10 uM iNFkB" & group2 == "10 uM iSYK") |
      (group1 == "2.5 uM of iBTK + iNFkB" & (group2 == "2.5 uM of iSYK + iBTK" | group2 == "2.5 uM of iSYK + iNFkB")) | 
      (group1 == "2.5 uM of iSYK + iBTK" & group2 == "2.5 uM of iSYK + iNFkB") | 
      (group1 == "1 uM of iSYK + iBTK + iNFkB" & (group2 == "2.5 uM of iSYK + iBTK + iNFkB" | group2 == "10 uM of iSYK + iBTK + iNFkB")) |
      (group1 == "10 uM of iSYK + iBTK + iNFkB" & group2 == "2.5 uM of iSYK + iBTK + iNFkB") | 
      
      (group1 == "5 uM iBTK + 1 uM of iSYK + iNFkB" & (group2 == "5 uM iNFkB + 1 uM of iSYK + iBTK" | group2 == "5 uM iSYK + 1 uM of iBTK + iNFkB")) | 
      (group1 == "5 uM iNFkB + 1 uM of iSYK + iBTK" & group2 == "5 uM iSYK + 1 uM of iBTK + iNFkB")
      ) %>%
  adjust_pvalue(method = "BH") %>%
  # add_xy_position(x = "inhib_text_new")
  mutate(xmin = c(8,  8, 8, 2, 2, 2, 4, 4, 3, 10, 10, 6, 6, 6, 5, 5, 9, 7, 11, 11, 11, 13, 13, 12),
         xmax = c(10, 9, 1, 4, 3, 1, 3, 1, 1, 9,  1,  5, 7, 1, 7, 1, 1, 1, 13, 12, 1,  12, 1,  1),
         plot_order = c(20, 19, 7, 14, 13, 1, 15, 3, 2, 21, 9, 16, 18, 5, 17, 4, 8, 6, 23, 22, 10, 24, 12, 11), 
         plot_order_alt = c(20, 19, 7, -1, -2, 1, 0, 3, 2, 21, 9, 16, 18, 5, 17, 4, 8, 6, 23, 22, 10, 24, 12, 11)) %>%
  arrange(plot_order) %>%
    mutate(grouping = c(rep("DMSO ctrl", times = 12), 
                        rep("Single inhibitor", times = 3), 
                        rep("Two inhibitors", times = 3), 
                        rep("Three inhibitors equal", times = 3), 
                        rep("Three inhibitors mixed", times = 3)), 
           grouping_alt = c(rep("lvl1", times = 12), 
                         rep("lvl1", times = 3), 
                         rep("lvl2", times = 3), 
                         rep("lvl3", times = 3), 
                         rep("lvl4", times = 3))) %>%
  arrange(plot_order_alt)
figS16D_dunn

# Figure
suppl_figS16_panelD_stat <- ggplot() +
  geom_jitter(data = data_select_suppl_figS16D, 
              aes(x = interaction(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16),
                                  factor(inhib_group, levels = inhib_group_suppl_figS16, labels = inhib_group_label_suppl_figS16)
                                  , sep = "!"), 
                  y = counts_norm, 
                  group = factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16), 
                  color = factor(stimulus, levels = stim_suppl_figS16)), 
              alpha = 1, size = 1, width = 0.16) +
  geom_errorbar(data = mean_select_suppl_figS16D,
                aes(interaction(factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16),
                                factor(inhib_group, levels = inhib_group_suppl_figS16, labels = inhib_group_label_suppl_figS16)
                                , sep = "!"), 
                    ymin = counts_norm, ymax = counts_norm,
                    group = factor(inhib_text_new, levels = conc_all2_suppl_figS16, labels = conc_label_suppl_figS16),
                    color = factor(stimulus, levels = stim_suppl_figS16)),
                width = 0.5, size = 0.6) +
  stat_pvalue_manual(figS16D_dunn, label = "p.adj.signif", tip.length = 0.01,
                     y.position = 3500, step.increase = 0.1, step.group.by = "grouping_alt", size = 1.25, vjust = 0.4) + 
  scale_color_manual(values = colors_stim, breaks = stim_suppl_figS16, labels = stim_label_suppl_figS16, name = "Stimulus") +
  scale_x_discrete(guide = guide_axis_nested(delim = "!"), name = "") +
  labs(x = element_blank(), y = "Normalized counts", title = proteins_name_suppl_figS16) +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), 
        legend.key.size = unit(0.5, "cm"), legend.spacing.y = unit(0.2, "cm"), legend.box.spacing = unit(0.1, "cm"), 
        legend.position = "right", legend.justification = "right", 
        axis.text.x = element_text(hjust = 0.9, size = 6)) +
  textsize_small
suppl_figS16_panelD_stat
```


### Combined fig

```{r suppl_figS16_combi, fig.width=7.3, fig.height=8, fig.retina=1, eval=F}
# Combine all panels of the figure
suppl_figS16 <- plot_grid(suppl_figS16_panelA, suppl_figS16_panelB, suppl_figS16_panelC, suppl_figS16_panelD, labels = PANEL_labels[c(1:4)], ncol = 1, rel_heights = c(1, 1, 1, 1), label_size = 10)
suppl_figS16

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS16,
  filename = "output/figures/paper/suppl_figS16.pdf",
  width = 7.3,
  height = 8,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS16,
  filename = "output/figures/paper/suppl_figS16.jpg",
  width = 7.3,
  height = 8,
  units = "in",
  dpi = 300
  )
```

```{r suppl_figS16_combi_stat, fig.width=7.3, fig.height=8, fig.retina=1}
# Combine all panels of the figure
# suppl_figS16 <- plot_grid(suppl_figS16_panelA_stat, suppl_figS16_panelB_stat, suppl_figS16_panelC_stat, suppl_figS16_panelD_stat, labels = PANEL_labels[c(1:4)], ncol = 1, rel_heights = c(1, 1, 1, 1), label_size = 10)
suppl_figS16 <- plot_grid(suppl_figS16_panelA_stat, suppl_figS16_panelC_stat, labels = PANEL_labels[c(1:2)], ncol = 1, rel_heights = c(1, 1, 1, 1), label_size = 10)
suppl_figS16

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS16,
  filename = "output/figures//papersuppl_figS16.pdf",
  width = 7.3,
  height = 8,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS16,
  filename = "output/figures//papersuppl_figS16.jpg",
  width = 7.3,
  height = 8,
  units = "in",
  dpi = 300
  )
```
*Figure S16: Individual protein data exemplifying either strong repression across all inhibitor combinations that were investigated, or inhibitor-dependent differences in the strength of repression.*

```{r suppl_figS16_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS16"))
# rm(list = ls(pattern = "_fig1"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S17

*Flow cytometry gating strategy.*

Input:
-   DS108 phosphoflow data

    -   Gating plots


### Panels {.tabset}

#### Panel A
```{r suppl_figS17_panelA, fig.retina=1}
# Placeholder
suppl_figS17_panelA <- ggplot() +
  geom_blank() +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 10)) + 
  # labs(title = "BCR signaling network") + 
  theme_bw() +
  theme(axis.text = element_text(color = "white"), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank()) +
  textsize_small
# suppl_figS17_panelA

# PNG
png_suppl_figS17_panelA <- magick::image_read("output/figures/gating_figs/fig_debris_DS108.png") %>%
  image_ggplot(interpolate = TRUE)
png_suppl_figS17_panelA
```

#### Panel B
```{r suppl_figS17_panelB, fig.retina=1}
# Placeholder
suppl_figS17_panelB <- ggplot() +
  geom_blank() +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 10)) + 
  # labs(title = "BCR signaling network") + 
  theme_bw() +
  theme(axis.text = element_text(color = "white"), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank()) +
  textsize_small
# suppl_figS17_panelB

# PNG
png_suppl_figS17_panelB <- magick::image_read("output/figures/gating_figs/fig_singlets_DS108.png") %>%
  image_ggplot(interpolate = TRUE)
png_suppl_figS17_panelB
```

#### Panel C
```{r suppl_figS17_panelC, fig.retina=1}
# Placeholder
suppl_figS17_panelC <- ggplot() +
  geom_blank() +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 10)) + 
  # labs(title = "BCR signaling network") + 
  theme_bw() +
  theme(axis.text = element_text(color = "white"), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank()) +
  textsize_small
# suppl_figS17_panelC

# PNG
png_suppl_figS17_panelC <- magick::image_read("output/figures/gating_figs/fig_live_DS108.png") %>%
  image_ggplot(interpolate = TRUE)
png_suppl_figS17_panelC
```


### Combined fig

```{r suppl_figS17_combi, fig.width=7.3, fig.height=2.5, fig.retina=1}
# Combine all panels of the figure
suppl_figS17 <- plot_grid(png_suppl_figS17_panelA, png_suppl_figS17_panelB, png_suppl_figS17_panelC, labels = PANEL_labels[c(1, 2, 3)], ncol = 3, rel_widths = c(1, 1, 1), label_size = 10)
suppl_figS17

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS17,
  filename = "output/figures/paper/suppl_figS17.pdf",
  width = 7.3,
  height = 2.5,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS17,
  filename = "output/figures/paper/suppl_figS17.jpg",
  width = 7.3,
  height = 2.5,
  units = "in",
  dpi = 300
  )
```
*Figure S17: Flow cytometry gating strategy.*

```{r suppl_figS17_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS17"))
# rm(list = ls(pattern = "_fig1"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S18

*Antibody barcode design for the ID-seq protocol.*

Input:
-   BioRender schematic figure


### Panels {.tabset}

#### Panel A
```{r suppl_figS18_panelA, fig.retina=1}
# Placeholder
suppl_figS18_panelA <- ggplot() +
  geom_blank() +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 10)) + 
  labs(title = "Ab barcode design") +
  theme_bw() +
  theme(axis.text = element_text(color = "white"), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank()) +
  textsize_small
# suppl_figS18_panelA

# PNG
png_suppl_figS18 <- magick::image_read("output/figures/non_R_figs/Ab_barcode_primers_design.png") %>%
  magick::image_ggplot()
png_suppl_figS18
```


### Combined fig

```{r suppl_figS18_combi, fig.width=7.3, fig.height=3, fig.retina=1}
# Combine all panels of the figure
png_suppl_figS18

# Save figure as pdf, jpg, and png
# ggsave(
#   suppl_figS18,
#   filename = "output/figures/paper/suppl_figS18.pdf",
#   width = 6,
#   height = 3,
#   units = "in",
#   dpi = 300
#   )
ggsave(
  suppl_figS18_panelA,
  filename = "output/figures/paper/suppl_figS18_place.jpg",
  width = 7.3,
  height = 3,
  units = "in",
  dpi = 300
  )
```
*Figure S18: Antibody barcode design for the ID-seq protocol.*

```{r suppl_figS18_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS18"))
# rm(list = ls(pattern = "_fig1"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S19

*Examples of successful antibody-DNA tag conjugation for ID-seq. Samples were run on a non-reducing SDS-PAGE gel electrophoresis.*

Input:
-   SDS gel images


### Panels {.tabset}

#### Panel A
```{r suppl_figS19_panelA, fig.retina=1}
# Placeholder
suppl_figS19_panelA <- ggplot() +
  geom_blank() +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 10)) + 
  # labs(title = "Gel example A") +
  theme_bw() +
  theme(axis.text = element_text(color = "white"), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank()) +
  textsize_small
# suppl_figS19_panelA

# PNG
png_suppl_figS19_panelA <- magick::image_read("output/figures/non_R_figs/conjugation_example_2.png") %>%
  magick::image_ggplot()
png_suppl_figS19_panelA
```

#### Panel B
```{r suppl_figS19_panelB, fig.retina=1}
# Placeholder
suppl_figS19_panelB <- ggplot() +
  geom_blank() +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 10)) + 
  # labs(title = "Gel example A") +
  theme_bw() +
  theme(axis.text = element_text(color = "white"), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank()) +
  textsize_small
# suppl_figS19_panelB

# PNG
png_suppl_figS19_panelB <- magick::image_read("output/figures/non_R_figs/conjugation_example_1.png") %>%
  magick::image_ggplot()
png_suppl_figS19_panelB
```

#### Panel C
```{r suppl_figS19_panelC, fig.retina=1}
# Placeholder
suppl_figS19_panelC <- ggplot() +
  geom_blank() +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 10)) + 
  # labs(title = "Gel example A") +
  theme_bw() +
  theme(axis.text = element_text(color = "white"), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank()) +
  textsize_small
# suppl_figS19_panelC

# PNG
png_suppl_figS19_panelC <- magick::image_read("output/figures/non_R_figs/conjugation_example_3.png") %>%
  magick::image_ggplot()
png_suppl_figS19_panelC
```


### Combined fig

```{r suppl_figS19_combi, fig.width=7.3, fig.height=4, fig.retina=1}
# Combine all panels of the figure
suppl_figS19 <- plot_grid(png_suppl_figS19_panelA, png_suppl_figS19_panelB, png_suppl_figS19_panelC, labels = PANEL_labels[c(1, 2, 3)], nrow = 1, rel_widths =  c(1.4, 1.05, 1.01), label_size = 10, label_colour = "white")
suppl_figS19

# Save figure as pdf, jpg, and png
ggsave(
  suppl_figS19,
  filename = "output/figures/paper/suppl_figS19.pdf",
  width = 7.3,
  height = 4,
  units = "in",
  dpi = 300
  )
ggsave(
  suppl_figS19,
  filename = "output/figures/paper/suppl_figS19.jpg",
  width = 7.3,
  height = 4,
  units = "in",
  dpi = 300
  )
```
*Figure S19: Examples of successful antibody-DNA tag conjugation for ID-seq. Samples were run on a non-reducing SDS-PAGE gel electrophoresis.*

```{r suppl_figS19_clean}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "figS19"))
# rm(list = ls(pattern = "_fig1"))
rm(list = ls(pattern = "png_"))
gc()
```



## Suppl. figure S0

*Figure title.*

Input:
-   BioRender schematic figures

-   ... phosphoflow data

-   ... ID-seq data

### Data

```{r suppl_figS0_data, eval=F}

```

```{r suppl_figS0_labels, eval=F}

```


### Panels {.tabset}

#### Panel A
```{r suppl_figS0_panelA, fig.retina=1, eval=F}
# Placeholder
suppl_figS0_panelA <- ggplot() +
  geom_blank() +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 10)) + 
  # labs(title = "BCR signaling network") + 
  theme_bw() +
  theme(axis.text = element_text(color = "white"), 
        axis.ticks = element_blank(), 
        panel.grid = element_blank()) +
  textsize_small
# suppl_figS0_panelA

# PNG
png_suppl_figS0 <- image_read("output/figures/non_R_figs/xxx.png") %>%
  image_ggplot()
# png_suppl_figS0
```

#### Panel B
```{r suppl_figS0_panelB, fig.width=6, fig.height=3, fig.retina=1, eval=F}
# Select data

# Figure

```

#### Panel C


### Combined fig

```{r suppl_figS0_combi, fig.width=6, fig.height=3, fig.retina=1, eval=F}
# Combine all panels of the figure
suppl_figS0 <- plot_grid(panelA, panelB, labels = panel_labels[c(1, 2)], ncol = 1, rel_heights = c(1, 1), label_size = 10)
suppl_figS0

# Save figure as pdf, jpg, and png
# ggsave(
#   suppl_figS1,
#   filename = "output/figures/paper/suppl_figS1.pdf",
#   width = 6,
#   height = 3,
#   units = "in",
#   dpi = 300
#   )
ggsave(
  suppl_figS0,
  filename = "output/figures/paper/suppl_figS0.jpg",
  width = 6,
  height = 3,
  units = "in",
  dpi = 300
  )
# ggsave(
#   suppl_figS1,
#   filename = "output/figures/paper/suppl_figS1.png",
#   width = 6,
#   height = 3,
#   units = "in",
#   dpi = 300
#   )
```

```{r suppl_figS0_clean, eval=F}
# Remove unnecessary files to clear up memory
rm(list = ls(pattern = "suppl_figS1"))
# rm(list = ls(pattern = "_fig1"))
rm(list = ls(pattern = "png_"))
gc()
```



## Moved from main

### Main figure 2

#### Panel E

Effect of ID-seq data normalisation on counts per sample
```{r fig2_panelE, fig.width=6, fig.height=3, fig.retina=1, eval=F}
# Select data
fig2E1_data <- fig2_data_id %>%
  unique()%>%
  group_by(plate_well) %>%
  summarize(counts_total = sum(counts), 
            step = "Raw counts") %>%
  left_join(fig2_data_id[, 1:13]) %>%
  distinct()

fig2E2_data <- fig2_data_id %>%
  unique()%>%
  group_by(plate_well) %>%
  summarize(counts_total = sum(counts_norm), 
            step = "Normalised counts") %>%
  left_join(fig2_data_id[, 1:13]) %>%
  distinct()

fig2E_data <- full_join(fig2E1_data, fig2E2_data)

# Figure
fig2_panelE <- ggplot(fig2E_data, aes(cell_line, counts_total, color = factor(inhib_conc, levels = fig2_conc), shape = stimulus)) +
  geom_jitter(alpha = 1, size = 0.75, width = 0.1) +
  facet_wrap(vars(factor(step, levels =  c("Raw counts", "Normalised counts")))) +
  scale_y_log10() +
  # scale_color_manual(values = c("PBS" = "black", "aIg+H2O2" = "orange"), name = "") +
  scale_color_manual(values = colors_purple9[c(2, 3, 5, 6, 8, 9)], name = "Inhibitor conc.") +
  scale_shape_manual(values = c(16, 17), name = "Stimulus") +
  labs(x = "Inhibitor conc", y = "Counts (log10 scale)") + 
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.2, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm")) + #legend.position = "none"
  guides(fill = guide_legend(byrow = TRUE)) +
  textsize_small
fig2_panelE
```

#### Panel F

Signal of isotype controls
```{r fig2_panelF, fig.width=6, fig.height=3, fig.retina=1, eval=F}
# Select data
fig2F_prot <- c("Isotype_Mouse_IgG1", "Isotype_Rabbit_IgG")
fig2F_data <- fig2_data_id %>%
  subset(target_nospace %in% fig2F_prot & inhib_conc %in% c("0 uM (DMSO)", "100 uM"))
fig2F_mean <- fig2_mean_id %>%
  subset(target_nospace %in% fig2F_prot & inhib_conc %in% c("0 uM (DMSO)", "100 uM")) %>%
  dplyr::group_by(cell_line, stimulus, inhib_conc, target) %>%
  summarise(counts_norm = mean(counts_norm, na.rm = T))

# Figure
fig2_panelF <- ggplot() + 
  geom_jitter(data = fig2F_data,
              aes(inhib_conc, 
                  counts_norm, 
                  color = stimulus, 
                  # shape = cell_line
              ), 
              alpha = 1, size = 0.75, width = 0.1) +
  geom_errorbar(data = fig2F_mean,
                aes(inhib_conc,
                    ymin = counts_norm,
                    ymax = counts_norm,
                    group = stimulus,
                    color = stimulus
                ),
                width = 0.5, size = 0.5) + #, color = "black"
  # facet_wrap(vars(factor(target_nospace, levels = prot_test4)), ncol = 4) +
  facet_wrap(vars(factor(target), factor(cell_line, levels = fig2_cells)), nrow = 1) +
  # scale_y_log10() +
  scale_y_continuous(limits = c(900, 2500)) +
  scale_color_manual(values = colors_stim, name = "Stimulus") + 
  labs(x = "", y = "Normalized counts") +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.3, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm")) + #legend.position = "none"
  textsize_small
fig2_panelF
```


### Main figure 3

#### Panel B

Effect of inhibitor concentration on phospho-protein levels: Clear activation and dose-response inhibition in both cell lines
```{r fig3_panelB, fig.width=6, fig.height=3, fig.retina=1, eval=F}
# Select data
fig3B_prot <- c("BTK_Y551", "JAK1_Y1022_Y1023")
fig3B_data <- fig3_data_id %>%
  subset(target_nospace %in% fig3B_prot & inhib_conc %in% fig3_conc)
fig3B_mean <- fig3_mean_id %>%
  subset(target_nospace %in% fig3B_prot & inhib_conc %in% fig3_conc) 
fig3B_prot_name <- unique(fig3B_data$target)

# Figure
# BTK
fig3_panelB1 <- ggplot() +
  geom_point(data = subset(fig3B_data, target_nospace == fig3B_prot[1]), 
             aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label), 
                 counts_norm, 
                 color = paste(cell_line, "-", stimulus), 
                 shape = paste(cell_line, "-", stimulus)
             ), 
             alpha = 1, size = 0.75) +
  geom_line(data = subset(fig3B_mean, target_nospace == fig3B_prot[1]), 
            aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label),
                counts_norm,
                group = paste(cell_line, "-", stimulus),
                color = paste(cell_line, "-", stimulus)
            ),
            size = 0.5) +
  facet_wrap(vars(factor(inhibitor, levels = fig3_inhib))) +
  # facet_grid(vars(factor(cell_line, levels = fig3_cells)), vars(factor(inhibitor, levels = fig3_inhib))) +
  scale_shape_manual(values = c(16, 16, 17, 17), breaks = fig3_cell_stim, name = "Cells - Stimulus") +
  scale_color_manual(values = colors_cell_stim, 
                     breaks = fig3_cell_stim, 
                     name = "Cells - Stimulus") +
  labs(x = "Inhibitor conc.", y = "Normalized counts", title = paste0("Dose-dependent inhibition in both cell lines\n", fig3B_prot_name[1])) +
  theme_bw() +
  # theme(legend.position = "none", panel.grid.major.x = element_blank()) +
  # theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.3, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm")) + #legend.position = "none"
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.position = "none") +
  textsize_small
# fig3_panelB1

# JAK1
fig3_panelB2 <- ggplot() +
  geom_point(data = subset(fig3B_data, target_nospace == fig3B_prot[2]), 
             aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label), 
                 counts_norm, 
                 color = paste(cell_line, "-", stimulus), 
                 shape = paste(cell_line, "-", stimulus)
             ), 
             alpha = 1, size = 0.75) +
  geom_line(data = subset(fig3B_mean, target_nospace == fig3B_prot[2]), 
            aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label),
                counts_norm,
                group = paste(cell_line, "-", stimulus),
                color = paste(cell_line, "-", stimulus)
            ),
            size = 0.5) +
  facet_wrap(vars(factor(inhibitor, levels = fig3_inhib))) +
  # facet_grid(vars(factor(cell_line, levels = fig3_cells)), vars(factor(inhibitor, levels = fig3_inhib))) +
  scale_shape_manual(values = c(16, 16, 17, 17), breaks = fig3_cell_stim, name = "Cells - Stimulus") +
  scale_color_manual(values = colors_cell_stim, 
                     breaks = fig3_cell_stim, 
                     name = "Cells - Stimulus") +
  labs(x = "Inhibitor conc.", y = "Normalized counts", title = paste0("\n", fig3B_prot_name[2])) +
  theme_bw() +
  # theme(legend.position = "none", panel.grid.major.x = element_blank()) +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.3, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm")) + #legend.position = "none"
  textsize_small
# fig3_panelB2

fig3_panelB <- plot_grid(fig3_panelB1, fig3_panelB2, ncol = 2, rel_widths = c(1, 1.5), align = "h")
fig3_panelB
```

#### Panel C

Effect of inhibitor concentration on phospho-protein levels: Activation and dose-response inhibition in one cell line
```{r fig3_panelC, fig.width=6, fig.height=3, fig.retina=1, eval=F}
# Select data
fig3C_prot <- c("CREB_S133", "MAPK_p38_T180_Y182")
fig3C_data <- fig3_data_id %>%
  subset(target_nospace %in% fig3C_prot & inhib_conc %in% fig3_conc)
fig3C_mean <- fig3_mean_id %>%
  subset(target_nospace %in% fig3C_prot & inhib_conc %in% fig3_conc) 
fig3C_prot_name <- unique(fig3C_data$target)

# Figure
# CREB
fig3_panelC1 <- ggplot() +
  geom_point(data = subset(fig3C_data, target_nospace == fig3C_prot[1]), 
             aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label), 
                 counts_norm, 
                 color = paste(cell_line, "-", stimulus), 
                 shape = paste(cell_line, "-", stimulus)
             ), 
             alpha = 1, size = 0.75) +
  geom_line(data = subset(fig3C_mean, target_nospace == fig3C_prot[1]), 
            aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label),
                counts_norm,
                group = paste(cell_line, "-", stimulus),
                color = paste(cell_line, "-", stimulus)
            ),
            size = 0.5) +
  # facet_wrap(vars(factor(inhibitor, levels = fig3_inhib))) +
  facet_grid(vars(factor(cell_line, levels = fig3_cells)), vars(factor(inhibitor, levels = fig3_inhib))) +
  scale_shape_manual(values = c(16, 16, 17, 17), breaks = fig3_cell_stim, name = "Cells - Stimulus") +
  scale_color_manual(values = colors_cell_stim, 
                     breaks = fig3_cell_stim, 
                     name = "Cells - Stimulus") +
  labs(x = "Inhibitor conc.", y = "Normalized counts", title = paste0("Dose-dependent inhibition in one cell line\n", fig3C_prot_name[1])) +
  theme_bw() +
  # theme(legend.position = "none", panel.grid.major.x = element_blank()) +
  # theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.3, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm")) + #legend.position = "none"
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.position = "none") +
  textsize_small
# fig3_panelC1

# p38
fig3_panelC2 <- ggplot() +
  geom_point(data = subset(fig3C_data, target_nospace == fig3C_prot[2]), 
             aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label), 
                 counts_norm, 
                 color = paste(cell_line, "-", stimulus), 
                 shape = paste(cell_line, "-", stimulus)
             ), 
             alpha = 1, size = 0.75) +
  geom_line(data = subset(fig3C_mean, target_nospace == fig3C_prot[2]), 
            aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label),
                counts_norm,
                group = paste(cell_line, "-", stimulus),
                color = paste(cell_line, "-", stimulus)
            ),
            size = 0.5) +
  # facet_wrap(vars(factor(inhibitor, levels = fig3_inhib))) +
  facet_grid(vars(factor(cell_line, levels = fig3_cells)), vars(factor(inhibitor, levels = fig3_inhib))) +
  scale_shape_manual(values = c(16, 16, 17, 17), breaks = fig3_cell_stim, name = "Cells - Stimulus") +
  scale_color_manual(values = colors_cell_stim, 
                     breaks = fig3_cell_stim, 
                     name = "Cells - Stimulus") +
  labs(x = "Inhibitor conc.", y = "Normalized counts", title =  paste0("\n", fig3C_prot_name[2])) +
  theme_bw() +
  # theme(legend.position = "none", panel.grid.major.x = element_blank()) +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.3, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm")) + #legend.position = "none"
  textsize_small
# fig3_panelC2

fig3_panelC <- plot_grid(fig3_panelC1, fig3_panelC2, ncol = 2, rel_widths = c(1, 1.5), align = "h")
fig3_panelC
```

#### Panel D

Effect of inhibitor concentration on phospho-protein levels: Inhibition in both basal and activated signaling states
```{r fig3_panelD, fig.width=6, fig.height=3, fig.retina=1, eval=F}
# Select data
fig3D_prot <- c("ATF2_T71", "S6_S240_S244")
fig3D_data <- fig3_data_id %>%
  subset(target_nospace %in% fig3D_prot & inhib_conc %in% fig3_conc)
fig3D_mean <- fig3_mean_id %>%
  subset(target_nospace %in% fig3D_prot & inhib_conc %in% fig3_conc) 
fig3D_prot_name <- unique(fig3D_data$target)

# Figure
# ATF2
fig3_panelD1 <- ggplot() +
  geom_point(data = subset(fig3D_data, target_nospace == fig3D_prot[1]), 
             aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label), 
                 counts_norm, 
                 color = paste(cell_line, "-", stimulus), 
                 shape = paste(cell_line, "-", stimulus)
             ), 
             alpha = 1, size = 0.75) +
  geom_line(data = subset(fig3D_mean, target_nospace == fig3D_prot[1]), 
            aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label),
                counts_norm,
                group = paste(cell_line, "-", stimulus),
                color = paste(cell_line, "-", stimulus)
            ),
            size = 0.5) +
  facet_wrap(vars(factor(inhibitor, levels = fig3_inhib))) +
  # facet_grid(vars(factor(cell_line, levels = fig3_cells)), vars(factor(inhibitor, levels = fig3_inhib))) +
  scale_shape_manual(values = c(16, 16, 17, 17), breaks = fig3_cell_stim, name = "Cells - Stimulus") +
  scale_color_manual(values = colors_cell_stim, 
                     breaks = fig3_cell_stim, 
                     name = "Cells - Stimulus") +
  labs(x = "Inhibitor conc.", y = "Normalized counts", title = paste0("Inhibition in basal and activated states\n", fig3D_prot_name[1])) +
  theme_bw() +
  # theme(legend.position = "none", panel.grid.major.x = element_blank()) +
  # theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.3, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm")) + #legend.position = "none"
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.position = "none") +
  textsize_small
# fig3_panelD1

# S6
fig3_panelD2 <- ggplot() +
  geom_point(data = subset(fig3D_data, target_nospace == fig3D_prot[2]), 
             aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label), 
                 counts_norm, 
                 color = paste(cell_line, "-", stimulus), 
                 shape = paste(cell_line, "-", stimulus)
             ), 
             alpha = 1, size = 0.75) +
  geom_line(data = subset(fig3D_mean, target_nospace == fig3D_prot[2]), 
            aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label),
                counts_norm,
                group = paste(cell_line, "-", stimulus),
                color = paste(cell_line, "-", stimulus)
            ),
            size = 0.5) +
  facet_wrap(vars(factor(inhibitor, levels = fig3_inhib))) +
  # facet_grid(vars(factor(cell_line, levels = fig3_cells)), vars(factor(inhibitor, levels = fig3_inhib))) +
  scale_shape_manual(values = c(16, 16, 17, 17), breaks = fig3_cell_stim, name = "Cells - Stimulus") +
  scale_color_manual(values = colors_cell_stim, 
                     breaks = fig3_cell_stim, 
                     name = "Cells - Stimulus") +
  labs(x = "Inhibitor conc.", y = "Normalized counts", title =  paste0("\n", fig3D_prot_name[2])) +
  theme_bw() +
  # theme(legend.position = "none", panel.grid.major.x = element_blank()) +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.3, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm")) + #legend.position = "none"
  textsize_small
# fig3_panelD2

fig3_panelD <- plot_grid(fig3_panelD1, fig3_panelD2, ncol = 2, rel_widths = c(1, 1.5), align = "h")
fig3_panelD
```

#### Panel E

Effect of inhibitor concentration on phospho-protein levels: Increased levels upon inhibition
```{r fig3_panelE, fig.width=6, fig.height=3, fig.retina=1, eval=F}
# Select data
fig3E_prot <- c("AKT_T308", "cMYC_T58") # "STAT6_Y641"
fig3E_data <- fig3_data_id %>%
  subset(target_nospace %in% fig3E_prot & inhib_conc %in% fig3_conc)
fig3E_mean <- fig3_mean_id %>%
  subset(target_nospace %in% fig3E_prot & inhib_conc %in% fig3_conc) 
fig3E_prot_name <- unique(fig3E_data$target)

# Figure
# AKT
fig3_panelE1 <- ggplot() +
  geom_point(data = subset(fig3E_data, target_nospace == fig3E_prot[1]), 
             aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label), 
                 counts_norm, 
                 color = paste(cell_line, "-", stimulus), 
                 shape = paste(cell_line, "-", stimulus)
             ), 
             alpha = 1, size = 0.75) +
  geom_line(data = subset(fig3E_mean, target_nospace == fig3E_prot[1]), 
            aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label),
                counts_norm,
                group = paste(cell_line, "-", stimulus),
                color = paste(cell_line, "-", stimulus)
            ),
            size = 0.5) +
  facet_wrap(vars(factor(inhibitor, levels = fig3_inhib))) +
  # facet_grid(vars(factor(cell_line, levels = fig3_cells)), vars(factor(inhibitor, levels = fig3_inhib))) +
  scale_shape_manual(values = c(16, 16, 17, 17), breaks = fig3_cell_stim, name = "Cells - Stimulus") +
  scale_color_manual(values = colors_cell_stim, 
                     breaks = fig3_cell_stim, 
                     name = "Cells - Stimulus") +
  labs(x = "Inhibitor conc.", y = "Normalized counts", title = paste0("Increased levels upon inhibition\n", fig3E_prot_name[1])) +
  theme_bw() +
  # theme(legend.position = "none", panel.grid.major.x = element_blank()) +
  # theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.3, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm")) + #legend.position = "none"
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.position = "none") +
  textsize_small
# fig3_panelE1

# cMYC
fig3_panelE2 <- ggplot() +
  geom_point(data = subset(fig3E_data, target_nospace == fig3E_prot[2]), 
             aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label), 
                 counts_norm, 
                 color = paste(cell_line, "-", stimulus), 
                 shape = paste(cell_line, "-", stimulus)
             ), 
             alpha = 1, size = 0.75) +
  geom_line(data = subset(fig3E_mean, target_nospace == fig3E_prot[2]), 
            aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label),
                counts_norm,
                group = paste(cell_line, "-", stimulus),
                color = paste(cell_line, "-", stimulus)
            ),
            size = 0.5) +
  facet_wrap(vars(factor(inhibitor, levels = fig3_inhib))) +
  # facet_grid(vars(factor(cell_line, levels = fig3_cells)), vars(factor(inhibitor, levels = fig3_inhib))) +
  scale_shape_manual(values = c(16, 16, 17, 17), breaks = fig3_cell_stim, name = "Cells - Stimulus") +
  scale_color_manual(values = colors_cell_stim, 
                     breaks = fig3_cell_stim, 
                     name = "Cells - Stimulus") +
  labs(x = "Inhibitor conc.", y = "Normalized counts", title =  paste0("\n", fig3E_prot_name[2])) +
  theme_bw() +
  # theme(legend.position = "none", panel.grid.major.x = element_blank()) +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.3, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm")) + #legend.position = "none"
  textsize_small
# fig3_panelE2

fig3_panelE <- plot_grid(fig3_panelE1, fig3_panelE2, ncol = 2, rel_widths = c(1, 1.5), align = "h")
fig3_panelE
```

#### Panel F

Effect of inhibitor concentration on phospho-protein levels: Increased or decreased levels upon inhibition depending on the inhibitor in question
```{r fig3_panelF, fig.width=6, fig.height=3, fig.retina=1, eval=F}
# Select data
fig3F_prot <- c("IKKa_b_S176_S180", "SYK_Y525_Y526") # "PARP_D214"
fig3F_data <- fig3_data_id %>%
  subset(target_nospace %in% fig3F_prot & inhib_conc %in% fig3_conc)
fig3F_mean <- fig3_mean_id %>%
  subset(target_nospace %in% fig3F_prot & inhib_conc %in% fig3_conc) 
fig3F_prot_name <- unique(fig3F_data$target)

# Figure
# IKKa/b
fig3_panelF1 <- ggplot() +
  geom_point(data = subset(fig3F_data, target_nospace == fig3F_prot[1]), 
             aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label), 
                 counts_norm, 
                 color = paste(cell_line, "-", stimulus), 
                 shape = paste(cell_line, "-", stimulus)
             ), 
             alpha = 1, size = 0.75) +
  geom_line(data = subset(fig3F_mean, target_nospace == fig3F_prot[1]), 
            aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label),
                counts_norm,
                group = paste(cell_line, "-", stimulus),
                color = paste(cell_line, "-", stimulus)
            ),
            size = 0.5) +
  facet_wrap(vars(factor(inhibitor, levels = fig3_inhib))) +
  # facet_grid(vars(factor(cell_line, levels = fig3_cells)), vars(factor(inhibitor, levels = fig3_inhib))) +
  scale_shape_manual(values = c(16, 16, 17, 17), breaks = fig3_cell_stim, name = "Cells - Stimulus") +
  scale_color_manual(values = colors_cell_stim, 
                     breaks = fig3_cell_stim, 
                     name = "Cells - Stimulus") +
  labs(x = "Inhibitor conc.", y = "Normalized counts", title = paste0("Inhibitor-dependent in- or decreased levels\n", fig3F_prot_name[1])) +
  theme_bw() +
  # theme(legend.position = "none", panel.grid.major.x = element_blank()) +
  # theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.3, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm")) + #legend.position = "none"
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.position = "none") +
  textsize_small
# fig3_panelF1

# S6
fig3_panelF2 <- ggplot() +
  geom_point(data = subset(fig3F_data, target_nospace == fig3F_prot[2]), 
             aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label), 
                 counts_norm, 
                 color = paste(cell_line, "-", stimulus), 
                 shape = paste(cell_line, "-", stimulus)
             ), 
             alpha = 1, size = 0.75) +
  geom_line(data = subset(fig3F_mean, target_nospace == fig3F_prot[2]), 
            aes(factor(inhib_conc, levels = fig3_conc, labels = fig3_conc_label),
                counts_norm,
                group = paste(cell_line, "-", stimulus),
                color = paste(cell_line, "-", stimulus)
            ),
            size = 0.5) +
  facet_wrap(vars(factor(inhibitor, levels = fig3_inhib))) +
  # facet_grid(vars(factor(cell_line, levels = fig3_cells)), vars(factor(inhibitor, levels = fig3_inhib))) +
  scale_shape_manual(values = c(16, 16, 17, 17), breaks = fig3_cell_stim, name = "Cells - Stimulus") +
  scale_color_manual(values = colors_cell_stim, 
                     breaks = fig3_cell_stim, 
                     name = "Cells - Stimulus") +
  labs(x = "Inhibitor conc.", y = "Normalized counts", title =  paste0("\n", fig3F_prot_name[2])) +
  theme_bw() +
  # theme(legend.position = "none", panel.grid.major.x = element_blank()) +
  theme(panel.grid.minor.y = element_blank(), panel.grid.major.x = element_blank(), legend.key.size = unit(0.3, "cm"), legend.spacing.y = unit(0.1, "cm"), legend.box.spacing = unit(0.1, "cm")) + #legend.position = "none"
  textsize_small
# fig3_panelF2

fig3_panelF <- plot_grid(fig3_panelF1, fig3_panelF2, ncol = 2, rel_widths = c(1, 1.5), align = "h")
fig3_panelF
```

